---
title: "LIM - analysis of results (montane)"
author: "Ceres Barros"
date: "26/04/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "D:/GitHub/LandscapesInMotion/")
knitr::opts_chunk$set(echo = FALSE, cache = 2, warning = FALSE,
                      fig.width = 10, fig.height = 8)
```

```{r setup2, include=FALSE}
library(data.table)
library(ggplot2)
library(ggpubr)
library(ggspatial)
library(cowplot)
library(raster)
library(stars)
library(sf)
library(quickPlot)
library(SpaDES)
library(qs)
library(purrr)
library(magick)
library(LandR)
library(future)
library(future.apply)
library(lme4)
library(MuMIn)
library(ToolsCB)

source("R/R_tools/convertToCNVegType.R")
source("R/R_tools/hypervolumesHelpers.R")
source("R/R_tools/Useful_functions.R")
options("reproducible.useNewDigestAlgorithm" = 2)
options("spades.moduleCodeChecks" = FALSE)
options("reproducible.useCache" = TRUE)
options("reproducible.destinationPath" = normPath("R/SpaDES/inputs"))
options("reproducible.useGDAL" = FALSE)


## general paths
simDirName <- "jun2021Runs"
simPaths <- list(cachePath = file.path("R/SpaDES/cache", simDirName)
                 , modulePath = file.path("R/SpaDES/m")
                 , inputPath = file.path("R/SpaDES/inputs")
                 , outputPath = file.path("R/SpaDES/outputs", simDirName))

## path to figure folder and cache folder
figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane")
cPath <- file.path(simPaths$cachePath, "postSimAnalyses")

## merge Douglas-fir/dry-conifer stands?
## no need with last year classif
mergeDMCPSME <- FALSE  ## merge DMCPSME PSME dryPSME
mergePSME <- TRUE ## merge PSME dryPSME
if (mergeDMCPSME) {
  figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane/mergeDMCPSME")
  HVoutputPathMergedVegType <- file.path(simPaths$outputPath, "hypervolumes", "mergeDMCPSME")
}
if (mergePSME) {
  HVoutputPathMergedVegType <- file.path(simPaths$outputPath, "hypervolumes", "mergePSME")
  figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane/mergePSME")
}
dir.create(figOutputPath, recursive = TRUE)
```

### DATA LOADING AND PROCESSING NOTES
Given the size of the data put together in a pixel-based format, results were sampled every 10 years (instead of the 5-year interval used for saving),

```{r dataPrep, include = FALSE, cache = FALSE}
yearSubset <- c(seq(2011, 2111, 5), 2111)

source("R/SpaDES/6_resultsDataPrep.R")

startYear <- min(yearSubset)
endYear <- max(yearSubset)

## check
if (endYear != max(allPixelCohortDataMnt$year, na.rm = TRUE)) {
  stop("endYear and max(year) differ")
}
if (startYear != min(allPixelCohortDataMnt$year, na.rm = TRUE)) {
  stop("startYear and min(year) differ")
}

if (mergeDMCPSME) {
  allPixelCohortDataMnt[vegTypeCN %in% c("DMCPSME", "PSME", "dryPSME"), vegTypeCN := "DMCPSME"]
  ageDataCN[Cover.dendro %in% c("DMCPSME", "PSME", "dryPSME"), Cover.dendro := "DMCPSME"]
}

if (mergePSME) {
  allPixelCohortDataMnt[vegTypeCN %in% c("PSME", "dryPSME"), vegTypeCN := "PSME"]
  ageDataCN[Cover.dendro %in% c("PSME", "dryPSME"), Cover.dendro := "PSME"]
}

## add vegTypes at the initial year - these are the ones we track in time, the final year may have changed completely -
## and pixels with no fires to burn data - note that we loose the yearly fire data.
allPixelBurnData <- allPixelBurnData[unique(allPixelCohortDataMnt[year == endYear, 
                                                                  .(scenario, rep, pixelIndex, vegTypeCN)]), 
                                     on = .(scenario, rep, pixelIndex)]
cols <- c("fireID", "noFires", "severity", "severityB", "fireSize", "patchSize", "fireInt", "fireFreq")
allPixelBurnData[, (cols) := lapply(.SD, replaceNAs), .SDcols = cols]

## summarise fire data
source("R/R_tools/prepFireData4HVs.R")

## drop unused levels
allPixelBurnData$vegTypeCN <- droplevels(allPixelBurnData$vegTypeCN)
allPixelCohortDataMnt$vegTypeCN <- droplevels(allPixelCohortDataMnt$vegTypeCN)
summaryFireAttributes$vegTypeCN <- droplevels(summaryFireAttributes$vegTypeCN)

## get HV data
HVoutputPath <- file.path(simPaths$outputPath, "hypervolumes")
source("R/R_tools/prepHVData.R")
```

```{r summaryTables, cache=FALSE, include=FALSE}
## SUMMARY ACROSS LANDSCAPE -----------------------------------
## BY SPECIES
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataSpp <- allPixelCohortDataMnt[, list(BiomassBySpecies = as.numeric(sum((B/100), na.rm = TRUE)),
                                                         MortalityBySpecies = as.numeric(sum((mortality/100), na.rm = TRUE)),
                                                         aNPPBySpecies = as.numeric(sum((aNPPAct/100), na.rm = TRUE)),
                                                         AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                         sum((B/100), na.rm = TRUE))),
                                                  by = .(scenario, rep, year, noFires, speciesCode)]
summaryBurnCohortDataSpp[is.nan(AgeBySppWeighted), AgeBySppWeighted := 0]
summaryBurnCohortDataSpp[, firePresAbs := as.integer(noFires != 0)]
amc::.gc()

## BY FOREST TYPE (def. as dominant species)
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataVegType <- allPixelCohortDataMnt[, list(BiomassByVegType = as.numeric(sum((B/100), na.rm = TRUE)),
                                                             MortalityByVegType = as.numeric(sum((mortality/100), na.rm = TRUE)),
                                                             aNPPByVegType = as.numeric(sum((aNPPAct/100), na.rm = TRUE)),
                                                             AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                             sum((B/100), na.rm = TRUE))),
                                                      by = .(scenario, rep, year, noFires, vegType)]
summaryBurnCohortDataVegType[is.nan(AgeBySppWeighted), AgeBySppWeighted := 0]
summaryBurnCohortDataVegType[, firePresAbs := as.integer(noFires != 0)]
amc::.gc()

## BY CAMERON'S VEG TYPE
summaryBurnCohortDataVegTypeCN <- allPixelCohortDataMnt[, list(BiomassByVegType = as.numeric(sum((B/100), na.rm = TRUE)),
                                                               MortalityByVegType = as.numeric(sum((mortality/100), na.rm = TRUE)),
                                                               aNPPByVegType = as.numeric(sum((aNPPAct/100), na.rm = TRUE)),
                                                               AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                               sum((B/100), na.rm = TRUE))),
                                                        by = .(scenario, rep, year, noFires, vegTypeCN)]
summaryBurnCohortDataVegTypeCN[is.nan(AgeBySppWeighted), AgeBySppWeighted := 0]
summaryBurnCohortDataVegTypeCN[, firePresAbs := as.integer(noFires != 0)]
amc::.gc()
```

```{r plotLabels, include = FALSE}
source("R/R_tools/plotLabels&Cols.R")

## filter labellers/colors according to the data
# uniqueVegTypeCN <- c(unique(allPixelCohortDataMnt$vegTypeCN), unique(ageDataCN$Cover.dendro))
# vegTypeCNColours <- vegTypeCNColours[uniqueVegTypeCN]
# vegTypeCNLabels <- vegTypeCNLabels[uniqueVegTypeCN]
# 
# vegTypeColours <- vegTypeColours[unique(allPixelCohortDataMnt$vegType)]
# vegTypeLabels <- vegTypeLabels[unique(allPixelCohortDataMnt$vegType)]
# 
# speciesColours <- speciesColours[unique(allPixelCohortDataMnt$speciesCode)]
# speciesLabels <- speciesLabels[unique(allPixelCohortDataMnt$speciesCode)]

## remove large objs rasters to save memory
rm(list = c(grep("Stk", ls(), value = TRUE), "allPixelCohortData"))
amc::.gc()
```

### TESTING DIFFERENCES BETWEEN OBSERVED AND SIMULATED DATA
AGES
At the end of the simulation, by species
```{r testAges}
## STAT TESTS ------------------------------------------
## AGE SIM VS OBS ----
## comparing simulated and observed ages - end of sim
## ages compared at the species-level, rather than veg type given that some veg types in the sims don't exist
## in the obs data and this would lead to data loss
plotData <- allPixelCohortDataMnt[year == endYear & B > 0,  ## absences can't lower the average ages
                                  list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                       sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]
## observed ages
plotData2 <- copy(ageDataCN[, .(Species, Reconstructed.age, firePresAbs)])
plotData2[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
plotData2[grepl("ABLA", Species), speciesCode := "Abie_sp"]
plotData2[grepl("PIEN", Species), speciesCode := "Pice_eng"]
plotData2[grepl("PICO", Species), speciesCode := "Pinu_sp"]
plotData2[grepl("PSME", Species), speciesCode := "Pseu_men"]
plotData2 <- plotData2[!is.na(speciesCode)]

plotData2 <- plotData2[, list(avgAgeBySppObs = mean(Reconstructed.age, na.rm = TRUE)), 
                       by = .(speciesCode, firePresAbs)]

## join simulated and observed
plotData2 <- plotData2[plotData, on = .(speciesCode, firePresAbs)]
plotData2[, firePresAbs := as.factor(firePresAbs)]
plotData2[, ageDiffSimObs := AgeBySppWeighted - avgAgeBySppObs]
plotData2 <- plotData2[!is.na(ageDiffSimObs)]

plotData2 <- plotData2[!is.na(ageDiffSimObs)]
ageDiffLMList <- lapply(split(plotData2, by = "firePresAbs"), function(DT) {
  # lm(abs(abs(ageDiffSimObs)) ~ scenario * speciesCode, data = DT)
  nlme::gls(abs(abs(ageDiffSimObs)) ~ scenario * speciesCode, weights = nlme::varIdent(form = ~1|speciesCode),
            data = DT)   ## better AIC and residuals
})

plotData2[firePresAbs == "0", 
          pred := predict(ageDiffLMList$`0`, type = "response")]
plotData2[firePresAbs == "1", 
          pred := predict(ageDiffLMList$`1`, type = "response")]
if (isFALSE(class(ageDiffLMList$`0`) == "gls")) {
  plotData2[firePresAbs == "0", 
            predSE := predict(ageDiffLMList$`0`, type = "response", se = TRUE)["se.fit"]]
}

if (isFALSE(class(ageDiffLMList$`1`) == "gls")) {
  plotData2[firePresAbs == "1", 
            predSE := predict(ageDiffLMList$`1`, type = "response", se = TRUE)["se.fit"]]
}


plotTest1 <- ggplot(plotData2, aes(x = firePresAbs)) +
  geom_boxplot(aes(y = abs(ageDiffSimObs), fill = scenario)) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. differences from observed ages",
       y = expression(bgroup("|", "sim." - bar("obs."), "|")),
       x = "") +
  facet_wrap(~ speciesCode, labeller = labeller(speciesCode = speciesLabels))

plotTest1.2 <- ggplot(plotData2, aes(x = firePresAbs)) +
  geom_boxplot(aes(y = abs(ageDiffSimObs), fill = scenario)) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. differences from observed ages",
       y = expression(bgroup("|", "sim." - bar("obs."), "|")),
       x = "")
```

```{r plot&savePlots, echo = FALSE}
plotSave <- ggarrange(plotTest1, 
                      plotTest1.2, common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20),
                      widths = c(1, 0.6))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest.tiff"),
       width = 14, height = 7)
rm(plotTest1)  ## plotTest1.2 is used again later
gc()
```

## SCENARIO LIKELIHOOD
!!! THIS IS WRONG - can't use likelihoods in this context, varying numbers of parameters
### Species B-weighted ages
```{r likelihoodAgeSpp, echo = FALSE, eval = FALSE}
spAgeSim <- allPixelCohortDataMnt[year == endYear & B > 0,  ## absences can't lower the average ages
                                  list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                       sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]

spAgeObs <- copy(ageDataCN[, .(Species, Reconstructed.age, firePresAbs)])
spAgeObs[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
spAgeObs[grepl("ABLA", Species), speciesCode := "Abie_sp"]
spAgeObs[grepl("PIEN", Species), speciesCode := "Pice_eng"]
spAgeObs[grepl("PICO", Species), speciesCode := "Pinu_sp"]
spAgeObs[grepl("PSME", Species), speciesCode := "Pseu_men"]
spAgeObs <- spAgeObs[!is.na(speciesCode)]

## calculate log sim age 
if (any(spAgeSim$AgeBySppWeighted == 0) | any(spAgeObs$Reconstructed.age == 0)) {
  warnings("there are zero ages, which can't be logged. Removing ages = 0 ")
  spAgeSim <- spAgeSim[AgeBySppWeighted > 0]
  spAgeObs <- spAgeObs[Reconstructed.age > 0]
}

spAgeSim[, logAgeBySppWeighted := log(AgeBySppWeighted)]

## calculate log obs age and mean/sd
obslogMeanSD <- cbind(spAgeObs, data.table(logReconstructed.age = log(spAgeObs$Reconstructed.age)))
obslogMeanSD <- obslogMeanSD[, list(mean = mean(logReconstructed.age, na.rm = TRUE), 
                                    sd = sd(logReconstructed.age, na.rm = TRUE)),
                             by = .(speciesCode, firePresAbs)]

combos <- unique(spAgeSim[, .(scenario, rep, speciesCode, firePresAbs)])
negSumLogliks <- apply(as.data.frame(combos), 1, FUN = function(combo, spAgeSim, obslogMeanSD) {
  combo <- as.data.table(as.list(combo))
  cols <- c("rep", "firePresAbs")
  combo[, (cols) := lapply(.SD, as.numeric), .SDcols = cols] 
  
  ## subset data
  simData <- spAgeSim[combo, on = names(combo)]
  cols <- intersect(names(obslogMeanSD), names(combo))
  obsData <- obslogMeanSD[combo[, ..cols], on = cols]
  if (is.na(obsData$mean)) {
    message(paste("no observed data for:", paste(combo, collapse = " ")))
    return(cbind(combo, data.table(SNLL = NA)))
  } else {
    logLiks <- dlnorm(x = simData$logAgeBySppWeighted, meanlog = obsData$mean, sdlog = obsData$sd, log = TRUE)
    return(cbind(combo, data.table(SNLL = -sum(logLiks))))
  }
}, obslogMeanSD = obslogMeanSD, spAgeSim = spAgeSim)

SNLLAgeSp <- rbindlist(negSumLogliks)
SNLLAgeSp[, mean(SNLL, na.rm = TRUE), by = .(scenario)]
SNLLAgeSp[, mean(SNLL, na.rm = TRUE), by = .(speciesCode, scenario)]

```

### Forest type B-weighted ages
```{r likelihoodAgeVegTypeCN, echo = FALSE, eval = FALSE}
spAgeSim <- allPixelCohortDataMnt[year == endYear & B > 0,  ## absences can't lower the average ages
                                  list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                       sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, vegTypeCN)]

spAgeObs <- copy(ageDataCN[, .(Cover.dendro, Reconstructed.age, firePresAbs)])
setnames(spAgeObs, "Cover.dendro", "vegTypeCN")

## calculate log sim age 
if (any(spAgeSim$AgeBySppWeighted == 0) | any(spAgeObs$Reconstructed.age == 0)) {
  warnings("there are zero ages, which can't be logged. Removing ages = 0 ")
  spAgeSim <- spAgeSim[AgeBySppWeighted > 0]
  spAgeObs <- spAgeObs[Reconstructed.age > 0]
}

spAgeSim[, logAgeBySppWeighted := log(AgeBySppWeighted)]

## calculate log obs age and mean/sd
obslogMeanSD <- cbind(spAgeObs, data.table(logReconstructed.age = log(spAgeObs$Reconstructed.age)))
obslogMeanSD <- obslogMeanSD[, list(mean = mean(logReconstructed.age, na.rm = TRUE), 
                                    sd = sd(logReconstructed.age, na.rm = TRUE)),
                             by = .(vegTypeCN, firePresAbs)]

combos <- unique(spAgeSim[, .(scenario, rep, vegTypeCN, firePresAbs)])
negSumLogliks <- apply(as.data.frame(combos), 1, FUN = function(combo, spAgeSim, obslogMeanSD) {
  combo <- as.data.table(as.list(combo))
  cols <- c("rep", "firePresAbs")
  combo[, (cols) := lapply(.SD, as.numeric), .SDcols = cols] 
  
  ## subset data
  simData <- spAgeSim[combo, on = names(combo)]
  cols <- intersect(names(obslogMeanSD), names(combo))
  obsData <- obslogMeanSD[combo[, ..cols], on = cols]
  if (is.na(obsData$mean)) {
    message(paste("no observed data for:", paste(combo, collapse = " ")))
    return(cbind(combo, data.table(SNLL = NA)))
  } else {
    logLiks <- dlnorm(x = simData$logAgeBySppWeighted, meanlog = obsData$mean, sdlog = obsData$sd, log = TRUE)
    return(cbind(combo, data.table(SNLL = -sum(logLiks))))
  }
}, obslogMeanSD = obslogMeanSD, spAgeSim = spAgeSim)

SNLLAgeVegTypeCN <- rbindlist(negSumLogliks)
SNLLAgeVegTypeCN[, mean(SNLL, na.rm = TRUE), by = .(scenario)]
SNLLAgeVegTypeCN[, mean(SNLL, na.rm = TRUE), by = .(vegTypeCN, scenario)]
```

### Species no. cohorts
```{r likelihoodCohortsSpp, echo = FALSE, eval = FALSE}
spCohortSim <- allPixelCohortDataMnt[year == endYear & B > 0 & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                                     list(noCohorts = length(unique(age))),
                                     by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]

spCohortObs <- copy(ageDataCN[, .(Species, noCohorts, firePresAbs)])
spCohortObs[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
spCohortObs[grepl("ABLA", Species), speciesCode := "Abie_sp"]
spCohortObs[grepl("PIEN", Species), speciesCode := "Pice_eng"]
spCohortObs[grepl("PICO", Species), speciesCode := "Pinu_sp"]
spCohortObs[grepl("PSME", Species), speciesCode := "Pseu_men"]
spCohortObs <- spCohortObs[!is.na(speciesCode)]

## calculate log sim no Cohorts 
if (any(spCohortSim$noCohorts == 0) | any(spCohortObs$noCohorts == 0)) {
  warnings("there are zero noCohorts, which can't be logged. Removing noCohorts = 0 ")
  spCohortSim <- spCohortSim[noCohorts > 0]
  spCohortObs <- spCohortObs[noCohorts > 0]
}

spCohortSim[, logNoCohorts := log(noCohorts)]

## calculate log obs age and mean/sd
obslogMeanSD <- cbind(spCohortObs, data.table(logNoCohorts = log(spCohortObs$noCohorts)))
obslogMeanSD <- obslogMeanSD[, list(mean = mean(logNoCohorts, na.rm = TRUE), 
                                    sd = sd(logNoCohorts, na.rm = TRUE)),
                             by = .(speciesCode, firePresAbs)]

combos <- unique(spCohortSim[, .(scenario, rep, speciesCode, firePresAbs)])
negSumLogliks <- apply(as.data.frame(combos), 1, FUN = function(combo, spCohortSim, obslogMeanSD) {
  combo <- as.data.table(as.list(combo))
  cols <- c("rep", "firePresAbs")
  combo[, (cols) := lapply(.SD, as.numeric), .SDcols = cols] 
  
  ## subset data
  simData <- spCohortSim[combo, on = names(combo)]
  cols <- intersect(names(obslogMeanSD), names(combo))
  obsData <- obslogMeanSD[combo[, ..cols], on = cols]
  if (is.na(obsData$mean)) {
    message(paste("no observed data for:", paste(combo, collapse = " ")))
    return(cbind(combo, data.table(SNLL = NA)))
  } else {
    logLiks <- dlnorm(x = simData$logNoCohorts, meanlog = obsData$mean, sdlog = obsData$sd, log = TRUE)
    return(cbind(combo, data.table(SNLL = -sum(logLiks))))
  }
}, obslogMeanSD = obslogMeanSD, spCohortSim = spCohortSim)

SNLLCohortSp <- rbindlist(negSumLogliks)
SNLLCohortSp[, mean(SNLL, na.rm = TRUE), by = .(scenario)]
```

### Forest type no. cohorts
```{r likelihoodCohortsVegTypeCN, echo = FALSE, eval = FALSE}
spCohortSim <- allPixelCohortDataMnt[year == endYear & B > 0 & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                                     list(noCohorts = length(unique(age))),
                                     by = .(scenario, rep, pixelIndex, firePresAbs, vegTypeCN)]

spCohortObs <- copy(ageDataCN[, .(Cover.dendro, noCohorts, firePresAbs)])
setnames(spCohortObs, "Cover.dendro", "vegTypeCN")

## calculate log sim no Cohorts 
if (any(spCohortSim$noCohorts == 0) | any(spCohortObs$noCohorts == 0)) {
  warnings("there are zero noCohorts, which can't be logged. Removing noCohorts = 0 ")
  spCohortSim <- spCohortSim[noCohorts > 0]
  spCohortObs <- spCohortObs[noCohorts > 0]
}

spCohortSim[, logNoCohorts := log(noCohorts)]

## calculate log obs age and mean/sd
obslogMeanSD <- cbind(spCohortObs, data.table(logNoCohorts = log(spCohortObs$noCohorts)))
obslogMeanSD <- obslogMeanSD[, list(mean = mean(logNoCohorts, na.rm = TRUE), 
                                    sd = sd(logNoCohorts, na.rm = TRUE)),
                             by = .(vegTypeCN, firePresAbs)]

combos <- unique(spCohortSim[, .(scenario, rep, vegTypeCN, firePresAbs)])
negSumLogliks <- apply(as.data.frame(combos), 1, FUN = function(combo, spCohortSim, obslogMeanSD) {
  combo <- as.data.table(as.list(combo))
  cols <- c("rep", "firePresAbs")
  combo[, (cols) := lapply(.SD, as.numeric), .SDcols = cols] 
  
  ## subset data
  simData <- spCohortSim[combo, on = names(combo)]
  cols <- intersect(names(obslogMeanSD), names(combo))
  obsData <- obslogMeanSD[combo[, ..cols], on = cols]
  if (is.na(obsData$mean)) {
    message(paste("no observed data for:", paste(combo, collapse = " ")))
    return(cbind(combo, data.table(SNLL = NA)))
  } else {
    logLiks <- dlnorm(x = simData$logNoCohorts, meanlog = obsData$mean, sdlog = obsData$sd, log = TRUE)
    return(cbind(combo, data.table(SNLL = -sum(logLiks))))
  }
}, obslogMeanSD = obslogMeanSD, spCohortSim = spCohortSim)

SNLLCohortTypeCN <- rbindlist(negSumLogliks)
SNLLCohortTypeCN[, mean(SNLL, na.rm = TRUE), by = .(scenario)]
SNLLCohortTypeCN[, mean(SNLL, na.rm = TRUE), by = .(vegTypeCN, scenario)]
```

### Forest type mean fire interval
```{r likelihoodFIVegTypeCN, echo = FALSE, eval = FALSE}
spFISim <- summaryFireAttributes
spFIObs <- copy(ageDataCN[, .(Cover.dendro, mean.FI)])
setnames(spFIObs, "Cover.dendro", "vegTypeCN")

## calculate obs meanFI and mean/sd
obsMeanSD <- spFIObs[, list(mean = mean(mean.FI, na.rm = TRUE), 
                            sd = sd(mean.FI, na.rm = TRUE)),
                     by = .(vegTypeCN)]

combos <- unique(spFISim[, .(scenario, rep, vegTypeCN)])
negSumLogliks <- apply(as.data.frame(combos), 1, FUN = function(combo, spFISim, obsMeanSD) {
  combo <- as.data.table(as.list(combo))
  cols <- c("rep")
  combo[, (cols) := lapply(.SD, as.numeric), .SDcols = cols] 
  
  ## subset data
  simData <- spFISim[combo, on = names(combo)]
  cols <- intersect(names(obsMeanSD), names(combo))
  obsData <- obsMeanSD[combo[, ..cols], on = cols]
  if (is.na(obsData$mean)) {
    message(paste("no observed data for:", paste(combo, collapse = " ")))
    return(cbind(combo, data.table(SNLL = NA)))
  } else {
    logLiks <- dexp(x = simData$meanFreq, rate = obsData$mean, log = TRUE)
    return(cbind(combo, data.table(SNLL = -sum(logLiks))))
  }
}, obsMeanSD = obsMeanSD, spFISim = spFISim)

SNLLFITypeCN <- rbindlist(negSumLogliks)
SNLLFITypeCN[, mean(SNLL, na.rm = TRUE), by = .(scenario)]
SNLLFITypeCN[, mean(SNLL, na.rm = TRUE), by = .(vegTypeCN, scenario)]
```

## SCENARIO EFFECTS ON STAND AGE, ALPHA DIVERSITY AND BETA DIVERSITY
### Across the landscape in pixels with/without fire
```{r age_scenario}
## SCENARIO EFFECTS ON STAND AGE------
## scenario effects on stand age across landscape
plotData <- allPixelCohortDataMnt[year == endYear,
                                  list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                       sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]

plotData[, firePresAbs := as.factor(firePresAbs)]
plotData[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData <- plotData[!is.na(ecoregionGroup) & !is.na(AgeBySppWeighted)]

## some ecoregionGroups only have one observation, leading to signular fit
ageEffectsLMList <- lapply(split(plotData, by = "firePresAbs"), function(DT) {
  lmer(AgeBySppWeighted ~ scenario + (scenario | ecoregionGroup), data = DT)
})
print("No fire")
summary(ageEffectsLMList$`0`)

print("Fire")
summary(ageEffectsLMList$`1`)

## fitted values vector is shorter than nrow, prob. due to signularity. predict using the same data.
plotData[firePresAbs == 0, predVals := predict(ageEffectsLMList$`0`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 0])]
plotData[firePresAbs == 1, predVals := predict(ageEffectsLMList$`1`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 1])]

plotTest2 <- ggplot(plotData) +
  geom_boxplot(aes(x = firePresAbs, y = AgeBySppWeighted, fill = scenario)) +
  geom_point(aes(x = firePresAbs, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_color_manual(values = c("red", "red")) +
  scale_fill_discrete(labels = scenLabels) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(y = "biomass-weighted age", x = "")
```

```{r alphaDiv_scenario}
## SCENARIO EFFECTS ON ALPHA DIVERSITY ------------------
## scenario effects on alpha-div across landscape
## inverse Simpson concentration (Whittaker 1972)
plotData <- allPixelCohortDataMnt[year == endYear]
plotData[, sumB := sum(B, na.rm = TRUE),
         by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, pixelIndex, speciesCode, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]

plotData[, firePresAbs := as.factor(firePresAbs)]
plotData[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData <- plotData[!is.na(ecoregionGroup) & !is.na(alphaDiv)]

## some ecoregionGroups only have one observation, leading to signular fit
alphaEffectsLMList <- lapply(split(plotData, by = "firePresAbs"), function(DT) {
  lmer(alphaDiv ~ scenario + (scenario | ecoregionGroup), data = DT)
})
summary(alphaEffectsLMList$`1`)

## fitted values vector is shorter than nrow, prob. due to signularity. predict using the same data.
plotData[firePresAbs == 0, predVals := predict(alphaEffectsLMList$`0`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 0])]
plotData[firePresAbs == 1, predVals := predict(alphaEffectsLMList$`1`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 1])]

plotTest3 <- ggplot(plotData) +
  geom_boxplot(aes(x = firePresAbs, y = alphaDiv, fill = scenario)) +
  geom_point(aes(x = firePresAbs, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_color_manual(values = c("red", "red")) +
  scale_fill_discrete(labels = scenLabels) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(y = "alpha-div.", x = "")
```

```{r betaDiv_scenario}
## SCENARIO EFFECTS ON BETA DIVERSITY ------------------
## scenario effects on beta-div across landscape - with fire vs. no fire
## from multiplicative decomposition where both alpha
## and gamma diversity are inverse Simpson concentration (Whittaker 1972)
# alpha-div
plotData <- allPixelCohortDataMnt[year == endYear]
plotData[, sumB := sum(B, na.rm = TRUE),
         by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, pixelIndex, speciesCode, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]

## gamma-div
plotData2 <- allPixelCohortDataMnt[year == endYear,
                                   list(BiomassBySpecies = sum(B, na.rm = TRUE)),
                                   by = .(scenario, rep, firePresAbs, speciesCode, ecoregionGroup)]
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, firePresAbs, ecoregionGroup)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, firePresAbs, speciesCode, ecoregionGroup)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, firePresAbs, ecoregionGroup)]

## beta-div
plotData2 <- plotData2[plotData, on = .(scenario, rep, firePresAbs, ecoregionGroup)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, firePresAbs, ecoregionGroup)]

plotData2[, firePresAbs := as.factor(firePresAbs)]
plotData2[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData2 <- unique(plotData2[!is.na(ecoregionGroup) & !is.na(betaDiv)])

## some ecoregionGroups only have one observation, leading to signular fit
betaEffectsLMList <- lapply(split(plotData2, by = "firePresAbs"), function(DT) {
  lmer(betaDiv ~ scenario + (1|ecoregionGroup), data = DT)
})
summary(betaEffectsLMList$`1`)

## fitted values vector is shorter than nrow, prob. due to signularity. predict using the same data.
plotData2[firePresAbs == 0, predVals := predict(betaEffectsLMList$`0`, type = "response",
                                                re.form = NA,
                                                newdata = plotData2[firePresAbs == 0])]
plotData2[firePresAbs == 1, predVals := predict(betaEffectsLMList$`1`, type = "response",
                                                re.form = NA,
                                                newdata = plotData2[firePresAbs == 1])]

plotTest4 <- ggplot(plotData2) +
  geom_boxplot(aes(x = firePresAbs, y = betaDiv, fill = scenario)) +
  geom_point(aes(x = firePresAbs, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_color_manual(values = c("red", "red")) +
  scale_fill_discrete(labels = scenLabels) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(y = "beta-div.", x = "")

plotTest4
```

```{r betaDiv_scenario2}
## scenario effects on beta-div across landscape - regardless of fire presence
## from multiplicative decomposition where both alpha
## and gamma diversity are inverse Simpson concentration (Whittaker 1972)
# alpha-div
plotData <- allPixelCohortDataMnt[year == endYear]
plotData[, sumB := sum(B, na.rm = TRUE),
         by = .(scenario, rep, pixelIndex, ecoregionGroup)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, pixelIndex, speciesCode, ecoregionGroup)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, pixelIndex, ecoregionGroup)]

## gamma-div
plotData2 <- allPixelCohortDataMnt[year == endYear,
                                   list(BiomassBySpecies = sum(B, na.rm = TRUE)),
                                   by = .(scenario, rep, speciesCode, ecoregionGroup)]
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, ecoregionGroup)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, speciesCode, ecoregionGroup)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, ecoregionGroup)]

## beta-div
plotData2 <- plotData2[plotData, on = .(scenario, rep, ecoregionGroup)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, ecoregionGroup)]

plotData2[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData2 <- unique(plotData2[!is.na(ecoregionGroup) & !is.na(betaDiv)])

## some ecoregionGroups only have one observation, leading to signular fit
betaEffectsLMList2 <- lmer(betaDiv ~ scenario + (1|ecoregionGroup), data = plotData2)
## no effect - pixels wihout fire dampen the response.
plotData2[, predVals := predict(betaEffectsLMList2, type = "response", re.form = NA)]

plotTest5 <- ggplot(plotData2) +
  geom_boxplot(aes(x = scenario, y = betaDiv, fill = scenario)) +
  geom_point(aes(x = scenario, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_fill_discrete(labels = scenLabels) +
  scale_x_discrete(labels = scenLabels) +
  scale_color_manual(values = c("red", "red")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(y = "beta-div.", x = "")
```

```{r plot&savePlots2, echo = FALSE}
plotSave <- ggarrange(plotTest2 + theme(legend.position = "none"),
                      plotTest3 + theme(legend.position = "none"),
                      plotTest5 + theme(legend.position = "none"),
                      get_legend(plotTest2 + theme(legend.key.size = unit(1.5, "cm"))),
                      ncol = 2, nrow = 2,
                      labels = c("a", "b", "c", ""), font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageAlphaBetaDivEffectsTest.tiff"),
       width = 12, height = 7)
rm(plotTest2, plotTest3, plotTest5)
gc()
```

```{r modelSave, include = FALSE}
## save models:
saveRDS(ageDiffLMList, file = file.path(simPaths$outputPath, "ageDiffModel.rds"))
saveRDS(ageEffectsLMList, file = file.path(simPaths$outputPath, "ageEffectsModel.rds"))
saveRDS(alphaEffectsLMList, file = file.path(simPaths$outputPath, "alphaEffectsModel.rds"))
saveRDS(betaEffectsLMList, file = file.path(simPaths$outputPath, "betaEffectsModel.rds"))
saveRDS(betaEffectsLMList2, file = file.path(simPaths$outputPath, "betaEffectsModel2.rds"))
```

## BIOMASS, MORTALITY, AVG. AGE AND NO COHORTS BY SPECIES
```{r plotsBySpecies, cache = FALSE}
## PLOTS -----------------------------------------------
## MODELLED PROPERTIES ---------------------------------
## BY SPECIES ------------
## total biomass
plotData <- summaryBurnCohortDataSpp[, list(BiomassBySpecies = sum(BiomassBySpecies)),
                                     by = .(scenario, year, rep, speciesCode, firePresAbs)]
plot1 <- ggplot(data = plotData,
                aes(x = year, y = log(BiomassBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape biomass", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot2 <- ggplot(data = summaryBurnCohortDataSpp,
                aes(x = year, y = log(BiomassBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape biomass", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## total mortality
plotData <- summaryBurnCohortDataSpp[, list(MortalityBySpecies = sum(MortalityBySpecies)),
                                     by = .(scenario, year, rep, speciesCode, firePresAbs)]
plot3 <- ggplot(data = plotData,
                aes(x = year, y = log(MortalityBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape mortality", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot4 <- ggplot(data = summaryBurnCohortDataSpp,
                aes(x = year, y = log(MortalityBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape mortality", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))
amc::.gc()

## average age
plotData <- allPixelCohortDataMnt[, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                         sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, year, rep, firePresAbs, speciesCode)]
plot5 <- ggplot(data = plotData,
                aes(x = year, y = AgeBySppWeighted, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by species") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot6 <- ggplot(data = summaryBurnCohortDataSpp,
                aes(x = year, y = AgeBySppWeighted, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## no. cohorts
plotData <- allPixelCohortDataMnt[B > 0, list(noCohorts = length(unique(age))),
                                  by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, speciesCode)]
plot7 <- ggplot(data = plotData,
                aes(x = year, y = noCohorts, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts",
       subtitle = "by species") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot8 <- ggplot(data = plotData,
                aes(x = year, y = noCohorts, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts",
       subtitle = "by species") +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

amc::.gc()
```

```{r plot&savePlots3, echo = FALSE}
## biomass
plotSave <- ggarrange(plot1,
                      plot2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeB.tiff"),
       width = 14, height = 7)

## age
plotSave <- ggarrange(plot5,
                      plot6 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAge.tiff"),
       width = 14, height = 7)

## no. cohorts:
plotSave <- ggarrange(plot7 + theme(plot.subtitle = element_blank()),
                      plot8 +
                        theme(plot.subtitle = element_blank(),
                              axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_noCohorts.tiff"),
       width = 14, height = 7)
rm(plot1, plot2, plot5, plot6, plot7, plot8)
gc()
```

## BIOMASS, MORTALITY, AVG. AGE AND NO COHORTS BY VEG TYPE (dom species)
```{r plotsByDomSpecies, cache = FALSE}
## BY FOREST TYPE (DOMINANT SPECIES) ------------
## no. pixels
plotData <- allPixelCohortDataMnt[, list(noPixelsVeg = length(unique(pixelIndex))),
                                  by = .(scenario, year, rep, firePresAbs, vegType)]
## add 0s to missing veg types in a year
plotData <- plotData %>%
  tidyr::pivot_wider(names_from = vegType, values_from = noPixelsVeg,
                     values_fill = list(noPixelsVeg = 0)) %>%
  as.data.table(.) %>%
  melt(., id.vars = c("scenario", "year", "rep", "firePresAbs"),
       variable.name = "vegType", value.name = "noPixelsVeg")

plot9 <- ggplot(data = plotData,
                aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "stack") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Abundance of cover type", y = "no. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot9.2 <- ggplot(data = plotData,
                  aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "fill") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Cover type abundance", y = "prop. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))
amc::.gc()

plotData <- allPixelCohortDataMnt[, list(noPixelsVeg = length(unique(pixelIndex))),
                                  by = .(scenario, year, rep, noFires, vegType)]
## add 0s to missing veg types in a year
plotData <- plotData %>%
  tidyr::pivot_wider(names_from = vegType, values_from = noPixelsVeg,
                     values_fill = list(noPixelsVeg = 0)) %>%
  as.data.table(.) %>%
  melt(., id.vars = c("scenario", "year", "rep", "noFires"),
       variable.name = "vegType", value.name = "noPixelsVeg")

plot10 <- ggplot(data = plotData,
                 aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "stack") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Cover type abundance", y = "no. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

plot10.2 <- ggplot(data = plotData,
                   aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "fill") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Cover type abundance", y = "prop. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## no. cohorts
plotData <- allPixelCohortDataMnt[B > 0, list(noCohorts = length(unique(age))),
                                  by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, vegType)]
plot11 <- ggplot(data = plotData,
                 aes(x = year, y = noCohorts, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. no. cohorts in a stand", y = "no. cohorts",
       subtitle = "by dom. species cover type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot12 <- ggplot(data = plotData,
                 aes(x = year, y = noCohorts, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. no. cohorts in a stand", y = "no. cohorts",
       subtitle = "by dom. species cover type") +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## total biomass
plotData <- summaryBurnCohortDataVegType[, list(BiomassByVegType = sum(BiomassByVegType)),
                                         by = .(scenario, year, rep, vegType, firePresAbs)]
plot13 <- ggplot(data = plotData,
                 aes(x = year, y = log(BiomassByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot14 <- ggplot(data = summaryBurnCohortDataVegType,
                 aes(x = year, y = log(BiomassByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))


plot14 <- ggplot(data = summaryBurnCohortDataVegType,
                 aes(x = year, y = log(BiomassByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))


## total mortality
plotData <- summaryBurnCohortDataVegType[, list(MortalityByVegType = sum(MortalityByVegType)),
                                         by = .(scenario, year, rep, vegType, firePresAbs)]
plot15 <- ggplot(data = plotData,
                 aes(x = year, y = log(MortalityByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total mortality", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot16 <- ggplot(data = summaryBurnCohortDataVegType,
                 aes(x = year, y = log(MortalityByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total mortality", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## average age
plotData <- allPixelCohortDataMnt[, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                         sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, year, rep, firePresAbs, vegType)]

plot17 <- ggplot(data = plotData,
                 aes(x = year, y = AgeBySppWeighted, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by dominant species cover type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot18 <- ggplot(data = summaryBurnCohortDataVegType,
                 aes(x = year, y = AgeBySppWeighted, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by dominant species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))
amc::.gc()
```

```{r plot&savePlots4, echo = FALSE}
## biomass
plotSave <- ggarrange(plot13 + theme(plot.title = element_text(size = 17)),
                      plot14 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeBVegType.tiff"),
       width = 14, height = 7)

## age
plotSave <- ggarrange(plot17,
                      plot18 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAgeVegType.tiff"),
       width = 14, height = 7)

## veg type abundance 
plotSave <- ggarrange(plot9.2,
                      plot10.2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = ""),
                      widths = c(0.4, 0.7), labels = "auto", font.label = list(size = 20),
                      legend = "bottom", common.legend = TRUE)
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeVegTypes.tiff"),
       width = 14, height = 7)

## no. cohorts
plotSave <- ggarrange(plot11,
                      plot12 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_noCohortsVegType.tiff"),
       width = 14, height = 7)

rm(plot13, plot14, plot17, plot18, plot9.2, plot10.2, plot11, plot12)
gc()
```

## BIOMASS, MORTALITY, AVG. AGE AND NO COHORTS BY FUNCTIONAL VEG TYPE (Cameron's veg types)
For biomass, mortality, age and no. cohorts forest types are defined at the last year of the simulation and pixels are kept constant.
```{r plotsByFunctVegType, cache = FALSE}
## BY CAMERON'S VEG TYPE ------------
## no. pixels
plotData <- allPixelCohortDataMnt[, list(noPixelsVeg = length(unique(pixelIndex))),
                                  by = .(scenario, year, rep, firePresAbs, vegTypeCN)]
## add 0s to missing veg types in a year
plotData <- plotData %>%
  tidyr::pivot_wider(names_from = vegTypeCN, values_from = noPixelsVeg,
                     values_fill = list(noPixelsVeg = 0)) %>%
  as.data.table(.) %>%
  melt(., id.vars = c("scenario", "year", "rep", "firePresAbs"),
       variable.name = "vegTypeCN", value.name = "noPixelsVeg")

plot19 <- ggplot(data = plotData,
                 aes(x = year, y = noPixelsVeg, fill = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "area", position = "stack") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Cover type abundance", y = "no. pixels",
       subtitle = "(forest type)") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot19.2 <- ggplot(data = plotData,
                   aes(x = year, y = noPixelsVeg, fill = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "area", position = "fill") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Cover type abundance", y = "prop. pixels",
       subtitle = "(forest type)") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))
amc::.gc()

plotData <- allPixelCohortDataMnt[, list(noPixelsVeg = length(unique(pixelIndex))),
                                  by = .(scenario, year, rep, noFires, vegTypeCN)]
## add 0s to missing veg types in a year
plotData <- plotData %>%
  tidyr::pivot_wider(names_from = vegTypeCN, values_from = noPixelsVeg,
                     values_fill = list(noPixelsVeg = 0)) %>%
  as.data.table(.) %>%
  melt(., id.vars = c("scenario", "year", "rep", "noFires"),
       variable.name = "vegTypeCN", value.name = "noPixelsVeg")

plot20 <- ggplot(data = plotData,
                 aes(x = year, y = noPixelsVeg, fill = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "area", position = "stack") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Cover type abundance", y = "no. pixels",
       subtitle = "(forest type)") +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

plot20.2 <- ggplot(data = plotData,
                   aes(x = year, y = noPixelsVeg, fill = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "area", position = "fill") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Cover type abundance", y = "prop. pixels",
       subtitle = "(forest type)") +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## no. cohorts
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  
plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[B > 0, list(noCohorts = length(unique(age))),
                     by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, vegTypeCN)]
plot21 <- ggplot(plotData,
                 aes(x = year, y = noCohorts, colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts",
       subtitle = "by forest type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot22 <- ggplot(data = plotData,
                 aes(x = year, y = noCohorts, colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts",
       subtitle = "by forest type") +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## total biomass
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[, BiomassByVegType := sum(B),
                     by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, vegTypeCN)]
plotData <- plotData[, list(BiomassByVegType = sum(BiomassByVegType)),
                     by = .(scenario, year, rep, vegTypeCN, firePresAbs)]
plot23 <- ggplot(data = plotData[vegTypeCN != "No veg."],
                 aes(x = year, y = log(BiomassByVegType + 0.000001), colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by forest type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

## total biomass BY pixel (not summed, but averaged across the landscape)
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData[, sumB := sum(B, na.rm = TRUE), by = .(scenario, rep, year, pixelIndex)]
plotData <- plotData[vegTypeCN != "No veg.", list(avgSumB = mean(sumB, na.rm = TRUE)),
                     by = .(scenario, rep, year, vegTypeCN, firePresAbs)]
plot23.2 <- ggplot(data = plotData,
                   aes(x = year, y = log(avgSumB + 0.000001), colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by forest type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[, BiomassByVegType := sum(B),
                     by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, vegTypeCN)]
plotData <- plotData[, list(BiomassByVegType = sum(BiomassByVegType)),
                     by = .(scenario, year, rep, vegTypeCN, noFires)]

plot24 <- ggplot(data = plotData[vegTypeCN != "No veg."],
                 aes(x = year, y = log(BiomassByVegType + 0.000001), colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by forest type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  
plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData[, sumB := sum(B, na.rm = TRUE), by = .(scenario, rep, year, pixelIndex)]
plotData <- plotData[vegTypeCN != "No veg.", list(avgSumB = mean(sumB)),
                     by = .(scenario, rep, year, vegTypeCN, noFires)]
plot24.2 <- ggplot(data = plotData,
                   aes(x = year, y = log(avgSumB + 0.000001), colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by forest type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## total mortality
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[, MortalityByVegType := sum(mortality),
                     by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, vegTypeCN)]
plotData <- plotData[, list(MortalityByVegType = sum(MortalityByVegType)),
                     by = .(scenario, year, rep, vegTypeCN, firePresAbs)]

plot25 <- ggplot(data = plotData[vegTypeCN != "No veg."],
                 aes(x = year, y = log(MortalityByVegType + 0.000001), colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Total mortality", y = "log-biomass (ton/ha)",
       subtitle = "by forest type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[, MortalityByVegType := sum(mortality),
                     by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, vegTypeCN)]
plotData <- plotData[, list(MortalityByVegType = sum(MortalityByVegType)),
                     by = .(scenario, year, rep, vegTypeCN, noFires)]
plot26 <- ggplot(data = plotData[vegTypeCN != "No veg."],
                 aes(x = year, y = log(MortalityByVegType + 0.000001), colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Total mortality", y = "log-biomass (ton/ha)",
       subtitle = "by forest type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))

## average age
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                            sum((B/100), na.rm = TRUE))),
                     by = .(scenario, year, rep, firePresAbs, vegTypeCN)]
plot27 <- ggplot(data = plotData,
                 aes(x = year, y = AgeBySppWeighted, colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by forest type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                            sum((B/100), na.rm = TRUE))),
                     by = .(scenario, year, rep, noFires, vegTypeCN)]
plot28 <- ggplot(data = plotData,
                 aes(x = year, y = AgeBySppWeighted, colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by forest type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires, labeller = labeller(scenario = scenLabels))
```

```{r plot&savePlots5, echo = FALSE}
## biomass
plotSave <- ggarrange(plot23,
                      plot24 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_landscapeBVegTypeCN.tiff"),
       width = 14, height = 7)

## biomass
plotSave <- ggarrange(plot23.2,
                      plot24.2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_pixelBVegTypeCN.tiff"),
       width = 14, height = 7)
## age
plotSave <- ggarrange(plot27,
                      plot28 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_landscapeAgeVegTypeCN.tiff"),
       width = 14, height = 7)

## veg type abundance 
plotSave <- ggarrange(plot19.2,
                      plot20.2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeVegTypesCN.tiff"),
       width = 14, height = 7)

## no. cohorts
plotSave <- ggarrange(plot21,
                      plot22 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_noCohortsVegTypeCN.tiff"),
       width = 14, height = 7)

rm(plot23, plot24, plot27, plot28, plot19.2, plot20.2, plot21, plot22)
gc()
```

## SPECIES RELATIVE ABUNDANCE AND AVG. AGE AND NO COHORTS BY SPECIES WITHIN VEG TYPE
Averaged across pixels, burnt and unburnt. Forest types are defined at the last year of the simulation and pixels are kept constant.
```{r relB_plotsBySpecies, cache = FALSE}
## PLOTS -----------------------------------------------
## MODELLED PROPERTIES ---------------------------------
## BY SPECIES ------------
## sum biomass by spp within pixel, then average
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  
plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]

plotData <- plotData[, list(BiomassBySpecies = as.numeric(sum(B/100, na.rm = TRUE)),
                            AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                            sum((B/100), na.rm = TRUE))),
                     by = .(scenario, year, rep, pixelIndex, vegTypeCN, speciesCode)]
plotData <- plotData[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
                     by = .(scenario, year, rep, pixelIndex)]
plotData <- plotData[, relBBySpecies := BiomassBySpecies/sumB]
plotData2 <- plotData[, list(relBBySpecies = mean(relBBySpecies, na.rm = TRUE),
                             AgeBySppWeighted = mean(AgeBySppWeighted, na.rm = TRUE)),
                      by = .(scenario, year, rep, vegTypeCN, speciesCode)]
plotData2 <- rbind(plotData2,
                   plotData[, list(relBBySpecies = mean(relBBySpecies, na.rm = TRUE),
                                   AgeBySppWeighted = mean(AgeBySppWeighted, na.rm = TRUE),
                                   vegTypeCN = "landscape"),
                            by = .(scenario, year, rep, speciesCode)])


plot1.2 <- ggplot(data = plotData2,
                  aes(x = year, y = relBBySpecies, linetype = scenario, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_linetype_manual(values = scenLinetype,
                        labels = scenLabels) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Relative species abundance", y = "Average relative abundance\n(per pixel)") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_wrap( ~ vegTypeCN, nrow = 2,
              labeller = labeller(vegTypeCN = vegTypeCNLabels))

## average age
plot5.2 <- ggplot(data = plotData2,
                  aes(x = year, y = AgeBySppWeighted, linetype = scenario, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  scale_linetype_manual(values = scenLinetype,
                        labels = scenLabels) +
  labs(title = "Average species age", y = "biomass-weighted age") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_wrap( ~ vegTypeCN, nrow = 2,
              labeller = labeller(vegTypeCN = vegTypeCNLabels))
amc::.gc()
```

```{r plot&savePlots6, echo = FALSE}
## biomass
plotSave <- ggarrange(plot1.2,
                      plot5.2,
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_meanRelB_Age_sppVegTypeCN.tiff"),
       width = 18, height = 8)

```

## COMPARING SIMULATED AND OBSERVED DATA
### Age means CIs - by species
```{r simVsObsAges, cache = FALSE}
## SIMULATED VS. OBSERVED DATA ------------
## age distribution at end of simulation vs cameron's

## pixel-level differences from observed mean
plotData <- allPixelCohortDataMnt[year == endYear & B > 0,  ## absences can't lower the average ages
                                  list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                       sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]

plotData2 <- copy(ageDataCN[, .(Species, Reconstructed.age, firePresAbs)])
plotData2[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
plotData2[grepl("ABLA", Species), speciesCode := "Abie_sp"]
plotData2[grepl("PIEN", Species), speciesCode := "Pice_eng"]
plotData2[grepl("PICO", Species), speciesCode := "Pinu_sp"]
plotData2[grepl("PSME", Species), speciesCode := "Pseu_men"]
plotData2 <- plotData2[!is.na(speciesCode)]

## make sure the data used here is the same in the MAD calculations
plotData <- plotData2[, list(avgAgeBySppObs = mean(Reconstructed.age, na.rm = TRUE)), 
                      by = .(speciesCode, firePresAbs)][plotData, on = .(speciesCode, firePresAbs)]
plotData[, firePresAbs := as.factor(firePresAbs)]
plotData[, ageDiffSimObs := AgeBySppWeighted - avgAgeBySppObs]
plotData <- plotData[!is.na(ageDiffSimObs)]

plot29 <- ggplot() +
  geom_violin(data = plotData,
              mapping = aes(x = speciesCode, y = AgeBySppWeighted, fill = scenario, colour = scenario),
              alpha = 0.3, position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData,
               mapping = aes(x = speciesCode, y = AgeBySppWeighted, colour = scenario),
               fun.data = "mean_cl_boot", 
               position = position_dodge(width = 0.9)) +
  geom_violin(data = plotData2,
              mapping = aes(x = speciesCode, y = Reconstructed.age, colour = "observed", fill = "observed"),
              alpha = 0.3) +
  stat_summary(data = plotData2,
               aes(x = speciesCode, y = Reconstructed.age, colour = "observed"),
               fun.data = "mean_cl_boot") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = speciesLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed")) +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "by species") +
  facet_grid( ~ firePresAbs,
              labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire"))) 

plot30 <- ggplot() +
  geom_violin(data = plotData,
              mapping = aes(x = as.factor(firePresAbs), y = AgeBySppWeighted, fill = scenario, 
                            colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData,
               mapping = aes(x = as.factor(firePresAbs), y = AgeBySppWeighted, colour = scenario),
               fun.data = "mean_cl_boot", 
               position = position_dodge(width = 0.9)) +
  geom_violin(data = plotData2,
              mapping = aes(x = as.factor(firePresAbs), y = Reconstructed.age, fill = "observed", 
                            colour = "observed"),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData2,
               aes(x = as.factor(firePresAbs), y = Reconstructed.age, colour = "observed"),
               fun.data = "mean_cl_boot") +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed")) +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2], 
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "across species")


## only fire pixels, no means
plotData3 <- data.table(plotData2[firePresAbs == 1], scenario = "observed")
setnames(plotData3, "Reconstructed.age", "AgeBySppWeighted")
plotData3 <- rbind(plotData3, plotData[firePresAbs == 1], fill = TRUE, use.names = TRUE)
plot29.1 <- ggplot() +
  geom_violin(data = plotData3,
              mapping =  aes(x = speciesCode, y = AgeBySppWeighted,
                             fill = scenario, colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = speciesLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed"), guide = "none") +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "by species")

plot30.1 <- ggplot() +
  geom_violin(data = plotData3,
              mapping = aes(x = scenario, y = AgeBySppWeighted, fill = scenario, 
                            colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = scenLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed"), guide = "none") +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "across species")

```

```{r plot&savePlots7, echo = FALSE}
plotSave <- plot_grid(plot_grid(plot29 + theme(legend.position = "none"),
                                plot30 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObs.tiff"),
       width = 14, height = 7)

plotSave <- plot_grid(plot_grid(plot29.1 + theme(legend.position = "none"),
                                plot30.1 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29.1 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObs2.tiff"),
       width = 14, height = 7)
```

### Age means CIs - by forest type
Forest types are defined at the LAST year of the simulation and pixels are kept constant.
Choosing the last year is more similar to what happens in the field.

```{r simVsObsAges_vegType, cache = FALSE}
## SIMULATED VS. OBSERVED DATA ------------
## age distribution at end of simulation vs cameron's
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(scenario, rep, vegTypeCN, pixelIndex)])

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[year == endYear & B > 0,  ## absences can't lower the average ages
                     list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                          sum((B/100), na.rm = TRUE))),
                     by = .(scenario, rep, pixelIndex, firePresAbs, vegTypeCN)]

plotData2 <- copy(ageDataCN[, .(Cover.dendro, Reconstructed.age, firePresAbs)])
setnames(plotData2, "Cover.dendro", "vegTypeCN")

## make sure the data used here is the same as in the MAD calculations
plotData <- plotData2[, list(avgAgeBySppObs = mean(Reconstructed.age, na.rm = TRUE)), 
                      by = .(vegTypeCN, firePresAbs)][plotData, on = .(vegTypeCN, firePresAbs)]
plotData[, firePresAbs := as.factor(firePresAbs)]
plotData[, ageDiffSimObs := AgeBySppWeighted - avgAgeBySppObs]
plotData <- plotData[!is.na(ageDiffSimObs)]

plot29.2 <- ggplot() +
  geom_violin(data = plotData,
              mapping = aes(x = vegTypeCN, y = AgeBySppWeighted, fill = scenario, 
                            colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData,
               mapping = aes(x = vegTypeCN, y = AgeBySppWeighted, colour = scenario),
               fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.9)) +
  geom_violin(data = plotData2,
              mapping = aes(x = vegTypeCN, y = Reconstructed.age, fill = "observed", 
                            colour = "observed"),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData2,
               aes(x = vegTypeCN, y = Reconstructed.age, colour = "observed"),
               fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.9)) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed")) +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "by forest type") +
  facet_grid( ~ firePresAbs,
              labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire"))) 

plot30.2 <- ggplot() +
  geom_violin(data = plotData,
              mapping = aes(x = as.factor(firePresAbs), y = AgeBySppWeighted, fill = scenario, 
                            colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData,
               mapping = aes(x = as.factor(firePresAbs), y = AgeBySppWeighted, colour = scenario),
               fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.9)) +
  geom_violin(data = plotData2,
              aes(x = as.factor(firePresAbs), y = Reconstructed.age, fill = "observed", 
                  colour = "observed"),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData2,
               aes(x = as.factor(firePresAbs), y = Reconstructed.age, colour = "observed"),
               fun.data = "mean_cl_boot") +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed")) +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "across forest type")


## only fire pixels, no means
plotData3 <- data.table(plotData2[firePresAbs == 1], scenario = "observed")
setnames(plotData3, "Reconstructed.age", "AgeBySppWeighted")
plotData3 <- rbind(plotData3, plotData[firePresAbs == 1], fill = TRUE, use.names = TRUE)
plot29.3 <- ggplot() +
  geom_violin(data = plotData3,
              mapping = aes(x = vegTypeCN, y = AgeBySppWeighted, fill = scenario, 
                            colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed"), guide = "none") +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "by forest type")

plot30.3 <- ggplot() +
  geom_violin(data = plotData3,
              mapping = aes(x = scenario, y = AgeBySppWeighted, fill = scenario, 
                            colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = scenLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed"), guide = "none") +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  labs(title = "Avg. age", y = "age", x = "",
       subtitle = "across forest type")
```

```{r plot&savePlots8, echo = FALSE}
plotSave <- plot_grid(plot_grid(plot29.2 + theme(legend.position = "none"),
                                plot30.2 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29.2 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_ageSimVsObsVegTypeCN.tiff"),
       width = 14, height = 7)

plotSave <- plot_grid(plot_grid(plot29.3 + theme(legend.position = "none"),
                                plot30.3 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29.3 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_ageSimVsObsVegTypeCN2.tiff"),
       width = 14, height = 7)
```

### No. cohorts means CIs by forest type
Forest types are defined at the LAST year of the simulation and pixels are kept constant.
Choosing the last year is more similar to what happens in the field.
```{r simVsObsCohorts, cache = FALSE}
## no. cohorts at end of simulation vs cameron's - subset to common veg types
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(scenario, rep, vegTypeCN, pixelIndex)])

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[year == endYear & B > 0 & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                     list(noCohorts = length(unique(age))),
                     by = .(scenario, rep, pixelIndex, firePresAbs, vegTypeCN)]
plot31 <- ggplot() +
  geom_violin(data = plotData,
              aes(x = vegTypeCN, y = noCohorts, fill = scenario, 
                  colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData,
               aes(x = vegTypeCN, y = noCohorts, colour = scenario), 
               fun.data = "mean_cl_boot", geom = "pointrange", 
               position = position_dodge(width = 0.9)) +
  geom_violin(data = ageDataCN,
              aes(x = Cover.dendro, y = noCohorts, fill = "observed", 
                  colour = "observed"),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = ageDataCN,
               aes(x = Cover.dendro, y = noCohorts, colour = "observed"),
               fun.data = "mean_cl_boot", geom = "pointrange",
               position = position_dodge(width = 0.9)) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed")) +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2], 
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts", x = "",
       subtitle = "by forest type") +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))
```

```{r plot&savePlots9, echo = FALSE}
plot31
ggsave(plot = plot31, filename = file.path(figOutputPath, "fixedPixels", "results_noCohortsSimVsObsVegTypeCN.tiff"),
       width = 14, height = 7)
```

### No. cohorts means CIs by species
```{r simVsObsCohorts_species, cache = FALSE}
## no. cohorts at end of simulation vs cameron's - subset to common veg types
plotData <- allPixelCohortDataMnt[year == endYear & B > 0 & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                                  list(noCohorts = length(unique(age))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]
plotData2 <- copy(ageDataCN[, .(Species, noCohorts, firePresAbs)])
plotData2[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
plotData2[grepl("ABLA", Species), speciesCode := "Abie_sp"]
plotData2[grepl("PIEN", Species), speciesCode := "Pice_eng"]
plotData2[grepl("PICO", Species), speciesCode := "Pinu_sp"]
plotData2[grepl("PSME", Species), speciesCode := "Pseu_men"]
plotData2 <- plotData2[!is.na(speciesCode)]

plot31.4 <- ggplot() +
  geom_violin(data = plotData,
              aes(x = speciesCode, y = noCohorts, fill = scenario, 
                  colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData,
               aes(x = speciesCode, y = noCohorts, colour = scenario), 
               fun.data = "mean_cl_boot", geom = "pointrange", 
               position = position_dodge(width = 0.9)) +
  geom_violin(data = plotData2,
              aes(x = speciesCode, y = noCohorts, fill = "observed", 
                  colour = "observed"),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData2,
               aes(x = speciesCode, y = noCohorts, colour = "observed"),
               fun.data = "mean_cl_boot", geom = "pointrange",
               position = position_dodge(width = 0.9)) +
  scale_x_discrete(labels = speciesLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2],
                                 "observed" = "grey50"),
                      labels = c(scenLabels, "observed" = "observed")) +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2], 
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts", x = "",
       subtitle = "by species") +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))
```

```{r plot&savePlots10, echo = FALSE}
plot31.4
ggsave(plot = plot31.4, filename = file.path(figOutputPath, "results_noCohortsSimVsObsSpecies.tiff"),
       width = 14, height = 7)
```

### Mean absolute deviation of simulated no. cohorts with respect to average observed no. cohorts for a given stand type
Forest types are defined at the LAST year of the simulation and pixels are kept constant.
Choosing the last year is more similar to what happens in the field.
```{r simVsObsCohortsDif, cache = FALSE}
## Cohorts mean absolute deviation 
## calculate the mean absolute deviation of each stand to the observed average (per veg type) across reps
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(scenario, rep, vegTypeCN, pixelIndex)])

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[year == endYear & B > 0 & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                     list(noCohorts = length(unique(age))),
                     by = .(scenario, rep, pixelIndex, firePresAbs, vegTypeCN)]
plotData2 <- ageDataCN[, list(avgNoCohortsObs = mean(noCohorts, na.rm = TRUE)),
                       by = .(Cover.dendro, firePresAbs)]
plotData <- plotData2[plotData, on = c("Cover.dendro==vegTypeCN", "firePresAbs")]
setnames(plotData, "Cover.dendro", "vegTypeCN")

plotData <- plotData[!is.na(avgNoCohortsObs) & !is.na(noCohorts)]
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(noCohorts - avgNoCohortsObs))),
                      by = .(scenario, rep, vegTypeCN, firePresAbs)]

## differences
plot31.2 <- ggplot(plotData,
                   aes(x = vegTypeCN,
                       y = noCohorts - avgNoCohortsObs,
                       fill = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  geom_violin() +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_fill_discrete(labels = scenLabels) +
  labs(title = "Avg differences from observed no. cohorts",
       y = expression("sim." - bar("obs.")), x = "") +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

## mean absolute deviation across reps
plot31.3 <- ggplot(plotData2,
                   aes(x = vegTypeCN, y = meanAbsDevSimObs,
                       colour = scenario)) +
  stat_summary(fun.data = "mean_sdl", position = position_dodge(width = 0.5)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_y_continuous(limits = c(0, max(plotData2$meanAbsDevSimObs))) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_colour_discrete(labels = scenLabels) +
  labs(title = "Mean abs. deviation from observed no. cohorts",
       y = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))), x = "") +
  coord_flip() +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))
```

```{r plot&savePlots11, echo = FALSE}
plot31.2
ggsave(plot = plot31.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "fixedPixels", "results_meanCohortDiffVegTypeCN.tiff"),
       width = 14, height = 7)
plot31.3
ggsave(plot = plot31.3 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "fixedPixels", "results_meanAbsCohortDevVegTypeCN.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(
  plot_grid(plot31 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot31.3 + theme(legend.position = "none", plot.title = element_blank()),
            nrow = 2, axis = "l", align = "v", rel_heights = c(1, 0.7),
            labels = "auto", label_size = 20),
  get_legend(plot31 + theme(legend.direction = "vertical")),
  nrow = 1, rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_noCohortsSimVsObsTest_MAD_VegTypeCN.tiff"),
       width = 10, height = 10)

rm(plot31.2, plot31.3)
gc()
```

### Mean absolute deviation of simulated no. cohorts with respect to average observed no. cohorts for a given species
```{r simVsObsCohortsDif_species, cache = FALSE}
## Cohorts mean absolute deviation 
## calculate the mean absolute deviation of each stand to the observed average (per veg type) across reps
plotData <- allPixelCohortDataMnt[year == endYear & B > 0 & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                                  list(noCohorts = length(unique(age))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]
plotData2 <- copy(ageDataCN[, .(Species, noCohorts, firePresAbs)])
plotData2[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
plotData2[grepl("ABLA", Species), speciesCode := "Abie_sp"]
plotData2[grepl("PIEN", Species), speciesCode := "Pice_eng"]
plotData2[grepl("PICO", Species), speciesCode := "Pinu_sp"]
plotData2[grepl("PSME", Species), speciesCode := "Pseu_men"]
plotData2 <- plotData2[!is.na(speciesCode)]
plotData2 <- plotData2[, list(avgNoCohortsObs = mean(noCohorts, na.rm = TRUE)),
                       by = .(speciesCode, firePresAbs)]
plotData <- plotData2[plotData, on = c("speciesCode", "firePresAbs")]
plotData <- plotData[!is.na(avgNoCohortsObs) & !is.na(noCohorts)]
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(noCohorts - mean(avgNoCohortsObs)), na.rm = TRUE)),
                      by = .(scenario, rep, speciesCode, firePresAbs)]

## differences
plot31.5 <- ggplot(plotData,
                   aes(x = speciesCode,
                       y = noCohorts - avgNoCohortsObs,
                       fill = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  geom_boxplot() +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = speciesLabels) +
  scale_fill_discrete(labels = scenLabels) +
  labs(title = "Avg differences from observed no. cohorts",
       y = expression("sim." - bar("obs.")), x = "") +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

## mean absolute deviation across reps
plot31.6 <- ggplot(plotData2,
                   aes(x = speciesCode, y = meanAbsDevSimObs,
                       colour = scenario)) +
  stat_summary(fun.data = "mean_sdl", position = position_dodge(width = 0.5)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_y_continuous(limits = c(0, max(plotData2$meanAbsDevSimObs))) +
  scale_colour_discrete(labels = scenLabels) +
  scale_x_discrete(labels = speciesLabels) +
  labs(title = "Mean abs. deviation from observed no. cohorts",
       y = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))), x = "") +
  coord_flip() +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))
```

```{r plot&savePlots12, echo = FALSE}
plot31.5
ggsave(plot = plot31.5 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanCohortDiffSpecies.tiff"),
       width = 14, height = 7)
plot31.6
ggsave(plot = plot31.6 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsCohortDevSpecies.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(
  plot_grid(plot31.4 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot31.6 + theme(legend.position = "none", plot.title = element_blank()),
            nrow = 2, axis = "l", align = "v", rel_heights = c(1, 0.7),
            labels = "auto", label_size = 20),
  get_legend(plot29 + theme(legend.direction = "vertical")),
  nrow = 1, rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_noCohortsSimVsObsTest_MAD_Species.tiff"),
       width = 10, height = 10)

gc()
```

### Mean absolute deviation simulated age with respect to average observed age for a given stand type
(typical MAD, and quantile deviations - 50, 75, 95%)
Forest types are defined at the LAST year of the simulation and pixels are kept constant.
```{r simVsObsAgesDif, cache = FALSE}
## mean age differences
## calculate avg weighted ages across observed stands first
## then the absolute difference of each stand to the observed average (per veg type) across reps
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(scenario, rep, vegTypeCN, pixelIndex)])

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData <- plotData[year == endYear & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                     list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                          sum((B/100), na.rm = TRUE))),
                     by = .(scenario, rep, pixelIndex, firePresAbs, vegTypeCN)]

plotData2 <- ageDataCN[, list(avgAgeBySppObs = mean(Reconstructed.age, na.rm = TRUE)),
                       by = .(Cover.dendro, firePresAbs)]
plotData <- plotData2[plotData, on = c("Cover.dendro==vegTypeCN", "firePresAbs")]
setnames(plotData, "Cover.dendro", "vegTypeCN")
plotData <- plotData[!is.na(avgAgeBySppObs) & !is.na(AgeBySppWeighted)]
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(AgeBySppWeighted - mean(avgAgeBySppObs)))),
                      by = .(scenario, rep, vegTypeCN, firePresAbs)]
plotData2 <- rbind(plotData2,
                   plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(AgeBySppWeighted - mean(avgAgeBySppObs))),
                                   vegTypeCN = "landscape"),
                            by = .(scenario, rep, firePresAbs)])

## differences
plot32 <- ggplot(plotData,
                 aes(x = vegTypeCN,
                     y = AgeBySppWeighted - avgAgeBySppObs,
                     fill = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  geom_boxplot() +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_fill_discrete(labels = scenLabels) +
  labs(title = "Avg. differences from observed ages",
       y = expression("sim." - bar("obs.")), x = "") +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

## mean absolute differences
plot32.2 <- ggplot(plotData2,
                   aes(x = vegTypeCN, y = meanAbsDevSimObs,
                       colour = scenario)) +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.5)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_y_continuous(limits = c(0, max(plotData2$meanAbsDevSimObs))) +
  scale_colour_discrete(labels = scenLabels) +
  scale_x_discrete(labels = vegTypeCNLabels, 
                   limits = unique(c("landscape", sort(unique(plotData2$vegTypeCN))))) +
  labs(title = "Mean abs. deviation from observed ages",
       y = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))), x = "") +
  coord_flip() +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))


## forest-type-level differences between simulated and observed upper quuantiles
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(scenario, rep, vegTypeCN, pixelIndex)])

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]

plotData <- plotData[year == endYear & B > 0,  ## absences can't lower the average ages
                     list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                          sum((B/100), na.rm = TRUE))),
                     by = .(scenario, rep, pixelIndex, firePresAbs, vegTypeCN)]
plotData <- plotData[, list(quant50AgeBySpp = quantile(AgeBySppWeighted, probs = 0.5, na.rm = TRUE),
                            quant75AgeBySpp = quantile(AgeBySppWeighted, probs = 0.75, na.rm = TRUE),
                            quant95AgeBySpp = quantile(AgeBySppWeighted, probs = 0.95, na.rm = TRUE)),
                     by = .(scenario, rep, firePresAbs, vegTypeCN)]

plotData2 <- ageDataCN[, list(quant50AgeBySppObs = quantile(Reconstructed.age, probs = 0.5, na.rm = TRUE),
                              quant75AgeBySppObs = quantile(Reconstructed.age, probs = 0.75, na.rm = TRUE),
                              quant95AgeBySppObs = quantile(Reconstructed.age, probs = 0.95, na.rm = TRUE)), 
                       by = .(Cover.dendro, firePresAbs)]
plotData <- plotData2[plotData, on = c("Cover.dendro==vegTypeCN", "firePresAbs")]
setnames(plotData, "Cover.dendro", "vegTypeCN")
plotData[, firePresAbs := as.factor(firePresAbs)]
plotData <- plotData[!is.na(quant50AgeBySppObs)]
if (any(is.na(plotData))) stop()

plotData2 <- plotData[, list(meanAbsDevSimObsQuant50 = 1/.N * sum(abs(quant50AgeBySpp - quant50AgeBySppObs)),
                             meanAbsDevSimObsQuant75 = 1/.N * sum(abs(quant75AgeBySpp - quant75AgeBySppObs)),
                             meanAbsDevSimObsQuant95 = 1/.N * sum(abs(quant95AgeBySpp - quant95AgeBySppObs))),
                      by = .(scenario, rep, vegTypeCN, firePresAbs)]
temp <- plotData[, list(meanAbsDevSimObsQuant50 = 1/.N * sum(abs(quant50AgeBySpp - quant50AgeBySppObs)),
                        meanAbsDevSimObsQuant75 = 1/.N * sum(abs(quant75AgeBySpp - quant75AgeBySppObs)),
                        meanAbsDevSimObsQuant95 = 1/.N * sum(abs(quant95AgeBySpp - quant95AgeBySppObs)),
                        vegTypeCN = "landscape"),
                 by = .(scenario, rep, firePresAbs)]
plotData2 <- rbind(plotData2, temp)
plotData2 <- melt(plotData2, id.vars = c("scenario", "rep", "vegTypeCN", "firePresAbs"))

plot32.3 <- ggplot(plotData2, 
                   aes(x = vegTypeCN, y = value, colour = variable, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               alpha = 0.7, fill = "white") +
  scale_color_viridis_d(option = "viridis", begin = 0.3, end = 0.8, 
                        labels = c("meanAbsDevSimObsQuant50" = "50%", 
                                   "meanAbsDevSimObsQuant75" = "75%", 
                                   "meanAbsDevSimObsQuant95" = "95%"),
                        name = "Quantile: ") +
  scale_x_discrete(labels = vegTypeCNLabels, 
                   limits = unique(c("landscape", sort(unique(plotData2$vegTypeCN)))),
                   expand = c(-0.2, 1.1)) +
  scale_shape_manual(labels = scenLabels, values = c("PM" = 24, "noPM" = 19)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Quantile absolute deviation", shape = "",
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|")), x = "") +
  coord_flip() +
  facet_wrap(~ firePresAbs, scales = "free_x", 
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## only pixels with fire
## order veg types, with landscape at the end
factorLevs <- c(as.character(sort(setdiff(unique(plotData2$vegTypeCN), "landscape"))), "landscape")
plotData2[, vegTypeCN := factor(vegTypeCN, levels = factorLevs)]

plot32.4 <- ggplot(plotData2[firePresAbs == "1"], 
                   aes(x = variable, y = value, colour = scenario, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               size = 1) +
  scale_x_discrete(labels = c("meanAbsDevSimObsQuant50" = "50%", 
                              "meanAbsDevSimObsQuant75" = "75%", 
                              "meanAbsDevSimObsQuant95" = "95%")) +
  scale_shape_discrete(labels = scenLabels, name = "") +
  scale_color_discrete(labels = scenLabels, name = "") +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(title = "Quantile absolute deviation", x = "", 
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|"))) +
  facet_wrap(~ vegTypeCN, scales = "free_x", ncol = 4,
             labeller = labeller(vegTypeCN = vegTypeCNLabels))

```

```{r plot&savePlots13, echo = FALSE}
plot32
ggsave(plot = plot32 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "fixedPixels", "results_meanAgeDiffVegTypeCN.tiff"),
       width = 14, height = 7)
plot32.2
ggsave(plot = plot32.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "fixedPixels", "results_meanAbsAgeDevVegTypeCN.tiff"),
       width = 10, height = 5)
plot32.3
ggsave(plot = plot32.3 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "fixedPixels", "results_MADquantVegTypeCNs.tiff"),
       width = 10, height = 6)

plotSave <- plot_grid(
  plot_grid(plot29.2 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.2 + theme(legend.position = "none", plot.title = element_blank()),
            nrow = 1, rel_widths = c(1, 0.7), axis = "b", align = "h",
            labels = "auto", label_size = 20),
  plot_grid(plot32.2 + theme(legend.position = "none", plot.title = element_blank()),
            get_legend(plot29.2 + theme(legend.direction = "vertical")),
            nrow = 1, rel_widths = c(1, 0.7), axis = "t", align = "v",
            labels = c("c", ""), label_size = 20),
  nrow = 2, rel_heights = c(1, 0.7), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_ageSimVsObsTest_MAD_VegTypeCN.tiff"),
       width = 12, height = 10)

plotSave <- plot_grid(
  plot_grid(plot29.2 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.2 + theme(legend.position = "bottom", plot.title = element_blank()),
            nrow = 1, 
            rel_widths = c(1, 0.7),
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot32.3 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_ageSimVsObsTest_MADquant_VegTypeCN.tiff"),
       width = 10, height = 10)

plotSave <- plot_grid(
  plot_grid(plot29.3 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.3 + theme(legend.position = "right", plot.title = element_blank(), plot.subtitle = element_blank()),
            nrow = 1, 
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot32.4 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "lr", align = "v")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_ageSimVsObsTest_MADquant_VegTypeCN2.tiff"),
       width = 10, height = 10)

gc()
```

### Mean absolute deviation simulated age with respect to average observed age for a given species
(typical MAD, and quantile deviations - 50, 75, 95%)
```{r simVsObsAgesDif2, cache = FALSE}
## mean age differences
## calculate avg weighted ages across observed stands first
## then the absolute difference of each stand to the observed average (per veg type) across reps
plotData <- allPixelCohortDataMnt[year == endYear & vegTypeCN %in% unique(ageDataCN$Cover.dendro),
                                  list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                       sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]

plotData2 <- copy(ageDataCN[, .(Species, Reconstructed.age, firePresAbs)])
plotData2[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
plotData2[grepl("ABLA", Species), speciesCode := "Abie_sp"]
plotData2[grepl("PIEN", Species), speciesCode := "Pice_eng"]
plotData2[grepl("PICO", Species), speciesCode := "Pinu_sp"]
plotData2[grepl("PSME", Species), speciesCode := "Pseu_men"]
plotData2 <- plotData2[!is.na(speciesCode)]
plotData2 <- plotData2[, list(avgAgeBySppObs = mean(Reconstructed.age, na.rm = TRUE)),
                       by = .(speciesCode, firePresAbs)]

plotData <- plotData2[plotData, on = .(speciesCode, firePresAbs)]
plotData <- plotData[!is.na(avgAgeBySppObs) & !is.na(AgeBySppWeighted)]
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(AgeBySppWeighted - mean(avgAgeBySppObs)))),
                      by = .(scenario, rep, speciesCode, firePresAbs)]

temp <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(AgeBySppWeighted - mean(avgAgeBySppObs))),
                        speciesCode = "landscape"),
                 by = .(scenario, rep, firePresAbs)]
plotData2 <- rbind(plotData2, temp)

## differences
plot43 <- ggplot(plotData,
                 aes(x = speciesCode,
                     y = AgeBySppWeighted - avgAgeBySppObs,
                     fill = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  geom_boxplot() +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  scale_x_discrete(labels = speciesLabels) +
  scale_fill_discrete(labels = scenLabels) +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. differences from observed ages",
       y = expression("sim." - bar("obs.")), x = "") +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

## mean absolute differences
plot43.2 <- ggplot(plotData2,
                   aes(x = speciesCode, y = meanAbsDevSimObs,
                       colour = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.5)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = c(speciesLabels, landscape = "landscape"), 
                   limits = c("landscape", names(speciesLabels))) +
  scale_colour_discrete(labels = scenLabels) +
  labs(title = "Mean abs. deviation from observed ages",
       y = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))), x = "") +
  coord_flip() +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))


## species-level differences between simulated and observed upper quuantiles
plotData <- allPixelCohortDataMnt[year == endYear & B > 0,  ## absences can't lower the average ages
                                  list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                       sum((B/100), na.rm = TRUE))),
                                  by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]
plotData <- plotData[, list(quant50AgeBySpp = quantile(AgeBySppWeighted, probs = 0.5, na.rm = TRUE),
                            quant75AgeBySpp = quantile(AgeBySppWeighted, probs = 0.75, na.rm = TRUE),
                            quant95AgeBySpp = quantile(AgeBySppWeighted, probs = 0.95, na.rm = TRUE)),
                     by = .(scenario, rep, firePresAbs, speciesCode)]

plotData2 <- copy(ageDataCN[, .(Species, Reconstructed.age, firePresAbs)])
plotData2[grepl("POBA|POTR", Species), speciesCode := "Popu_sp"]  ## collapse populus
plotData2[grepl("ABLA", Species), speciesCode := "Abie_sp"]
plotData2[grepl("PIEN", Species), speciesCode := "Pice_eng"]
plotData2[grepl("PICO", Species), speciesCode := "Pinu_sp"]
plotData2[grepl("PSME", Species), speciesCode := "Pseu_men"]
plotData2 <- plotData2[!is.na(speciesCode)]

plotData2 <- plotData2[, list(quant50AgeBySppObs = quantile(Reconstructed.age, probs = 0.5, na.rm = TRUE),
                              quant75AgeBySppObs = quantile(Reconstructed.age, probs = 0.75, na.rm = TRUE),
                              quant95AgeBySppObs = quantile(Reconstructed.age, probs = 0.95, na.rm = TRUE)), 
                       by = .(speciesCode, firePresAbs)]
plotData <- plotData2[plotData, on = .(speciesCode, firePresAbs)]
plotData[, firePresAbs := as.factor(firePresAbs)]
plotData <- plotData[!is.na(quant50AgeBySppObs)]
if (any(is.na(plotData))) stop()

plotData2 <- plotData[, list(meanAbsDevSimObsQuant50 = 1/.N * sum(abs(quant50AgeBySpp - quant50AgeBySppObs)),
                             meanAbsDevSimObsQuant75 = 1/.N * sum(abs(quant75AgeBySpp - quant75AgeBySppObs)),
                             meanAbsDevSimObsQuant95 = 1/.N * sum(abs(quant95AgeBySpp - quant95AgeBySppObs))),
                      by = .(scenario, rep, speciesCode, firePresAbs)]
temp <- plotData[, list(meanAbsDevSimObsQuant50 = 1/.N * sum(abs(quant50AgeBySpp - quant50AgeBySppObs)),
                        meanAbsDevSimObsQuant75 = 1/.N * sum(abs(quant75AgeBySpp - quant75AgeBySppObs)),
                        meanAbsDevSimObsQuant95 = 1/.N * sum(abs(quant95AgeBySpp - quant95AgeBySppObs)),
                        speciesCode = "landscape"),
                 by = .(scenario, rep, firePresAbs)]
plotData2 <- rbind(plotData2, temp)

plotData2 <- melt(plotData2, id.vars = c("scenario", "rep", "speciesCode", "firePresAbs"))

plot43.3 <- ggplot(plotData2, 
                   aes(x = speciesCode, y = value, colour = variable, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               alpha = 0.7, fill = "white") +
  scale_color_viridis_d(option = "viridis", begin = 0.3, end = 0.8, 
                        labels = c("meanAbsDevSimObsQuant50" = "50%", 
                                   "meanAbsDevSimObsQuant75" = "75%", 
                                   "meanAbsDevSimObsQuant95" = "95%"),
                        name = "Quantile: ") +
  scale_x_discrete(labels = speciesLabels,
                   limits = unique(c("landscape", sort(plotData2$speciesCode))),
                   expand = c(-0.2, 1.1)) +
  scale_shape_manual(labels = scenLabels, values = c("PM" = 24, "noPM" = 19)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Quantile absolute deviation", shape = "",
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|")), x = "") +
  coord_flip() +
  facet_wrap(~ firePresAbs, scales = "free_x", 
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## only pixels with fire
## order veg types, with landscape at the end
factorLevs <- c(as.character(sort(setdiff(unique(plotData2$speciesCode), "landscape"))), "landscape")
plotData2[, speciesCode := factor(speciesCode, levels = factorLevs)]

plot43.4 <- ggplot(plotData2[firePresAbs == "1"], 
                   aes(x = variable, y = value, colour = scenario, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               size = 1) +
  scale_x_discrete(labels = c("meanAbsDevSimObsQuant50" = "50%", 
                              "meanAbsDevSimObsQuant75" = "75%", 
                              "meanAbsDevSimObsQuant95" = "95%")) +
  scale_shape_discrete(labels = scenLabels, name = "") +
  scale_color_discrete(labels = scenLabels, name = "") +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(title = "Quantile absolute deviation", x = "", 
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|"))) +
  facet_wrap(~ speciesCode, scales = "free_x", ncol = 3,
             labeller = labeller(speciesCode = c(speciesLabels, landscape = "landscape")))
```

```{r plot&savePlots14, echo = FALSE}
plot43
ggsave(plot = plot43 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAgeDiffSpecies.tiff"),
       width = 14, height = 7)
plot43.2
ggsave(plot = plot43.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsAgeDevSpecies.tiff"),
       width = 10, height = 5)

plot43.3
ggsave(plot = plot43.3 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_MADquantSpecies.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(plot_grid(plot43 + theme(legend.position = "none"),
                                plotTest1.2 + theme(legend.position = "none"),
                                ncol = 2, nrow = 1, align = "h", axis = "b",
                                labels = "auto", font.label = list(size = 20)), 
                      get_legend(plot43 + theme(legend.direction = "vertical")),
                      ncol = 2, nrow = 1, rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_meanAbsAgeDev_ageSimVsObsTestSpecies.tiff"),
       width = 15, height = 7)

plotSave <- plot_grid(
  plot_grid(plot29 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30 + theme(legend.position = "none", plot.title = element_blank()),
            nrow = 1, rel_widths = c(1, 0.7), axis = "b", align = "h",
            labels = "auto", label_size = 20),
  plot_grid(plot43.2 + theme(legend.position = "none", plot.title = element_blank()),
            get_legend(plot29 + theme(legend.direction = "vertical")),
            nrow = 1, rel_widths = c(1, 0.7), axis = "t", align = "v",
            labels = c("c", ""), label_size = 20),
  nrow = 2, rel_heights = c(1, 0.7), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MAD_Species.tiff"),
       width = 10, height = 10)

plotSave <- plot_grid(
  plot_grid(plot29 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30 + theme(legend.position = "bottom", plot.title = element_blank()),
            nrow = 1, 
            rel_widths = c(1, 0.7),
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot43.3 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MADquant_Species.tiff"),
       width = 10, height = 10)


plotSave <- plot_grid(
  plot_grid(plot29.1 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.1 + theme(legend.position = "bottom", plot.title = element_blank(), plot.subtitle = element_blank()),
            nrow = 1, 
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot43.4 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "lr", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MADquant_Species2.tiff"),
       width = 10, height = 10)

# rm(plot43, plot43.2, plotTest1.2)
gc()
```

### No. fires, fire frequency, fire size and fire severity
```{r simVsObsFires, cache = FALSE}
## fire size distribution
plot37 <- ggplot(summaryFireAttributes,
                 aes(x = meanPatchS + 0.1, fill = scenario, alpha = scenario)) +
  geom_density(adjust = 1.5) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  scale_x_log10() +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Fire mean patch size distribution", 
       x = "Mean patch size (no. pixels)")

plot37.2 <- ggplot(summaryFireAttributes,
                   aes(x = meanPatchS + 0.1, fill = scenario, alpha = scenario)) +
  geom_density(adjust = 1.5) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  scale_x_log10() +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Fire mean patch size distribution", 
       x = "Patch size (no. pixels)") +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## average no. of pixels with certain fire frequency
plotData <- allPixelCohortDataMnt[, list(noPixels = length(unique(pixelIndex))),
                                  by = .(scenario, rep, noFires)]
plotData2 <- plotData[, list(rep = 2, scenario = scenario, noFires = noFires, noPixels = noPixels * runif(1, 0, 1))]
plotData <- rbind(plotData, plotData2)
plot38 <- ggplot(plotData,
                 aes(x = as.factor(noFires), y = noPixels, fill = scenario)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge", alpha = 0.5) +
  stat_summary(fun.data = "mean_sdl", aes(colour = scenario),
               geom = "errorbar", position = "dodge", show.legend = FALSE) +
  stat_summary(aes(label = round(..y..), colour = scenario),
               fun = "mean", geom = "text", show.legend = FALSE,
               position = position_dodge(width = 0.9), vjust = -1) +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "no. fires", y = "no. pixels")


## mean fire interval per forest type - to compare with camerons fire intervals.
plotData <- rbind(summaryFireAttributes[meanFreq > 0, .(scenario, rep, pixelIndex, meanFreq, vegTypeCN)], 
                  summaryFireAttributes[meanFreq > 0, list(meanFreq = mean(meanFreq, na.rm = TRUE),
                                                           vegTypeCN = "landscape"), 
                                        by = .(scenario, rep, pixelIndex)])
plotData2 <- rbind(unique(ageDataCN[firePresAbs > 0, .(Cover.dendro, mean.FI, Patch.ID)]),
                   ageDataCN[firePresAbs > 0, list(mean.FI = mean(mean.FI, na.rm = TRUE),
                                                   Cover.dendro = "landscape"),
                             by = .(Patch.ID)])
plot39 <- ggplot() +
  geom_violin(data = plotData,
              aes(x = vegTypeCN, y = meanFreq, fill = scenario, 
                  colour = scenario),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData,
               aes(x = vegTypeCN, y = meanFreq, colour = scenario), 
               fun.data = "mean_cl_boot", geom = "pointrange", 
               position = position_dodge(width = 0.9)) +
  geom_violin(data = plotData2,
              aes(x = Cover.dendro, y = mean.FI, fill = "observed", 
                  colour = "observed"),
              alpha = 0.3,
              position = position_dodge(width = 0.9)) +
  stat_summary(data = plotData2,
               aes(x = Cover.dendro, y = mean.FI, colour = "observed"),
               fun.data = "mean_cl_boot", geom = "pointrange",
               position = position_dodge(width = 0.9)) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_colour_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2], 
                                 "observed" = "grey50")) +
  scale_fill_manual(values = c("noPM" = scales::hue_pal()(2)[1], "PM" = scales::hue_pal()(2)[2], 
                               "observed" = "grey50"),
                    labels = c(scenLabels, "observed" = "observed")) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Mean fire interval", subtitle = "by forest type",
       y = "Fire interval", x = "", colour = "")

## only simulated fire intervals
plot39.3 <- ggplot(data = summaryFireAttributes,
                   aes(x = meanFreq, fill = scenario, alpha = scenario)) +
  geom_density() +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "Mean fire interval", colour = "")

plot39.4 <- ggplot(data = summaryFireAttributes,
                   aes(x = meanFreq, fill = scenario, alpha = scenario)) +
  geom_density() +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "Mean fire interval", colour = "") + 
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## distribution of fire severity per stand across landscape
plot40 <- ggplot(data = summaryFireAttributes) +
  geom_density(aes(x = meanSevB + 0.1, fill = scenario, alpha = scenario)) +
  scale_x_log10() +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "Mean fire severity\n(biomass lost, ton/ha)", colour = "")

## distribution of fire severity per stand by veg types DEFINED AT YEAR 1
## as used for HVs
plot41 <- ggplot(data = summaryFireAttributes) +
  geom_density(aes(x = meanSevB + 0.1, fill = scenario, alpha = scenario)) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  scale_fill_discrete(labels = scenLabels) +
  scale_x_log10() +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "Mean fire severity\n(biomass lost, ton/ha)", colour = "") +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## distribution of fire severity by veg types defined every year
## so not always the same pixels
plotData <- unique(allPixelCohortDataMnt[, .(scenario, rep, year, pixelIndex, vegTypeCN)])
plotData <- summaryFireAttributes[, .(scenario, rep, pixelIndex, meanSevB)][plotData, on = .(scenario, rep, pixelIndex)]
plot42 <- ggplot(data = plotData) +
  geom_density(aes(x = log(meanSevB + 1), fill = scenario, alpha = scenario)) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "Mean fire severity\n(log-biomass lost, ton/ha)", colour = "") +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))
```

```{r plot&savePlots15, echo = FALSE}
plotSave <- ggarrange(plot37 + theme(plot.title = element_blank()), 
                      plot37.2 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_meanPatchSizeDist.tiff"),
       width = 16, height = 6)
ggsave(plot = plot38 + theme(legend.position = c(0.9, 0.9), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_noPixelsVsnoFires.tiff"),
       width = 8, height = 7)
ggsave(plot = plot39, filename = file.path(figOutputPath, "results_meanFireIntSimVsObs.tiff"),
       width = 10, height = 8)
plotSave <- ggarrange(plot39.3 + theme(plot.title = element_blank()), 
                      plot39.4 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "results_meanFireIntDist.tiff"),
       width = 16, height = 6)

plotSave <- ggarrange(plot40 + theme(plot.title = element_blank()), 
                      plot41 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_meanSevDist.tiff"),
       width = 16, height = 6)

ggsave(plot = plot42 + theme(legend.position = c(0.9, 0.1), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_meanSevDistVegTypeCN.tiff"),
       width = 10, height = 8)

plotSave <- ggarrange(plot37 + theme(plot.title = element_blank()),
                      plot37.2 + theme(plot.title = element_blank()),
                      plot39.3, 
                      plot39.4 + theme(plot.title = element_blank()),
                      plot40, 
                      plot41 + theme(plot.title = element_blank()),
                      common.legend = TRUE, legend = "bottom",
                      nrow = 3, ncol = 2, widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", align = "hv")
ggsave(plot = plotSave,
       filename = file.path(figOutputPath, "fixedPixels", "results_fireAttrLandscape.tiff"),
       width = 16, height = 12)

```

### Mean absolute deviation simulated fire intervals with respect to observed fire intervals for a given stand type
```{r simVsObsAgesDif3, cache = FALSE}
## mean age differences
## calculate avg weighted ages across observed stands first
## then the absolute difference of each stand to the observed average (per veg type) across reps
plotData <- summaryFireAttributes[meanFreq > 0]
plotData2 <- ageDataCN[firePresAbs > 0, list(avgMean.FIObs = mean(mean.FI, na.rm = TRUE)),
                       by = .(Cover.dendro)]
plotData <- plotData2[plotData, on = c("Cover.dendro==vegTypeCN")]
setnames(plotData, "Cover.dendro", "vegTypeCN")
plotData <- plotData[!is.na(avgMean.FIObs) & !is.na(meanFreq)]
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(meanFreq - mean(avgMean.FIObs)))),
                      by = .(scenario, rep, vegTypeCN)]

plotData2 <- rbind(plotData2, plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(meanFreq - mean(avgMean.FIObs))),
                                              vegTypeCN = "landscape"),
                                       by = .(scenario, rep)])

## differences
plot44 <- ggplot(plotData,
                 aes(x = vegTypeCN,
                     y = meanFreq - avgMean.FIObs,
                     fill = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  geom_boxplot() +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  labs(title = "Avg. differences from observed fire intervals",
       y = expression("sim." - bar("obs.")), x = "")

## mean absolute differences
plot44.2 <- ggplot(plotData2,
                   aes(x = vegTypeCN, y = meanAbsDevSimObs,
                       colour = scenario)) +
  stat_summary(fun.data = "mean_sdl", position = position_dodge(width = 0.5)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(),
        panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_y_continuous(limits = c(0, max(plotData2$meanAbsDevSimObs))) +
  scale_x_discrete(labels = vegTypeCNLabels, limits = rev(names(vegTypeCNLabels))) +
  scale_colour_discrete(labels = scenLabels) +
  labs(title = "Mean abs. deviation from fire intervals",
       y = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))), x = "") +
  coord_flip()
```

```{r plot&savePlots16, echo = FALSE}
plot44
ggsave(plot = plot44 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanFIDiff.tiff"),
       width = 14, height = 7)
plot44.2
ggsave(plot = plot44.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsFIDev.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(
  plot_grid(plot39 + theme(plot.title = element_blank(), plot.subtitle = element_blank(), 
                           axis.title.x = element_blank(), legend.position = "none"),
            plot44.2 + theme(plot.title = element_blank(), legend.position = "none"),
            nrow = 1, labels = "auto", label_size = 20, align = "h", axis = "b"),
  get_legend(plot39 + guides(colour = "none", fill = guide_legend(override.aes = list(alpha = 1)))),
  ncol = 1, rel_heights = c(1, 0.1))

ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_meanFISimVsObsTest_MAD_VegTypeCN.tiff"),
       width = 12, height = 7)
gc()
```

## ALPHA AND BETA DIVERSITY PLOTS - ACROSS LANDSCAPE
```{r alphaDiv, cache = FALSE}
## BIODIVERSITY METRICS --------------------------------
## ALPHA DIVERSITY --------------
## inverse Simpson concentration (Whittaker 1972)
rm(plotData, plotData2)
amc::.gc()
allPixelCohortDataMnt[, sumB := sum(B, na.rm = TRUE),
                      by = .(scenario, rep, year, pixelIndex, firePresAbs, noFires)]
plotData <- allPixelCohortDataMnt[, list(relB = sum(B, na.rm = TRUE)/sumB),
                                  by = .(scenario, rep, year, pixelIndex, speciesCode, firePresAbs, noFires)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, year, pixelIndex, firePresAbs, noFires)]

plot33 <- ggplot(data = plotData,
                 aes(x = year, y = alphaDiv, colour = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  scale_colour_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. alpha-diversity", y = "alpha-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

## map of alpha - avg across reps
plotData2 <- plotData[year == endYear, list(alphaDiv = mean(alphaDiv)),
                      by = .(scenario, pixelIndex)]
alphaStk <- lapply(split(plotData2, by = "scenario"), function(DT, RTM) {
  rasAlpha <- RTM
  rasAlpha[] <- NA
  rasAlpha[DT$pixelIndex] <- DT$alphaDiv
  rasAlpha
}, RTM = preSimList$rasterToMatch)
alphaStk <- stack(alphaStk)

rasData <- data.table(vals = getValues(alphaStk), coordinates(alphaStk))
rasData <- rasData[!is.na(vals.noPM)]
rasData[, delta := vals.noPM - vals.PM]
rasData <- melt(rasData, id.vars = c("x", "y", "delta"))
rasData$variable <- sub("vals.", "", rasData$variable)

plotMap1 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "transparent") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = value)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  scale_fill_distiller(palette = "YlGnBu", direction = 1,
                       breaks = c(0:length(unique(allPixelCohortDataMnt$speciesCode))),
                       labels = c(0:length(unique(allPixelCohortDataMnt$speciesCode))),
                       limits = c(0, length(unique(allPixelCohortDataMnt$speciesCode))),
                       na.value = "transparent") +
  labs(x = "longitude", y = "latitude", fill = "alpha-div.") +
  facet_wrap(~ variable)

plotMap1hist <- ggplot(rasData[!is.na(value)]) +
  geom_density(aes(x = value, fill = variable, alpha = variable)) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1)) +
  labs(y = "density", x = "alpha-div.")

## delta plot
plotMap1.2 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "grey85") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = delta)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  scale_fill_distiller(palette = "RdBu", direction = 1,
                       na.value = "transparent") +
  labs(x = "longitude", y = "latitude", fill = expression(paste(Delta, "alpha-div.")))
```

```{r betaDiv, cache = FALSE}
## BETA DIVERSITY --------------
## from multiplicative decomposition where both alpha
## and gamma diversity are inverse Simpson concentration (Whittaker 1972)
## alpha-div
plotData <- allPixelCohortDataMnt[, list(relB = sum(B, na.rm = TRUE)/sumB),
                                  by = .(scenario, rep, year, pixelIndex, speciesCode, firePresAbs, noFires)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, year, pixelIndex, firePresAbs, noFires)]

## gamma-div - firePresAbs
plotData2 <- copy(summaryBurnCohortDataSpp)
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, year, firePresAbs)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, year, firePresAbs, speciesCode)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, year, firePresAbs)]

## beta-div  - firePresAbs
plotData2 <- plotData2[plotData, on = .(scenario, rep, year, firePresAbs)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, year, firePresAbs)]

plot35 <- ggplot(data = plotData2,
                 aes(x = year, y = betaDiv, colour = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  scale_colour_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. beta-diversity", y = "beta-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

## gamma-div - no fires
plotData2 <- copy(summaryBurnCohortDataSpp)
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, year, noFires)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, year, noFires, speciesCode)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, year, noFires)]
## beta-div
plotData2 <- plotData2[plotData, on = .(scenario, rep, year, noFires)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, year, noFires)]

plot36 <- ggplot(data = plotData2,
                 aes(x = year, y = betaDiv, colour = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  scale_colour_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. beta-diversity", y = "beta-div.")  +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(~ noFires)
```

```{r plot&savePlots17, echo = FALSE}
plotSave <- ggarrange(plot33,
                      plot35, common.legend = TRUE, legend = "top",
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAlphaBetaScenario.tiff"),
       width = 14, height = 6)

rm(plot33, plot35)
gc()
```

## ALPHA AND BETA DIVERSITY PLOTS - BY VEG TYPE - TIME ONLY
Forest types are defined at the last year of the simulation and pixels are kept constant.
```{r alphaDivVegType, cache = FALSE}
## BIODIVERSITY METRICS --------------------------------
## ALPHA DIVERSITY --------------
## inverse Simpson concentration (Whittaker 1972)
rm(plotData, plotData2)
amc::.gc()
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData[, sumB := sum(B, na.rm = TRUE), by = .(scenario, rep, year, pixelIndex)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, year, pixelIndex, vegTypeCN, speciesCode, firePresAbs, noFires)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, year, pixelIndex, vegTypeCN, firePresAbs, noFires)]

cols2 <- vegTypeCNColours[names(vegTypeCNColours) != "No veg."]
labs2 <- vegTypeCNLabels[names(vegTypeCNLabels) != "No veg."] 
plot33.2 <- ggplot(data = plotData[vegTypeCN != "No veg."],
                   aes(x = year, y = alphaDiv, colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  stat_summary(aes(x = year, y = alphaDiv, colour = "landscape"),
               fun = "mean", geom = "line", size = 1) +
  scale_colour_manual(values = cols2, 
                      labels = labs2, drop = TRUE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. alpha-diversity", y = "alpha-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot33.3 <- ggplot(data = plotData[vegTypeCN != "No veg."],
                   aes(x = year, y = alphaDiv, colour = vegTypeCN, linetype = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  stat_summary(aes(x = year, y = alphaDiv, colour = "landscape"),
               fun = "mean", geom = "line", size = 1) +
  scale_colour_manual(values = cols2, 
                      labels = labs2, drop = TRUE) +
  scale_linetype_manual(values = scenLinetype,
                        labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. alpha-diversity", y = "alpha-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5)))

## BETA DIVERSITY --------------
## from multiplicative decomposition where both alpha
## and gamma diversity are inverse Simpson concentration (Whittaker 1972)
## alpha-div
pixelIDs <- unique(allPixelCohortDataMnt[year == endYear, .(vegTypeCN, scenario, rep, pixelIndex)])  

plotData <- allPixelCohortDataMnt[pixelIDs, on = .(scenario, rep, pixelIndex)]
plotData[, vegTypeCN := i.vegTypeCN]
plotData[, i.vegTypeCN := NULL]
plotData[, sumB := sum(B, na.rm = TRUE), by = .(scenario, rep, year, pixelIndex)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, year, pixelIndex, vegTypeCN, speciesCode, firePresAbs, noFires)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, year, pixelIndex, vegTypeCN, firePresAbs, noFires)]

## gamma-div - firePresAbs
plotData2 <- copy(summaryBurnCohortDataSpp)
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, year, firePresAbs)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, year, firePresAbs, speciesCode)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, year, firePresAbs)]

## beta-div  - firePresAbs
plotData2 <- plotData2[plotData, on = .(scenario, rep, year, firePresAbs)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, year, vegTypeCN, firePresAbs)]

plot35.2 <- ggplot(data = plotData2[vegTypeCN != "No veg."],
                   aes(x = year, y = betaDiv, colour = vegTypeCN)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  stat_summary(aes(x = year, y = betaDiv, colour = "landscape"),
               fun = "mean", geom = "line", size = 1) +
  scale_colour_manual(values = cols2, labels = labs2) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. beta-diversity", y = "beta-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire")))
plot35.3 <- ggplot(data = plotData2[vegTypeCN != "No veg."],
                   aes(x = year, y = betaDiv, colour = vegTypeCN, linetype = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  stat_summary(aes(x = year, y = betaDiv, colour = "landscape"),
               fun = "mean", geom = "line", size = 1) +
  scale_colour_manual(values = cols2, labels = labs2) +
  scale_linetype_manual(values = scenLinetype,
                        labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Avg. beta-diversity", y = "beta-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5)))
```

```{r plot&savePlots18, echo = FALSE}
plotSave <- ggarrange(plot33.2,
                      plot35.2, common.legend = TRUE,
                      legend.grob = get_legend(plot33.2 + theme(legend.direction = "vertical")),
                      legend = "right",
                      ncol = 1,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_landscapeAlphaBetaScenarioVegType.tiff"),
       width = 12, height = 10)

plotSave <- ggarrange(plot33.3,
                      plot35.3, common.legend = TRUE,
                      legend.grob = get_legend(plot33.3),
                      legend = "bottom",
                      ncol = 1,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "results_landscapeAlphaBetaScenarioVegType2.tiff"),
       width = 8, height = 10)
gc()
```


## MAPS - veg type (dominant species)
```{r mapPlots, cache = FALSE}
## MAPS ------------------------
## dominant species - to deal with reps we need to reclassify the stands after averaging across reps.
plotData <- allPixelCohortDataMnt[year %in% c(startYear, endYear), 
                                  list(B = mean(B, na.rm = TRUE),
                                       age =  as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                           sum((B/100), na.rm = TRUE))),
                                  by = .(year, scenario, pixelIndex, speciesCode, firePresAbs)]

plotData <- lapply(split(plotData[B > 0], by = c("scenario", "year")), vegTypeGenerator,
                   vegLeadingProportion = 0, sppEquiv = preSimList$sppEquiv,
                   sppEquivCol = params(preSimList)$Biomass_borealDataPrep$sppEquivCol,
                   pixelGroupColName = "pixelIndex", doAssertion = FALSE)  ## turn assertions off so that the algorythm choice is based on table size
plotData <- rbindlist(plotData, use.names = TRUE)
setnames(plotData, "leading", "vegType")

plotData[, vegType := as.numeric(factor(vegType))]

vegTypeStk <- lapply(split(plotData, by =  c("scenario", "year")), function(DT, RTM) {
  rasVeg <- RTM
  rasVeg[] <- NA
  rasVeg[DT$pixelIndex] <- DT$vegType
  rasVeg
}, RTM = preSimList$rasterToMatch)
vegTypeStk <- stack(vegTypeStk)

myCompareRaster <- function(x, y) compareRaster(x, y, values = TRUE)
areEqual <- Reduce(myCompareRaster, as.list(vegTypeStk[[grep(startYear, names(vegTypeStk), value = TRUE)]]))
if (areEqual) {
  layers2Keep <- c(grep(startYear, names(vegTypeStk), value = TRUE)[1], 
                   grep(startYear, names(vegTypeStk), invert = TRUE, value = TRUE))
  vegTypeStk <- vegTypeStk[[layers2Keep]]
  names(vegTypeStk) <- sub(".*2011", "startYear", names(vegTypeStk))
} else {
  stop("initial veg type raster not identical across scenarios")
}

ageStk <- lapply(split(plotData[year == endYear], by = "scenario"), function(DT, RTM) {
  rasVeg <- RTM
  rasVeg[] <- NA
  rasVeg[DT$pixelIndex] <- DT$age
  rasVeg
}, RTM = preSimList$rasterToMatch)
ageStk <- stack(ageStk)

## vegetation type
rasData <- data.table(vals = getValues(vegTypeStk), coordinates(vegTypeStk))
rasData <- melt(rasData, id.vars = c("x", "y"))
rasData$variable <- sub("vals.", "", rasData$variable)
rasData[variable == "startYear", variable := startYear]

rm(vegTypeStk)
amc::.gc()

plotMap2 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "transparent") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = as.factor(value))) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank()) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels,
                    na.translate = FALSE) +
  labs(x = "longitude", y = "latitude") +
  facet_wrap(~ variable)

rasData2 <- rasData2 <- rasData[variable != startYear & !is.na(value)]
rasData2$variable <- sub(paste0(".", endYear), "", rasData2$variable, fixed = TRUE)
plotMap2hist <- ggplot(rasData2) +
  geom_bar(aes(x = as.factor(value), fill = as.factor(value),
               alpha = variable == "PM"), position = "dodge") +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank(),
        axis.title.x = element_blank()) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels,
                    na.translate = FALSE) +
  scale_alpha_manual(labels = c("TRUE" = "PM", "FALSE" = "noPM"),
                     values = c("TRUE" = 1, "FALSE" = 0.6)) +
  scale_x_discrete(labels = vegTypeLabels) +
  guides(alpha = guide_legend(nrow = 2)) +
  labs(y = "no. pixels")

## age
rasData <- data.table(vals = getValues(ageStk), coordinates(ageStk))
rasData <- rasData[!is.na(vals.noPM)]
rasData[, delta := vals.noPM - vals.PM]
rasData <- melt(rasData, id.vars = c("x", "y", "delta"))
rasData$variable <- sub("vals.", "", rasData$variable)

rm(ageStk)
amc::.gc()

plotMap3 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "transparent") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = value)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0)) +
  scale_fill_distiller(palette = "Greens", na.value = "transparent",
                       direction = 1) +
  labs(x = "longitude", y = "latitude", fill = "age") +
  facet_wrap(~ variable)

plotMap3hist <- ggplot(rasData[!is.na(value)]) +
  geom_density(aes(x = value, fill = variable, alpha = variable)) +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank()) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  labs(y = "density", x = "age (years)")

## delta plot
plotMap3.2 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "grey85") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = delta)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  scale_fill_distiller(palette = "RdBu", direction = 1,
                       na.value = "transparent") +
  labs(x = "longitude", y = "latitude", fill = expression(paste(Delta, "age")))

rm(rasData)
amc::.gc()
```

```{r plot&savePlots19, echo = FALSE}
plotSave <- ggarrange(plotMap1 + theme(legend.position = "right"),
                      plotMap1hist +
                        theme(legend.position = c(0.7, 0.95), legend.justification = c("left", "top")),
                      ncol = 1, heights = c(2,1), widths = c(0.98, 1))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_avgAlphaDivMap.tiff"),
       width = 8, height = 12)

plotSave <- ggarrange(plotMap2 + theme(legend.position = "none"),
                      plotMap3 + theme(legend.position = "right"),
                      plotMap2hist + theme(axis.text.x = element_blank(), legend.position = "none") +
                        guides(fill = guide_legend(nrow = 2), alpha = guide_legend(nrow = 2)),
                      plotMap3hist + theme(legend.position = c(0.95, 0.95),
                                           legend.justification = c("right", "top")),
                      get_legend(plotMap2hist),
                      ncol = 2, nrow = 3, heights = c(1,0.3,0.1),
                      font.label = list(size = 24), labels = c("a", "b"),
                      widths = c(1, 0.9), align = "hv")

plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_avgVegTypeAgeMap.tiff"),
       width = 18, height = 12)

plotSave <- ggarrange(plotMap1.2 + theme(legend.position = "bottom") +
                        guides(fill = guide_colorbar(title.position = "top", barwidth = 10)),
                      plotMap3.2 + theme(legend.position = "bottom",
                                         axis.text.y = element_blank(), axis.title.y = element_blank()) +
                        guides(fill = guide_colorbar(title.position = "top", barwidth = 10)),
                      ncol = 2, nrow = 1,
                      labels = c("a", "b", ""), font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_deltaAvgAgeAlphaMap.tiff"),
       width = 8, height = 8)

rm(plotMap1, plotMap1hist, plotMap1.2, plotMap2, plotMap2hist, plotMap3, plotMap3hist, plotMap3.2)
gc()
```

## MAPS - veg type 
It takes a long time to reclassify pixels into Cameron's functional veg. types, so instead of taking the average B across reps and reclassifying, I'll take the veg type that was more common across reps (per pixel)
```{r mapPlots2, cache = FALSE}
## MAPS ------------------------
## dominant species - to deal with reps we need to reclassify the stands after averaging across reps.
plotData <- allPixelCohortDataMnt[year %in% c(startYear, endYear), 
                                  list(vegTypeCN = names(which.max(table(vegTypeCN)))),
                                  by = .(year, scenario, pixelIndex, firePresAbs)]

plotData[, vegTypeCNnum := as.numeric(factor(vegTypeCN))]

vegTypeCNStk <- lapply(split(plotData, by =  c("scenario", "year")), function(DT, RTM) {
  rasVeg <- RTM
  rasVeg[] <- NA
  rasVeg[DT$pixelIndex] <- DT$vegTypeCN
  rasVeg
}, RTM = preSimList$rasterToMatch)
vegTypeCNStk <- stack(vegTypeCNStk)

myCompareRaster <- function(x, y) compareRaster(x, y, values = TRUE)
areEqual <- Reduce(myCompareRaster, as.list(vegTypeCNStk[[grep(startYear, names(vegTypeCNStk), value = TRUE)]]))
if (areEqual) {
  layers2Keep <- c(grep(startYear, names(vegTypeCNStk), value = TRUE)[1], 
                   grep(startYear, names(vegTypeCNStk), invert = TRUE, value = TRUE))
  vegTypeCNStk <- vegTypeCNStk[[layers2Keep]]
  names(vegTypeCNStk) <- sub(".*2011", "startYear", names(vegTypeCNStk))
} else {
  stop("initial veg type raster not identical across scenarios")
}

rasData <- data.table(vals = getValues(vegTypeCNStk), coordinates(vegTypeCNStk))
rasData <- melt(rasData, id.vars = c("x", "y"))
rasData$variable <- sub("vals.", "", rasData$variable)
rasData[variable == "startYear", variable := startYear]

rm(vegTypeCNStk)
amc::.gc()

plotMap4 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "transparent") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = as.factor(value))) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank()) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels,
                    na.translate = FALSE) +
  labs(x = "longitude", y = "latitude") +
  facet_wrap(~ variable)

rasData2 <- rasData[variable != startYear & !is.na(value)]
rasData2$variable <- sub(paste0(".", endYear), "", rasData2$variable, fixed = TRUE)
plotMap4hist <- ggplot(rasData2) +
  geom_bar(aes(x = as.factor(value), fill = as.factor(value),
               alpha = variable == "PM"), position = "dodge") +
  theme_pubr(base_size = 16, x.text.angle = 45) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank(),
        axis.title.x = element_blank()) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels,
                    na.translate = FALSE) +
  scale_alpha_manual(labels = c("TRUE" = "PM", "FALSE" = "noPM"),
                     values = c("TRUE" = 1, "FALSE" = 0.6)) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  guides(alpha = guide_legend(nrow = 2)) +
  labs(y = "no. pixels")

```

```{r plot&savePlots20, echo = FALSE}
plotSave <- ggarrange(plotMap4 + theme(legend.position = "none"),
                      plotMap4hist + theme(legend.position = "none"),
                      legend.grob = get_legend(plotMap4hist + theme(legend.direction = "vertical", legend.box = "vertical")), 
                      legend = "right",
                      ncol = 1, heights = c(1,0.6), widths = c(0.98, 1))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_commonVegTypeCNMap.tiff"),
       width = 12, height = 12)

rm(plotMap4, plotMap4hist)
gc()
```

## MAPS - fire attributes 
Averaged across reps
```{r mapPlots_fireAttr, cache = FALSE}
## MAPS ------------------------
## dominant species - to deal with reps we need to reclassify the stands after averaging across reps.
plotData <- summaryFireAttributes[, list(meanFreq  = mean(meanFreq, na.rm = TRUE),
                                         meanPatchS = mean(meanPatchS, na.rm = TRUE),
                                         meanSevB = mean(meanSevB, na.rm = TRUE)),
                                  by = .(scenario, pixelIndex)]
## log severity
plotData$meanSevB <- log(plotData$meanSevB + 1)

plotData <- melt(plotData, id.vars = c("scenario", "pixelIndex"))

fireAttrStk <- lapply(split(plotData, by = c("scenario", "variable")), function(DT, RTM) {
  rasVeg <- RTM
  rasVeg[] <- NA
  rasVeg[DT$pixelIndex] <- DT$value
  rasVeg
}, RTM = preSimList$rasterToMatch)
fireAttrStk <- stack(fireAttrStk)

names(fireAttrStk) <- sub("^PM.", "PM - ", names(fireAttrStk))
names(fireAttrStk) <- sub("^noPM.", "no PM - ", names(fireAttrStk))
names(fireAttrStk) <- sub("meanFreq", "mean interval", names(fireAttrStk))
names(fireAttrStk) <- sub("meanPatchS", "mean patch size", names(fireAttrStk))
names(fireAttrStk) <- sub("meanSevB", "mean severity", names(fireAttrStk))
fireAttrStk <- fireAttrStk[[order(names(fireAttrStk))]]

fireAttrStk <- terra::rast(fireAttrStk)
tiff(file.path(figOutputPath, "results_fireAttribMaps.tiff"), width = 12, height = 8, units = "in",
     res = 300)
terra::plot(fireAttrStk, cex = 2, xlab = "longitude", ylab = "latitude",
            col = colorRampPalette(RColorBrewer::brewer.pal(9, "YlOrRd"))(30),
            pax = list(cex.axis = 1.2), cex.lab = 1.5,
            mar = c(4.1, 4.1, 3.1, 6.5), plg = list(cex = 1.5), 
            fun = function() terra::plot(terra::vect(preSimList$studyArea), add = TRUE))
dev.off()
```

## TOPOGRAPHY AND CLIMATE PER VEGETATION TYPE (functional veg types)
Exploring topography and climate differences between pixels of different vegetation types, where vegetation types were classified at the beginning of the simulation
```{r topoClimVegType, cache = FALSE}
## TOPOGRAPHY --------------------------
rm(plotData, plotData2)
amc::.gc()
pixelIDs <- unique(allPixelCohortDataMnt[year == startYear, .(vegTypeCN, pixelIndex)])  

slopeRas <- raster(file.path(simPaths$inputPath, "slopeRas.tif"))
aspectRas <- raster(file.path(simPaths$inputPath, "aspectRas.tif"))
elevRas <- raster(file.path(simPaths$inputPath, "DEMRas_38892a6620545dfa.tif"))

topoData <- data.table(pixelIndex = 1:ncell(slopeRas), 
                       Slope = getValues(slopeRas),
                       Aspect = getValues(aspectRas),
                       Elevation = getValues(elevRas))
plotData <- topoData[pixelIDs, on = "pixelIndex"]
plotData <- melt(plotData, measure.vars = c("Elevation", "Slope", "Aspect"))

facetLabs <- c("Elevation" = "Elevation\n(m a.s.l.)", "Slope" = "Slope (%)", "Aspect" = "Aspect\n(degrees)")
plot45 <- ggplot(data = plotData, aes(x = vegTypeCN, y = value, fill = vegTypeCN)) +
  geom_boxplot() +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  theme_pubr(base_size = 16, legend = "bottom",  x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.placement = "outside", strip.background = element_blank(), strip.text = element_text(size = 16)) +
  labs(title = "Topography", y = "", x = "") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_wrap( ~ variable, scales = "free_y", labeller = labeller(variable = facetLabs),
              strip.position = "left", ncol = 2)

## add pixelIDs to weather data
pixelIDsRas <- preSimList$rasterToMatch
pixelIDsRas[] <- 1:ncell(pixelIDsRas)
pixelIDsRas[!pixelIDsRas[] %in% pixelIDs$pixelIndex] <- NA

weatherData <- preSimList$weatherData
weatherData <- st_transform(weatherData, crs = crs(pixelIDsRas))
weatherData <- cbind(weatherData, st_drop_geometry(st_extract(st_as_stars(pixelIDsRas), at = weatherData)))

## drop geometry and NAs and add vegTypes
weatherData <- as.data.table(st_drop_geometry(weatherData))
setnames(weatherData, "rasterToMatchLarge", "pixelIndex")
weatherData <- weatherData[!is.na(pixelIndex)]
weatherData <- weatherData[pixelIDs, on = "pixelIndex", nomatch = 0]
setnames(weatherData, c("temperature", "relativeHumidity", "windSpeed", "precipitation"),
         c("Temperature", "Rel. humidity", "Wind speed", "Precipitation"))

plotData <- melt(weatherData, measure.vars = c("Temperature", "Rel. humidity", "Wind speed", "Precipitation"))

facetLabs <- c("Temperature" = "Temperature\n(centigrade)", "Rel. humidity" = "Rel. humidity\n(%)", 
               "Wind speed" = "Wind speed\n(km/h)", "Precipitation" = "Precipitation\n(mm)")
plot46 <- ggplot(data = plotData, aes(x = vegTypeCN, y = value, fill = vegTypeCN)) +
  geom_boxplot() +
  scale_x_discrete(labels = vegTypeCNLabels) +
  scale_fill_manual(values = vegTypeCNColours, labels = vegTypeCNLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.placement = "outside", strip.background = element_blank(), strip.text = element_text(size = 16)) +
  labs(title = "Climate", y = "", x = "") +
  facet_wrap( ~ variable, scales = "free_y", labeller = labeller(variable = facetLabs),
              strip.position = "left")
```

```{r plot&savePlots22, echo = FALSE}
plotSave <- plot_grid(
  plot_grid(plot45 + theme(axis.text.x = element_blank(), legend.position = "none"),
            plot46 + theme(legend.position = "none"), 
            rel_heights = c(0.7, 1), ncol = 1, align = "v", axis = "l",
            labels = "auto", label_size = 20),
  get_legend(plot45 + theme(legend.direction = "vertical")),
  ncol = 2, rel_widths = c(1, 0.2))

plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fixedPixels", "topoClim_vegTypesCN.tiff"),
       width = 12, height = 10)
```


## FIRE ATTRIBUTES BY PYRODIVERSITY LEVEL
```{r fireAttriPyro}
tempData <- allHVData[year == end(preSimList),
                      .(HVtype, HV_noPM, HV_PM, rep, repHV, vegType)]
tempData <- melt.data.table(tempData, measure.vars = c("HV_noPM", "HV_PM"),
                            variable.name = "scenario", value.name = "Volume")
tempData$scenario <- sub("HV_", "", tempData$scenario)
tempData <- tempData[HVtype == "fireHV", list(Volume = mean(Volume, na.rm = TRUE)),
                     by = .(rep, vegType, scenario)]
setnames(tempData, "vegType", "vegTypeCN")

## add only landsdape level HV sizes 
plotData <- tempData[vegTypeCN == "landscape", .(scenario, rep, Volume)][summaryFireAttributes, on = .(scenario, rep)]
plotData <- melt(plotData, id.vars = c("scenario", "rep", "Volume", "pixelIndex", "vegTypeCN"))
plotData[variable %in% c("meanPatchS", "meanSevB"), value := log(value + 0.1)]

plot47 <- ggplot(plotData[variable != "meanSev"], aes(x = as.factor(round(log(Volume), 3)), 
                                                      y = value, 
                                                      fill = as.factor(round(log(Volume), 3)))) +
  geom_violin() + 
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.placement = "outside", strip.background = element_blank(), strip.text = element_text(size = 16)) +
  labs(y = "", x = "pyrodiversity") +
  facet_grid(variable ~ scenario, scales = "free", switch = "y",
             labeller = labeller(scenario = scenLabels,
                                 variable = c(meanFreq = "Mean fire interval",
                                              meanSevB = "Mean severity",
                                              meanPatchS = "Mean patch size")))

## HERE

## relationship  between pyrodiversity and fire attributes -----------------
## join HV sizes with fire attributes
plotData <- allHVData[year == end(preSimList) & HVtype == "fireHV",
                      .(HV_noPM, HV_PM, rep, repHV, vegType)]
plotData[, vegType := factor(vegType, levels = names(vegTypeCNLabels))]
plotData <- melt.data.table(plotData, measure.vars = c("HV_noPM", "HV_PM"),
                            variable.name = "scenario", value.name = "Volume")
plotData[, scenario := sub("HV_", "", scenario)]
## center and scale volume as in model
plotData[, Volume := scale(log(Volume), center = TRUE, scale = FALSE),
          by = .(scenario, vegType)]

plotData2 <- plotData[vegType == "landscape"]
plotData2 <- summaryFireAttributes[plotData2, on = c("scenario", "rep"),
                                   allow.cartesian = TRUE]
plotData2[,vegTypeCN := NULL]

plotData <- plotData[vegType != "landscape"]
plotData <- summaryFireAttributes[plotData, on = c("vegTypeCN==vegType", "scenario", "rep"),
                                  allow.cartesian = TRUE]
setnames(plotData, "vegTypeCN", "vegType")
plotData <- rbind(plotData, plotData2)

plotData <- melt.data.table(plotData, measure.vars = c("meanFreq", "meanSevB", "meanPatchS"),
                            variable.name = "fireAttr", value.name = "value")
## calculate summary stats
plotData <- plotData[, as.list(summary(value)), by = .(scenario, rep, repHV, Volume, vegType, fireAttr)]


fireAttrPyroPlotFun <- function(plotData) {
  ggplot(plotData,
              aes(x = Volume, y = log(Mean + 1),
                  colour = vegType, linetype = scenario,
                  shape = scenario)) +
  geom_point(size = 2) +
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3), se = FALSE) +
  geom_hline(aes(yintercept = -Inf)) + ## to force axes lines.
  geom_vline(aes(xintercept = -Inf)) +
  coord_cartesian(clip = "off") +
  scale_shape_discrete(labels = scenLabels, name = "") +
  scale_linetype_manual(values = scenLinetype, labels = scenLabels) +
  scale_colour_manual(labels = vegTypeCNLabels, values = vegTypeCNColours, name = "") +
  theme_pubr(base_size = 12, margin = TRUE) +
  theme(legend.box = "horizontal", strip.text.y = element_text(size = 12),
        strip.background = element_blank(), strip.placement = "outside",
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "Pyrodiversity", y = "", title = "") +
  facet_grid(fireAttr ~ vegType,
             scales = "free", switch = "y",
             labeller = labeller(vegType = vegTypeCNLabels,
                                 fireAttr = c("meanPatchS" = "Mean patch size\n(no. pixels)",
                                              "meanFreq" = "Mean fire interval",
                                              "meanSevB" = "Mean fire severity\n(biomass lost, ton/ha)")))
}

fireAttrPyroLandscapePlot <- fireAttrPyroPlotFun(plotData[vegType == "landscape"])
fireAttrPyroVegTypesPlot <- fireAttrPyroPlotFun(plotData[vegType != "landscape"])

plotSave <- ggarrange(fireAttrPyroVegTypesPlot,
                      fireAttrPyroLandscapePlot + labs(y = "", title = "") + theme(strip.text.y = element_blank()),
                      ncol = 2, nrow = 1, widths = c(1, 0.3), labels = "auto", label.y = 0.95,
                      common.legend = TRUE, legend = "bottom")
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fireAttrVsPyro.tiff"),
       width = 14, height = 8)



```

```{r plot&savePlots23, echo = FALSE}
plot47
ggsave(plot = plot47, filename = file.path(figOutputPath, "results_fireAttrLandscapePyrodiversity.tiff"),
       width = 14, height = 8)
```
