---
title: "LIM - analysis of results (montane -- new: sims with 2000yrs)"
subtitle: "Only publication results are included" 
author: "Ceres Barros"
date: "22/06/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(getwd()))
knitr::opts_chunk$set(echo = FALSE, cache = 2, warning = FALSE,
                      fig.width = 10, fig.height = 8)
```

```{r setup2, include=FALSE}
if (!exists("pkgDir")) {
  pkgDir <- file.path(
    if (Sys.info()[["user"]] == "rstudio") "packages_docker" else "packages",
    version$platform,
    paste0(version$major, ".", strsplit(version$minor, "[.]")[[1]][1])
  )
  
  if (!dir.exists(pkgDir)) {
    dir.create(pkgDir, recursive = TRUE)
  }
  .libPaths(pkgDir)
}

library(Require)

Require(
  c("data.table",
    "ggplot2",
    "ggpubr",
    "ggspatial",
    "cowplot",
    "raster",
    "stars", 
    "sf",
    "quickPlot",
    "SpaDES",
    "qs",
    "purrr",
    "magick",
    "LandR (==1.0.7.9026)",
    "future",
    "future.apply",
    "lme4",
    "MuMIn",
    "ToolsCB"), install = FALSE)

source("R/R_tools/convertToCNVegType.R")
source("R/R_tools/hypervolumesHelpers.R")
source("R/R_tools/Useful_functions.R")
source("R/R_tools/utilsForResultsAnalyses.R")
options("reproducible.useNewDigestAlgorithm" = 2)
options("spades.moduleCodeChecks" = FALSE)
options("reproducible.useCache" = TRUE)
options("reproducible.destinationPath" = normPath("R/SpaDES/inputs"))
options("reproducible.useGDAL" = FALSE)


## general paths
simDirName <- "mar2022Runs"
if (Sys.info()["nodename"] == "W-VIC-A127584") {
  simPaths <- list(cachePath = file.path("F:", basename(getwd()), "R/SpaDES/cache", simDirName, "postSimAnalyses")
                   , modulePath = normPath(file.path("R/SpaDES/m"))
                   , inputPath = normPath(file.path("R/SpaDES/inputs"))
                   , outputPath = file.path("F:", basename(getwd()), "R/SpaDES/outputs", simDirName))
} else if (grepl("for-cast", Sys.info()["nodename"])) {
  simPaths <- list(cachePath = file.path("R/SpaDES/cache", simDirName, "postSimAnalyses")
                   , modulePath = normPath(file.path("R/SpaDES/m"))
                   , inputPath = normPath(file.path("R/SpaDES/inputs"))
                   , outputPath = normPath(file.path("R/SpaDES/outputs", simDirName))
                   , rasterPath = file.path("/mnt/scratch/cbarros", basename(getwd()), "R/SpaDES/scratch/raster")
                   , scratchPath = file.path("/mnt/scratch/cbarros", basename(getwd()), "R/SpaDES/scratch"))
} else {
  simPaths <- list(cachePath = normPath(file.path("R/SpaDES/cache", simDirName, "postSimAnalyses"))
                   , modulePath = normPath(file.path("R/SpaDES/m"))
                   , inputPath = normPath(file.path("R/SpaDES/inputs"))
                   , outputPath = normPath(file.path("R/SpaDES/outputs", simDirName)))
}

if (grepl("for-cast", Sys.info()["nodename"]) ||
    grepl("45eafed436c8", Sys.info()["nodename"])) {
  data.table::setDTthreads(5)
  options(bitmapType="cairo")
}

## path to figure folder and cache folder
figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane")

## merge Douglas-fir/dry-conifer stands?
## no need with last year classif
mergeDMCPSME <- FALSE  ## merge DMCPSME PSME dryPSME
mergePSME <- FALSE ## merge PSME dryPSME :: March 2026, decided not to merge
if (mergeDMCPSME) {
  figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane/mergeDMCPSME")
  HVoutputPathMergedVegType <- file.path(simPaths$outputPath, "hypervolumes", "mergeDMCPSME")
}
if (mergePSME) {
  HVoutputPathMergedVegType <- file.path(simPaths$outputPath, "hypervolumes", "mergePSME")
  figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane/mergePSME")
}
dir.create(figOutputPath, recursive = TRUE)
```

## DATA LOADING AND PROCESSING NOTES
Given the size of the data put together in a pixel-based format, results were sampled every 10 years (instead of the 5-year interval used for saving),

```{r dataPrep, cache=FALSE, include=FALSE}
yearSubset <- unique(as.integer(c(seq(3511, 4011, 5), 4011)))
runPrepResultsModule <- FALSE
source("R/SpaDES/simResultsDataPrep.R")
source("R/SpaDES/obsResultsDataPrep.R")
rm(allPixelCohortData) ## not needed
gc(reset = TRUE)

if (mergeDMCPSME) {
  allPixelCohortDataMnt[vegTypeCN %in% c("DMCPSME", "PSME", "dryPSME"), vegTypeCN := "DMCPSME"]
  ageDataCN[Cover.dendro %in% c("DMCPSME", "PSME", "dryPSME"), Cover.dendro := "DMCPSME"]
}

if (mergePSME) {
  allPixelCohortDataMnt[vegTypeCN %in% c("PSME", "dryPSME"), vegTypeCN := "PSME"]
  ageDataCN[Cover.dendro %in% c("PSME", "dryPSME"), Cover.dendro := "PSME"]
}

## need to use sampled years as "last year" -- maybe average per rep
yearSamples <- sample5SimYears(allPixelCohortDataMnt[, .(year, rep)])   ## seed ensures same years are drawn

allPixelCDMntEnd <- allPixelCohortDataMnt[yearSamples, on = .(year, rep)]

## average all continuous properties and re-classify stands.
# allPixelCDMntEnd <- Cache(averagAllPixelCDMntEnd,
#                           allPixelCDMntEnd = allPixelCDMntEnd,
#                           omitArgs = "allPixelCDMntEnd",
#                           cacheRepo = simPaths$cachePath,
#                           .cacheExtra = .robustDigest(allPixelCDMntEnd[, .(pixelIndex, speciesCode, year, B)], quick = TRUE))
# 
# allPixelCDMntEnd[, vegTypeCN := as.factor(vegTypeCN)]
gc(reset = TRUE)


## add vegTypes at end  year - for pyrodiv HV vegTypes were classified at the end to capture
## 500 years of fire history. This was not the same in vegHV for which we sampled 5 years, each 
## with it's veg types -- this seems wrong or hard to compare but it will do for now.

## summarise fire data
summaryFireAttributes <- summariseFireRegAttrs(allPixelBurnData, allPixelCohortDataMnt,
                                               yearSubset = yearSubset, addMedian = TRUE)

## drop unused levels
allPixelCohortDataMnt$vegTypeCN <- droplevels(allPixelCohortDataMnt$vegTypeCN)
allPixelCDMntEnd$vegTypeCN <- droplevels(allPixelCDMntEnd$vegTypeCN)
summaryFireAttributes$vegTypeCN <- droplevels(summaryFireAttributes$vegTypeCN)

## get HV data
HVoutputPath <- file.path(simPaths$outputPath, "hypervolumes")
useFirstLastYear <- FALSE
source("R/R_tools/prepHVData.R")
```

```{r summaryTables, cache=FALSE, include=FALSE}
## SUMMARY ACROSS LANDSCAPE -----------------------------------
byCols <-  c("scenario", "rep", "year", "noFires")
cols <- which(as.matrix(allPixelCohortDataMnt[, lapply(.SD, is.numeric)]))
cols <- names(allPixelCohortDataMnt)[cols]
cacheExtra <- colSums(allPixelCohortDataMnt[, ..cols])

## BY SPECIES
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataSpp <- Cache(makeSummaryTable,
                                  cohortData = allPixelCohortDataMnt, 
                                  byCols = c(byCols, "speciesCode"),
                                  .cacheExtra = list(cacheExtra),
                                  cacheRepo = simPaths$cachePath,
                                  userTags = c("summaryBurnCohortDataSpp"),
                                  omitArgs = c("userTags", "cohortData"))
gc(reset = TRUE)

## BY FOREST TYPE (def. as dominant species)
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataVegType <- Cache(makeSummaryTable,
                                      cohortData = allPixelCohortDataMnt, 
                                      byCols = c(byCols, "vegType"),
                                      .cacheExtra = list(cacheExtra),
                                      cacheRepo = simPaths$cachePath,
                                      userTags = c("summaryBurnCohortDataSpp"),
                                      omitArgs = c("userTags", "cohortData"))
gc(reset = TRUE)

## BY CAMERON'S VEG TYPE
summaryBurnCohortDataVegTypeCN <- Cache(makeSummaryTable,
                                        cohortData = allPixelCohortDataMnt, 
                                        byCols = c(byCols, "vegTypeCN"),
                                        .cacheExtra = list(cacheExtra),
                                        cacheRepo = simPaths$cachePath,
                                        userTags = c("summaryBurnCohortDataSpp"),
                                        omitArgs = c("userTags", "cohortData")) 
gc(reset = TRUE)
```

```{r plotLabels, include = FALSE}
source("R/R_tools/plotLabels&Cols.R")
rm(preSimList)  ## not needed anymore
## remove large objs rasters to save memory
rm(list = c(grep("Stk", ls(), value = TRUE)))
for (i in 1:3) gc(reset = TRUE)
```

## BIOMASS, MORTALITY, AVG. AGE AND NO COHORTS BY SPECIES
```{r plotsBySpecies, cache = FALSE}
## PLOTS -----------------------------------------------
## MODELLED PROPERTIES ---------------------------------
## total biomass
## biomass
summaryBurnCohortDataSpp[, logBiomassBySpecies := log(BiomassBySpecies + 1)]

plot1 <- summaryPlot(data = summaryBurnCohortDataSpp, x = "speciesCode", y = "logBiomassBySpecies", 
                     colour = "speciesCode", xlabels = speciesLabels, colValues = speciesColours,
                     colLabels = speciesLabels, titleLab = "Total landscape biomass", 
                     subtitleLab = "by species", yLab = "log-biomass (ton/ha)",
                     x.text.angle = 45, xLab = "")
plot1 <- plot1 +
  guides(colour = "none") +
  facet_grid(scenario ~ firePresAbs, labeller = labeller(scenario = label_parsed,
                                                         firePresAbs = fireLabels))

plot2 <- summaryPlot(data = summaryBurnCohortDataSpp, x = "noFires", y = "logBiomassBySpecies", 
                     colour = "speciesCode", colValues = speciesColours, 
                     colLabels = speciesLabels, titleLab = "Total landscape biomass",
                     subtitleLab = "by species", yLab = "log-biomass (ton/ha)", xLab = "No. fires")
plot2 <- plot2 +
  stat_summary(fun = "mean", position = position_dodge(width = 0.8),
               geom = "line") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ ., labeller = labeller(scenario = label_parsed))

plot5 <- summaryPlot(data = summaryBurnCohortDataSpp, x = "speciesCode", y = "avgAgeBySppSim", 
                     colour = "speciesCode", xlabels = speciesLabels, colValues = speciesColours,
                     colLabels = speciesLabels, titleLab = "Species age", 
                     yLab = "Median biomass-weighted age",
                     x.text.angle = 45, xLab = "") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = label_parsed, firePresAbs = fireLabels))
plot5 <- plot5 +
  guides(colour = "none") +
  facet_grid(scenario ~ firePresAbs, labeller = labeller(scenario = label_parsed,
                                                         firePresAbs = fireLabels))

plot6 <- summaryPlot(data = summaryBurnCohortDataSpp, x = "noFires", y = "avgAgeBySppSim", 
                     colour = "speciesCode", colValues = speciesColours,
                     colLabels = speciesLabels, titleLab = "Species age", 
                     yLab = "Median biomass-weighted age", xLab = "No. fires") +
  stat_summary(fun = "mean", geom = "line", linewidth = 1) +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ ., labeller = label_parsed)

gc(reset = TRUE)
```

```{r plot&savePlots3, echo = FALSE}
## biomass
plotSave <- plot_grid(plot1 + theme(axis.title.x = element_blank()),
                      plot2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      nrow = 1, rel_widths = c(0.4, 0.7),
                      labels = "auto", label_size = 20, axis = "b", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeB.tiff"),
       width = 14, height = 7)

## age
plotSave <- plot_grid(plot5 + theme(axis.title.y = element_blank()),
                      plot6 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      rel_widths = c(0.4, 0.7), align = "h", axis = "b", nrow = 1,
                      labels = "auto", label_size = 20)
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAge.tiff"),
       width = 14, height = 7)

rm(plot1, plot2, plot5, plot6)
gc(reset = TRUE)
```

## COMPARING SIMULATED AND OBSERVED DATA

### Testing differences between observed and simulated data
AGES
At the end of the simulation (or averaged across sampled years), by species
```{r testAges}
## STAT TESTS ------------------------------------------
## AGE SIM VS OBS ----
## comparing simulated and observed ages
## ages compared at the species-level, rather than veg type given that some veg types in the sims don't exist
## in the obs data and this would lead to data loss
## simulated ages below the minimum DBH age (and old cohorts with low B) are excluded from comparisons.
## note that HERE species-level comparisons do not use average species ages, so the differences 
## are calculated between simulated cohort age and the observed median species age

cacheExtra <- c(digest::digest(allPixelCDMntEnd), digest::digest(ageDataCN))
opts <- options(reproducible.cachePath = simPaths$cachePath)
plotData <- Cache(
  ageComp_data,
  simData = allPixelCDMntEnd,
  obsData = ageDataCN,
  speciesTraits = speciesTraits,
  omitArgs = c("simData", "obsData", "userTags"),
  .cacheExtra = cacheExtra
)
options(opts)
plotData[, ageDiffSimObs := age - avgAgeSppObs]   ## use median species ages based on raw cohort ages at the species-level
plotData <- plotData[!is.na(ageDiffSimObs)]
plotData[firePresAbs == 1]   ## there are no observed data without fire record

ageDifflm <- lm(abs(ageDiffSimObs) ~ scenario * speciesCode, data = plotData)

savedSeed <- .Random.seed
set.seed(12345)
cacheExtra2 <- plotData[sample(1:nrow(plotData), 100),]
assign(".Random.seed", savedSeed, envir = .GlobalEnv)

## Dec 3: to repeat
ageDiffgls <- Cache(nlme::gls,
                    model = abs(ageDiffSimObs) ~ scenario * speciesCode, 
                    weights = nlme::varIdent(form = ~1|speciesCode), 
                    data = plotData,
                    omitArgs = "data",
                    .cacheExtra = cacheExtra2,
                    cacheRepo = simPaths$cachePath) ## better AIC and residuals

AICcmodavg::AICc(ageDifflm)
AICcmodavg::AICc(ageDiffgls)  ## better
# opts <- par(mfrow = c(2,2))
# plot(ageDifflm)  ## ew
# par(opts)
# plot(ageDiffgls)   ## a bit better?

plotData[, pred := predict(ageDiffgls, type = "response")]

plotTest1.2 <- ggplot(copy(plotData), aes(x = scenario)) +
  geom_boxplot(aes(y = abs(ageDiffSimObs), fill = scenario)) +
  scale_x_discrete(labels = scenLabels) +
  scale_fill_manual(values = scenColours, labels = scenLabels, guide = NULL) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", linewidth = 11/22, linetype = "dotted")) +
  labs(title = "Differences between median simulated and observed ages",
       y = expression(bgroup("|", "sim." - bar("obs."), "|")),
       x = "")

plotTest1 <- plotTest1.2 +
  facet_wrap(~ speciesCode, labeller = labeller(speciesCode = speciesLabels))
```

```{r plot&savePlots, echo = FALSE}
plotSave <- ggarrange(plotTest1, 
                      plotTest1.2, common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20),
                      widths = c(1, 0.6))
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest.tiff"),
       width = 14, height = 7)
rm(plotTest1)  ## plotTest1.2 is used again later
gc(reset = TRUE)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```

### Age violins - by species
```{r simVsObsAges, cache = FALSE}
## ageComp_data removes cohorts with age > ageAtMinDBH with Biomass < 10 
## there were some old cohorts with virtually no biomass

## At the stand-level, `ageComp_data` calculates simulated median biomass-weighted (`standAgeSim` 
## - equivalent to what was previously `median(avgAgeBySppSim)`) across species in a pixel and
## median observed basal area weighted (`avgAgeStandObs` - equivalent to what was 
## previously `median(avgAgeBySppObs)`) across species in a plot.
## At the species-level, it calculates simulated and observed median raw ages 
## for each species (`sppAgeSim` and `avgAgeSppObs`, respectively - equivalent
## to what was previously `avgAgeBySppSim` and `avgAgeBySppObs).

## note that `standAgeSim` is biomass-weighted and `sppAgeSim` isn't 
##-- we've decided to weight at the stand level but not at the species level
cacheExtra <- c(digest::digest(allPixelCDMntEnd), digest::digest(ageDataCN))
opts <- options(reproducible.cachePath = simPaths$cachePath)
plotData <- Cache(
  ageComp_data,
  simData = allPixelCDMntEnd,
  obsData = ageDataCN,
  speciesTraits = speciesTraits,
  omitArgs = c("simData", "obsData", "userTags"),
  .cacheExtra = cacheExtra)
options(opts)

## make a "landscape" species
plotData2 <- copy(plotData)
plotData2[, speciesCode := "landscape"]
plotData <- rbind(plotData, plotData2)
plotData[firePresAbs == 1]

## now get patch-level species ages, and make a landscape equivalent for it too
plotData2 <- ageDataCN[firePresAbs == 1, .(speciesCode, Reconstructed.age, firePresAbs)]  
plotData2 <- plotData2[complete.cases(plotData2)]  ## there are NA species that have ages speciesCode

plotData3 <- copy(plotData2)
plotData3[, speciesCode := "landscape"]
plotData2 <- rbind(plotData2, plotData3)

## we need to subset the data to unique values of the following columns
## since keeping raw cohort ages will create duplicate median species cohort ages.
cols <- c("scenario", "rep", "year", "speciesCode", "firePresAbs", "pixelIndex", "sppAgeSim")
plotData <- unique(plotData[, ..cols])

## this plot is used later, so the data.table must be a copy
plotData$speciesCode <- factor(plotData$speciesCode, levels = names(speciesLabels), ordered = TRUE)
plotData2$speciesCode <- factor(plotData2$speciesCode, levels = names(speciesLabels), ordered = TRUE)
plot29 <- simObsDistsPlot(simData = copy(plotData), 
                          x = "speciesCode", ySim = "sppAgeSim",
                          colSim = "scenario", 
                          obsData = copy(plotData2), yObs = "Reconstructed.age", 
                          xlabels = speciesLabels, x.text.angle = 45,
                          colValues = scenColours, 
                          colLabels = scenLabels, 
                          titleLab = "Species age", yLab = "years") +
  theme(axis.title.x = element_blank())

## no means/whiskers
plot29.1 <- simObsDistsPlot(simData = copy(plotData), 
                            x = "speciesCode", ySim = "sppAgeSim",
                            colSim = "scenario", 
                            obsData = copy(plotData2), yObs = "Reconstructed.age", 
                            xlabels = speciesLabels, x.text.angle = 45,
                            colValues = scenColours, 
                            colLabels = scenLabels, 
                            showMeans = FALSE,
                            titleLab = "Species age", yLab = "years") + 
  theme(axis.title.x = element_blank())
```

```{r plot&savePlots7, echo = FALSE}
ggsave(plot = plot29, filename = file.path(figOutputPath, "results_ageSimVsObs.tiff"),
       width = 14, height = 7)

ggsave(plot = plot29.1, filename = file.path(figOutputPath, "results_ageSimVsObs2.tiff"),
       width = 14, height = 7)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```

### Age violins - by forest type
Forest types are defined for a sample of years across the quasi equilibrium period.
Non-forest forest type removed -- not present in observed data, so could impact "landscape" comparisons

```{r simVsObsAges_vegType, cache = FALSE}
## age distribution at "end" of simulation vs cameron's

## ageComp_data removes cohorts with age > ageAtMinDBH with Biomass < 10 
## there were some old cohorts with virtually no biomass

## At the stand-level, `ageComp_data` calculates simulated median biomass-weighted (`standAgeSim` 
## - equivalent to what was previously `median(avgAgeBySppSim)`) across species in a pixel and
## median observed basal area weighted (`avgAgeStandObs` - equivalent to what was 
## previously `median(avgAgeBySppObs)`) across species in a plot.
## At the species-level, it calculates simulated and observed median raw ages 
## for each species (`sppAgeSim` and `avgAgeSppObs`, respectively - equivalent
## to what was previously `avgAgeBySppSim` and `avgAgeBySppObs).

## note that `standAgeSim` is biomass-weighted and `sppAgeSim` isn't 
##-- we've decided to weight at the stand level but not at the species level

cacheExtra <- c(digest::digest(allPixelCDMntEnd), digest::digest(ageDataCN))
opts <- options(reproducible.cachePath = simPaths$cachePath)
plotData <- Cache(
  ageComp_data,
  simData = allPixelCDMntEnd,
  obsData = ageDataCN,
  speciesTraits = speciesTraits,
  omitArgs = c("simData", "obsData", "userTags"),
  .cacheExtra = cacheExtra)
options(opts)

## make a "landscape" species
plotData2 <- copy(plotData)
plotData2[, vegTypeCN := "landscape"]
plotData <- rbind(plotData, plotData2)
plotData[firePresAbs == 1]

## now get patch-level stand ages, and make a landscape equivalent for it too
plotData2 <- ageDataCN[firePresAbs == 1, .(Cover.dendro, Stand.age.3, firePresAbs)]  
plotData2 <- plotData2[complete.cases(plotData2)]  ## there are NA species that have ages speciesCode

plotData3 <- copy(plotData2)
plotData3[, Cover.dendro := "landscape"]
plotData2 <- rbind(plotData2, plotData3)

setnames(plotData2, "Cover.dendro", "vegTypeCN")

## we need to subset the data to unique values of the following columns
## since keeping raw cohort ages will create duplicate median species cohort ages.
cols <- c("scenario", "rep", "year", "vegTypeCN", "firePresAbs", "pixelIndex", "standAgeSim")
plotData <- unique(plotData[, ..cols])

plotData$vegTypeCN <- factor(plotData$vegTypeCN, levels = names(vegTypeCNLabels), ordered = TRUE)
plotData2$vegTypeCN <- factor(plotData2$vegTypeCN, levels = names(vegTypeCNLabels), ordered = TRUE)
plot29.2 <- simObsDistsPlot(simData = copy(plotData), x = "vegTypeCN", ySim = "standAgeSim",
                            colSim = "scenario", obsData = copy(plotData2), yObs = "Stand.age.3", 
                            xlabels = vegTypeCNLabels, x.text.angle = 45,
                            colValues = scenColours, 
                            colLabels = scenLabels, 
                            titleLab = "Stand age", subtitleLab = "by forest type", yLab = "years")

## no means
plot29.3 <- simObsDistsPlot(simData = copy(plotData), 
                            x = "vegTypeCN", ySim = "standAgeSim",
                            obsData = copy(plotData2), yObs = "Stand.age.3",
                            colSim = "scenario", x.text.angle = 45,
                            xlabels = vegTypeCNLabels, showMeans = FALSE,
                            colValues = scenColours, 
                            colLabels = scenLabels, 
                            titleLab = "Stand age", subtitleLab = "by forest type", yLab = "years") 
```

```{r plot&savePlots8, echo = FALSE}
ggsave(plot = plot29.2, filename = file.path(figOutputPath, "results_ageSimVsObsVegTypeCN.tiff"),
       width = 14, height = 7)
ggsave(plot = plot29.3, filename = file.path(figOutputPath, "results_ageSimVsObsVegTypeCN2.tiff"),
       width = 14, height = 7)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```

### Mean (absolute) deviations and quantile deviations of simulated ages by stand type
(deviations from observed median & quantile - 50, 75, 95%)

Forest types are defined for a sample of years across the quasi equilibrium period.
Non-forest forest type removed -- not present in observed data, so could impact "landscape" comparisons

```{r simVsObsAgesDif, cache = FALSE}
## ageComp_data removes cohorts with age > ageAtMinDBH with Biomass < 10 
## there were some old cohorts with virtually no biomass

## At the stand-level, `ageComp_data` calculates simulated median biomass-weighted (`standAgeSim` 
## - equivalent to what was previously `median(avgAgeBySppSim)`) across species in a pixel and
## median observed basal area weighted (`avgAgeStandObs` - equivalent to what was 
## previously `median(avgAgeBySppObs)`) across species in a plot.
## At the species-level, it calculates simulated and observed median raw ages 
## for each species (`sppAgeSim` and `avgAgeSppObs`, respectively - equivalent
## to what was previously `avgAgeBySppSim` and `avgAgeBySppObs).

## note that `standAgeSim` is biomass-weighted and `sppAgeSim` isn't 
##-- we've decided to weight at the stand level but not at the species level
opts <- options(reproducible.cachePath = simPaths$cachePath)
cacheExtra <- c(digest::digest(allPixelCDMntEnd), digest::digest(ageDataCN))
plotData <- Cache(
  ageComp_data,
  simData = allPixelCDMntEnd,
  obsData = ageDataCN,
  speciesTraits = speciesTraits,
  addLandscape = TRUE,
  speciesLevel = FALSE,
  omitArgs = c("simData", "obsData", "userTags"),
  .cacheExtra = cacheExtra)
options(opts)

plotData[, speciesCode := NULL]
plotData <- plotData[!is.na(avgAgeStandObs)]

## we need to subset the data to unique values of the following columns
## since keeping raw cohort ages will create duplicate median species cohort ages.
cols <- c("scenario", "rep", "year", "vegTypeCN", "firePresAbs", "pixelIndex", "standAgeSim", "avgAgeStandObs")
plotData <- unique(plotData[, ..cols])

plotData[, rawDevsSimObs := standAgeSim - avgAgeStandObs]

## MADs for age are no longer analysed -- note that here 'years' are dealt in the same way as pixels
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(standAgeSim - avgAgeStandObs))),
                      by = .(scenario, rep, vegTypeCN, firePresAbs)]

## differences from the observed median
x_order <- names(vegTypeCNLabels[vegTypeCNLabels != "No forest"])
plot32 <- DevPlot(plotData, x = "vegTypeCN", y = "rawDevsSimObs",
                  fill = "scenario", xlabels = vegTypeCNLabels, xorder = x_order,
                  fillLabels = scenLabels, fillValues = scenColours,
                  titleLab = "Differences from median observed ages",
                  yLab = expression("sim." - bar("obs.")))


## mean absolute differences -- note CIs are bootstrapped CLs
plot32.2 <- MADPlot(plotData2, x = "vegTypeCN", y = "meanAbsDevSimObs", 
                    colour = "scenario", colValues = scenColours, 
                    colLabels = scenLabels, xlabels = vegTypeCNLabels,
                    xorder = rev(x_order), flipCoord = FALSE,  
                    titleLab = "Mean abs. deviations from observed ages",
                    # yLab = expression(bar(bgroup("|", "sim." - bar("obs."), "|")))) 
                    yLab = "Mean abs. deviation")

## QUANTILE DEVIATIONS
## forest-type-level differences between simulated and observed upper quantiles

## we can use sppAgeSim, because it's at pixel-level.
plotData <- plotData[, `:=`(quant50StandAge = quantile(standAgeSim, probs = 0.5, na.rm = TRUE),
                            quant75StandAge = quantile(standAgeSim, probs = 0.75, na.rm = TRUE),
                            quant95StandAge = quantile(standAgeSim, probs = 0.95, na.rm = TRUE)),
                     by = .(scenario, rep, firePresAbs, vegTypeCN)]

## we need to use ageDataCN, to get the patch-level ages.
plotData2 <- rbind(
  ageDataCN[, list(quant50StandAgeObs = quantile(Stand.age.3, probs = 0.5, na.rm = TRUE),
                   quant75StandAgeObs = quantile(Stand.age.3, probs = 0.75, na.rm = TRUE),
                   quant95StandAgeObs = quantile(Stand.age.3, probs = 0.95, na.rm = TRUE)), 
            by = .(Cover.dendro, firePresAbs)],
  ageDataCN[, list(quant50StandAgeObs = quantile(Stand.age.3, probs = 0.5, na.rm = TRUE),
                   quant75StandAgeObs = quantile(Stand.age.3, probs = 0.75, na.rm = TRUE),
                   quant95StandAgeObs = quantile(Stand.age.3, probs = 0.95, na.rm = TRUE),
                   Cover.dendro = "landscape"), 
            by = .(firePresAbs)])
setnames(plotData2, "Cover.dendro", "vegTypeCN")

plotData2[, firePresAbs := as.factor(firePresAbs)]
plotData <- plotData2[plotData, on = c("vegTypeCN", "firePresAbs")]
plotData <- plotData[!is.na(quant50StandAgeObs)]
if (any(is.na(plotData))) stop("Something is wrong.")

plotData2 <- unique(plotData[, list(devSimObsQuant50 = quant50StandAge - quant50StandAgeObs,
                                    devSimObsQuant75 = quant75StandAge - quant75StandAgeObs,
                                    devSimObsQuant95 = quant95StandAge - quant95StandAgeObs),
                             by = .(scenario, rep, vegTypeCN, firePresAbs)])
plotData2 <- melt(plotData2, id.vars = c("scenario", "rep", "vegTypeCN", "firePresAbs"))

plotData2 <- plotData2[firePresAbs == "1"]

## only pixels with fire
## order veg types, with landscape at the end
factorLevs <- c(as.character(sort(setdiff(unique(plotData2$vegTypeCN), "landscape"))), "landscape")
plotData2[, vegTypeCN := factor(vegTypeCN, levels = factorLevs)]

plot32.3 <- ggplot(plotData2[firePresAbs == "1"], 
                   aes(x = variable, y = value, colour = scenario, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               size = 0.7) +
  scale_x_discrete(labels = c("devSimObsQuant50" = "50%", 
                              "devSimObsQuant75" = "75%", 
                              "devSimObsQuant95" = "95%")) +
  scale_shape_discrete(labels = scenLabels, name = "") +
  scale_color_discrete(labels = scenLabels, name = "") +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(title = "Quantile deviation", x = "", 
       y = expression("quantAge"["sim."] - "quantAge"["obs."])) +
  facet_wrap(~ vegTypeCN, scales = "free_x", ncol = 4,
             labeller = labeller(vegTypeCN = vegTypeCNLabels))

```

```{r plot&savePlots13, echo = FALSE}
plot32
ggsave(plot = plot32 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAgeDiffVegTypeCN.tiff"),
       width = 14, height = 7)
plot32.2
ggsave(plot = plot32.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsAgeDevVegTypeCN.tiff"),
       width = 10, height = 5)
plot32.3
ggsave(plot = plot32.3 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_DIFquantVegTypeCNs.tiff"),
       width = 10, height = 6)

plotSave <- plot_grid(plot29.2 + theme(legend.position = "right", plot.title = element_blank()),
                      plot32.2 + theme(legend.position = "right", plot.title = element_blank()),
                      labels = c("a", "b"), label_size = 20,
                      nrow = 2, axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MAD_VegTypeCN.tiff"),
       width = 12, height = 10)

plotSave <- plot_grid(plot29.2 + theme(legend.position = "right", plot.title = element_blank(), plot.subtitle = element_blank()),
                      plot32.3 + theme(legend.position = "right", plot.title = element_blank()),
                      labels = c("a", "b"), label_size = 20,
                      nrow = 2, rel_heights = c(0.8, 1), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_DIFquant_VegTypeCN.tiff"),
       width = 10, height = 10)

plotSave <- plot_grid(plot29.3 + theme(legend.position = "right", plot.title = element_blank(), plot.subtitle = element_blank()),
                      plot32.3 + theme(legend.position = "right", plot.title = element_blank()),
                      labels = c("a", "b"), label_size = 20,
                      nrow = 2, axis = "lr", align = "v")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_DIFquant_VegTypeCN2.tiff"),
       width = 10, height = 10)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```

### Mean (absolute) deviations and quantile deviations of simulated ages by species
(deviations from observed median & quantile - 50, 75, 95%)

```{r simVsObsAgesDif2, cache = FALSE}
## ageComp_data removes cohorts with age > ageAtMinDBH with Biomass < 10 
## there were some old cohorts with virtually no biomass

## At the stand-level, `ageComp_data` calculates simulated median biomass-weighted (`standAgeSim` 
## - equivalent to what was previously `median(avgAgeBySppSim)`) across species in a pixel and
## median observed basal area weighted (`avgAgeStandObs` - equivalent to what was 
## previously `median(avgAgeBySppObs)`) across species in a plot.
## At the species-level, it calculates simulated and observed median raw ages 
## for each species (`sppAgeSim` and `avgAgeSppObs`, respectively - equivalent
## to what was previously `avgAgeBySppSim` and `avgAgeBySppObs).

## note that `standAgeSim` is biomass-weighted and `sppAgeSim` isn't 
##-- we've decided to weight at the stand level but not at the species level
opts <- options(reproducible.cachePath = simPaths$cachePath)
cacheExtra <- c(digest::digest(allPixelCDMntEnd), digest::digest(ageDataCN))
plotData <- Cache(
  ageComp_data,
  simData = allPixelCDMntEnd,
  obsData = ageDataCN,
  speciesTraits = speciesTraits,
  addLandscape = TRUE,
  speciesLevel = TRUE,
  omitArgs = c("simData", "obsData", "userTags"),
  .cacheExtra = cacheExtra)
options(opts)

plotData <- plotData[!is.na(avgAgeSppObs)]

## we need to subset the data to unique values of the following columns
## since keeping raw cohort ages will create duplicate median species cohort ages.
cols <- c("scenario", "rep", "year", "speciesCode", "firePresAbs", "pixelIndex", "sppAgeSim", "avgAgeSppObs")
plotData <- unique(plotData[, ..cols])

plotData[, rawDevsSimObs := sppAgeSim - avgAgeSppObs]

## MADs for age are no longer analysed -- note that here 'years' are dealt in the same way as pixels
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(rawDevsSimObs))),
                      by = .(scenario, rep, speciesCode, firePresAbs)]

## differences from the observed median
plot43 <- DevPlot(plotData, x = "speciesCode", y = "rawDevsSimObs",
                  fill = "scenario", xlabels = speciesLabels, fillValues = scenColours,
                  fillLabels = scenLabels, xFacet = "firePresAbs", 
                  labllr = labeller(firePresAbs = fireLabels),
                  titleLab = "Differences from median observed ages",
                  yLab = expression("sim." - bar("obs.")))

## mean absolute differences
plot43.2 <- MADPlot(plotData2, x = "speciesCode", y = "meanAbsDevSimObs", 
                    colour = "scenario", colValues = scenColours, colLabels = scenLabels, 
                    xlabels = c(speciesLabels, landscape = "landscape"),
                    xorder = rev(c(names(speciesLabels), "landscape")), 
                    flipCoord = FALSE,
                    # xFacet = "firePresAbs", 
                    labllr = labeller(firePresAbs = fireLabels),
                    titleLab = "Mean abs. deviations from observed ages",
                    # yLab = expression(bar(bgroup("|", "sim." - bar("obs."), "|")))) 
                    yLab = "Mean abs. deviation")


## QUANTILE DEVIATIONS
## species-level differences between simulated and observed upper quantiles

## we can use sppAgeSim, because it's at pixel-level.
plotData <- plotData[, `:=`(quant50SppAge = quantile(sppAgeSim, probs = 0.5, na.rm = TRUE),
                            quant75SppAge = quantile(sppAgeSim, probs = 0.75, na.rm = TRUE),
                            quant95SppAge = quantile(sppAgeSim, probs = 0.95, na.rm = TRUE)),
                     by = .(scenario, rep, firePresAbs, speciesCode)]

## we need to use ageDataCN, to get the patch-level ages.
plotData2 <- rbind(
  ageDataCN[, list(quant50SppAgeObs = quantile(Reconstructed.age, probs = 0.5, na.rm = TRUE),
                   quant75SppAgeObs = quantile(Reconstructed.age, probs = 0.75, na.rm = TRUE),
                   quant95SppAgeObs = quantile(Reconstructed.age, probs = 0.95, na.rm = TRUE)), 
            by = .(speciesCode, firePresAbs)],
  ageDataCN[, list(quant50SppAgeObs = quantile(Reconstructed.age, probs = 0.5, na.rm = TRUE),
                   quant75SppAgeObs = quantile(Reconstructed.age, probs = 0.75, na.rm = TRUE),
                   quant95SppAgeObs = quantile(Reconstructed.age, probs = 0.95, na.rm = TRUE),
                   speciesCode = "landscape"), 
            by = .(firePresAbs)])

plotData2[, firePresAbs := as.factor(firePresAbs)]
plotData <- plotData2[plotData, on = c("speciesCode", "firePresAbs")]
plotData <- plotData[!is.na(quant50SppAgeObs)]

if (any(is.na(plotData))) stop("Something is wrong.")

plotData2 <- unique(plotData[, list(devSimObsQuant50 = quant50SppAge - quant50SppAgeObs,
                                    devSimObsQuant75 = quant75SppAge - quant75SppAgeObs,
                                    devSimObsQuant95 = quant95SppAge - quant95SppAgeObs),
                             by = .(scenario, rep, speciesCode, firePresAbs)])

plotData2 <- melt(plotData2, id.vars = c("scenario", "rep", "speciesCode", "firePresAbs"))

## only pixels with fire
## order veg types, with landscape at the end
factorLevs <- c(as.character(sort(setdiff(unique(plotData2$speciesCode), "landscape"))), "landscape")
plotData2[, speciesCode := factor(speciesCode, levels = factorLevs)]

plot43.3 <- ggplot(plotData2[firePresAbs == "1"], 
                   aes(x = variable, y = value, colour = scenario, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               size = 1) +
  scale_x_discrete(labels = c("devSimObsQuant50" = "50%", 
                              "devSimObsQuant75" = "75%", 
                              "devSimObsQuant95" = "95%")) +
  scale_shape_discrete(labels = scenLabels, name = "") +
  scale_color_discrete(labels = scenLabels, name = "") +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(title = "Quantile absolute deviation", x = "", 
       y = expression("quantAge"["sim."] - "quantAge"["obs."])) +
  facet_wrap(~ speciesCode, scales = "free_x", ncol = 3,
             labeller = labeller(speciesCode = c(speciesLabels, landscape = "landscape")))
```

```{r plot&savePlots14, echo = FALSE}
plot43
ggsave(plot = plot43 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAgeDiffSpecies.tiff"),
       width = 14, height = 7)
plot43.2
ggsave(plot = plot43.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsAgeDevSpecies.tiff"),
       width = 10, height = 5)

plot43.3
ggsave(plot = plot43.3 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_DIFquantSpecies.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(plot_grid(plot43 + theme(plot.title = element_blank(), legend.position = "none"),
                                plotTest1.2 + theme(plot.title = element_blank(), legend.position = "none"),
                                ncol = 2, nrow = 1, align = "h", axis = "b",
                                labels = "auto", label_size = 20,
                                rel_widths = c(1, 0.7)), 
                      get_legend(plot43 + theme(plot.title = element_blank(), legend.direction = "vertical")),
                      ncol = 2, nrow = 1, rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_meanAbsAgeDev_ageSimVsObsTestSpecies.tiff"),
       width = 15, height = 7)

plotSave <- plot_grid(plot29 + theme(legend.position = "right", plot.title = element_blank()),
                      plot43.2 + theme(legend.position = "right", plot.title = element_blank()),
                      labels = c("a", "b"), label_size = 20,
                      nrow = 2, rel_heights = c(1, 0.7), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MAD_Species.tiff"),
       width = 10, height = 10)

plotSave <- plot_grid(plot29 + theme(legend.position = "right",
                                     plot.title = element_blank(),
                                     legend.direction = "vertical",
                                     legend.box = "vertical"),
                      plot43.3 + theme(legend.position = "right",
                                       plot.title = element_blank(),
                                       legend.direction = "vertical",
                                       legend.box = "vertical"),
                      labels = c("a", "b"), label_size = 20,
                      nrow = 2, rel_heights = c(0.8, 1), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_DIFquant_Species.tiff"),
       width = 10, height = 10)

plotSave <- plot_grid(plot29.1 + theme(legend.position = "right",
                                       plot.title = element_blank(),
                                       legend.direction = "vertical",
                                       legend.box = "vertical"),
                      plot43.3 + theme(legend.position = "right",
                                       plot.title = element_blank(),
                                       legend.direction = "vertical",
                                       legend.box = "vertical"),
                      labels = c("a", "b"), label_size = 20,
                      nrow = 2, rel_heights = c(0.8, 1), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_DIFquant_Species2.tiff"),
       width = 10, height = 10)

# rm(plot43, plot43.2, plotTest1.2)
gc(reset = TRUE)
```

### No. fires, fire frequency, fire size and fire severity
```{r simVsObsFires, cache = FALSE}
## average no. of pixels with certain fire frequency
plotData <- allPixelCohortDataMnt[, list(noPixels = length(unique(pixelIndex))),
                                  by = .(scenario, rep, year, noFires)]
plot38 <- ggplot(copy(plotData),
                 aes(x = as.factor(noFires), y = noPixels, fill = scenario)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge", alpha = 0.5) +
  stat_summary(fun.data = "mean_sd", aes(colour = scenario),
               geom = "errorbar", position = "dodge", show.legend = FALSE) +
  stat_summary(aes(label = round(..y..), colour = scenario),
               fun = "mean", geom = "text", show.legend = FALSE,
               position = position_dodge(width = 0.9), vjust = -1) +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "no. fires", y = "no. pixels")

## average no. of fires per forest type across quasi-equilibrium period
plotData <- allPixelCDMntEnd[vegTypeCN != "No veg.", 
                             list(meanNoFires = mean(noFires),
                                  sdNoFires = sd(noFires)),
                             by = .(scenario, vegTypeCN)]
plot36 <- ggplot(copy(plotData)) +
  geom_bar(aes(x = vegTypeCN, y = meanNoFires, fill = scenario),
           position = "dodge", stat = "identity", alpha = 0.5) +
  geom_errorbar(aes(x = vegTypeCN,
                    ymin = meanNoFires - sdNoFires, 
                    ymax = meanNoFires + sdNoFires,
                    colour = scenario),
                position = "dodge", show.legend = FALSE) +
  scale_fill_discrete(labels = scenLabels) +
  scale_colour_discrete(labels = scenLabels) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(y = "no. fires", x = "")


## fire size distribution
## add + 1 because densityPlot uses a log scale
plotData <- summaryFireAttributes[vegTypeCN != "No veg."]
plotData[, `:=`(meanPatchS1 = meanPatchS + 1,
                meanFreq1 = meanFreq + 1,
                meanSevB1 = meanSevB + 1)]
plot37 <- densityPlot(copy(plotData), 
                      x = "meanPatchS1", fill = "scenario", alpha = "scenario",
                      fillValues = scenColours, fillLabels = scenLabels, 
                      alphaValues = c("PM" = 0.6, "noPM" = 1),
                      titleLab = "Fire patch size distribution",
                      xLab = "Mean patch size (no. pixels)")

plot37.2 <- plot37 +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## only simulated fire intervals
plot39.3 <- densityPlot(copy(plotData), 
                        x = "meanFreq1", fill = "scenario", alpha = "scenario",
                        fillValues = scenColours, fillLabels = scenLabels, 
                        alphaValues = c("PM" = 0.6, "noPM" = 1),
                        titleLab = "Fire interval distribution",
                        xLab = "Mean fire interval")

plot39.4 <- plot39.3 + 
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## distribution of fire severity per stand across landscape
## TODO: change to sevPropB
plot40 <- densityPlot(copy(plotData), 
                      x = "meanSevB1", fill = "scenario", alpha = "scenario",
                      fillValues = scenColours, fillLabels = scenLabels, 
                      alphaValues = c("PM" = 0.6, "noPM" = 1),
                      titleLab = "Fire severity distribution",
                      xLab = "Mean fire severity\n(biomass lost, ton/ha)")

## distribution of fire severity per stand by veg types defined for a sample of years across the quasi equilibrium period.
## TODO: change to sevPropB
## as used for HVs
plot41 <- plot40 +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## distribution of fire severity by veg types defined every year
## so not always the same pixels
plotData <- unique(allPixelCohortDataMnt[vegTypeCN != "No veg.", .(scenario, rep, year, pixelIndex, vegTypeCN)])
plotData <- summaryFireAttributes[vegTypeCN != "No veg.",
                                  .(scenario, rep, pixelIndex, meanSevB)][plotData, on = .(scenario, rep, pixelIndex)]
plotData[, meanSevB1 := meanSevB]
plot42 <- densityPlot(copy(plotData), 
                      x = "meanSevB1", fill = "scenario", alpha = "scenario",
                      fillValues = scenColours, fillLabels = scenLabels, 
                      alphaValues = c("PM" = 0.6, "noPM" = 1),
                      titleLab = "Fire severity distribution",
                      xLab = "Mean fire severity\n(biomass lost, ton/ha)")
plot42 <- plot42 +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))
```

```{r plot&savePlots15, echo = FALSE}
plotSave <- ggarrange(plot37 + theme(plot.title = element_blank()), 
                      plot37.2 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "results_meanPatchSizeDist.tiff"),
       width = 16, height = 6)
ggsave(plot = plot36 + theme(legend.position = c(0.9, 0.9), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_noFiresVegTypeCN.tiff"),
       width = 8, height = 7)
ggsave(plot = plot38 + theme(legend.position = c(0.9, 0.9), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_noPixelsVsnoFires.tiff"),
       width = 8, height = 7)
plotSave <- ggarrange(plot39.3 + theme(plot.title = element_blank()), 
                      plot39.4 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "results_meanFireIntDist.tiff"),
       width = 16, height = 6)

plotSave <- ggarrange(plot40 + theme(plot.title = element_blank()), 
                      plot41 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "results_meanSevDist.tiff"),
       width = 16, height = 6)

ggsave(plot = plot42 + theme(legend.position = c(0.9, 0.1), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_meanSevDist_sampleYearVegTypeCN.tiff"),
       width = 10, height = 8)

plotSave <- ggarrange(plot37 + theme(plot.title = element_blank()),
                      plot37.2 + theme(plot.title = element_blank()),
                      plot39.3, 
                      plot39.4 + theme(plot.title = element_blank()),
                      plot40, 
                      plot41 + theme(plot.title = element_blank()),
                      common.legend = TRUE, legend = "bottom",
                      nrow = 3, ncol = 2, widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", align = "hv")
ggsave(plot = plotSave,
       filename = file.path(figOutputPath, "results_fireAttrLandscape.tiff"),
       width = 16, height = 12)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```

#### Boxplots of  no. fires, fire frequency, fire size and fire severity (means as in HVs)
Non-forest forest types and pixels w/o included since these plots are showing data used for PBRs
```{r fireAttr_boxplots, cache = FALSE}
x_order <- names(vegTypeCNLabels)
## fire size
plotData <- copy(summaryFireAttributes)

factorLevs <- c(
  as.character(sort(setdiff(unique(plotData$vegTypeCN), c("landscape", "No veg.")))),
  "No veg.", "landscape")
plotData[, vegTypeCN := factor(vegTypeCN, levels = factorLevs)]

## add 1 for log scale
# plotData[, `:=`(meanPatchS1 = meanPatchS + 1,
#                 meanFreq1 = meanFreq + 1,
#                 meanSevB1 = meanSevB + 1)]
plot45 <- boxPlot(plotData, x = "vegTypeCN", y = "meanPatchS", logY = FALSE,
                  fill = "scenario", xlabels = vegTypeCNLabels, xorder = x_order,
                  fillValues = scenColours, fillLabels = scenLabels,
                  titleLab = NULL, yLab = "Mean patch size")

plot46 <- boxPlot(plotData, x = "vegTypeCN", y = "meanFreq", logY = FALSE,
                  fill = "scenario", xlabels = vegTypeCNLabels, xorder = x_order,
                  fillValues = scenColours, fillLabels = scenLabels,
                  titleLab = NULL, yLab = "Mean fire interval")

## fire severity
plot47 <- boxPlot(plotData, x = "vegTypeCN", y = "meanSevPropB", logY = FALSE, 
                  fill = "scenario", xlabels = vegTypeCNLabels, xorder = x_order,
                  fillValues = scenColours, fillLabels = scenLabels,
                  titleLab = NULL, yLab = "Mean fire severity")
```

```{r plot&savePlots17, echo = FALSE}
plotSave <- ggarrange(plot45,
                      plot46, 
                      plot47, 
                      common.legend = TRUE, legend = "bottom",
                      ncol = 1,
                      font.label = list(size = 20),
                      labels = "auto")
ggsave(plot = plotSave,
       filename = file.path(figOutputPath, "results_fireAttrLandscape_boxplots.tiff"),
       width = 13, height = 12, dpi = 300)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```


### "Fire regime" plots
As in Cameron & Daniels 2020 (Fig. 9b,c): median and  SD of fire interval~severity, per forest type

```{r fireAttr_boxplots, cache = FALSE}
plotData <- summaryFireAttributes[vegTypeCN != "No veg.", 
                                  list(meanFreq_median = median(meanFreq),
                                       meanFreq_sd = sd(meanFreq),
                                       meanSevB_median = median(meanSevB),
                                       meanSevB_sd = sd(meanSevB)),
                                  by = .(scenario, vegTypeCN)]

plotData$scenario <- as.character(scenLabels[match(plotData$scenario, names(scenLabels))])

jitter_wd <- 100
jitter_hg <- 5
jitter_sd <- 456
plot48 <- ggplot(plotData, aes(y = meanFreq_median, x = meanSevB_median, colour = vegTypeCN)) +
  geom_point(size = 2, alpha = 0.5, 
             position = position_jitter(width = jitter_wd, height = jitter_hg, seed = jitter_sd)) +
  geom_errorbar(aes(ymin = meanFreq_median - meanFreq_sd, 
                    ymax = meanFreq_median + meanFreq_sd),
                alpha = 0.5, 
                position = position_jitter(width = jitter_wd, height = jitter_hg, seed = jitter_sd)) +
  geom_errorbar(aes(xmin = meanSevB_median - meanSevB_sd, 
                    xmax = meanSevB_median + meanSevB_sd),
                alpha = 0.5, 
                position = position_jitter(width = jitter_wd, height = jitter_hg, seed = jitter_sd),
                orientation = "y") +
  scale_colour_manual(labels = vegTypeCNLabels[names(vegTypeCNLabels) %in% plotData$vegTypeCN],
                      values = vegTypeCNColours[names(vegTypeCNLabels) %in% plotData$vegTypeCN]) +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(x = "Mean fire severity\n(biomass lost, ton/ha)",
       y = "Mean fire interval (years)") +
  facet_wrap(~ scenario, labeller = label_parsed)

```

```{r plot&savePlots16, echo = FALSE}
ggsave(plot = plot48, filename = file.path(figOutputPath, "results_fireRegime_crossPlot.tiff"),
       width = 8, height = 6)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```


### Fire interval comparisons  with observed data
Non-forest forest type removed, only pixel/plots with fire evidence
Note that `summaryFireAttributes`  has pixels with fire and without fires. So pixels without fires need to be removed
Also, in the observed data mean/median fire intervals were not calculated for plots that had one fire event only. So pixels with a single fire event are also removed
```{r simVsObsFires, cache = FALSE}
## allPixelBurnData only has burnt pixels, use it to filter summaryFireAttributes
pixWFires <- unique(allPixelBurnData[noFires > 1, .(scenario, rep, pixelIndex)])

## median fire interval per forest type - to compare with camerons fire intervals.
plotData <- summaryFireAttributes[pixWFires, on = .(scenario, rep, pixelIndex), nomatch = 0]
plotData <- plotData[vegTypeCN %in% ageDataCN$Cover.dendro, 
                     .(scenario, rep, pixelIndex, medianFreq, vegTypeCN)] 
plotData2 <- copy(plotData)
plotData2[, vegTypeCN := "landscape"]
plotData <- rbind(plotData, plotData2)

plotData2 <- unique(ageDataCN[firePresAbs > 0, .(Cover.dendro, median.FI, Patch.ID)])
plotData3 <- copy(plotData2)
plotData3[, Cover.dendro := "landscape"]
plotData2 <- rbind(plotData2, plotData3)

setnames(plotData2, "Cover.dendro", "vegTypeCN")

plot39 <- simObsDistsPlot(simData = copy(plotData), x = "vegTypeCN", ySim = "medianFreq", 
                          colSim = "scenario",
                          obsData = copy(plotData2), yObs = "median.FI", xlabels = vegTypeCNLabels,
                          colValues = scenColours, colLabels = scenLabels, x.text.angle = 45,
                          showMeans = FALSE,
                          titleLab = "Median fire interval", subtitleLab = "by forest type",
                          yLab = "Fire interval")
plot39 <- plot39 + 
  geom_point(data = copy(plotData2[vegTypeCN %in% c("broadleaf", "PIEN")]),   ## these only have one point
             aes(x = vegTypeCN, y = median.FI, colour = "observed"),
             position = position_dodge(width = 0.9), show.legend = FALSE) 
```

```{r plot&savePlots16, echo = FALSE}
ggsave(plot = plot39, filename = file.path(figOutputPath, "results_meanFireIntSimVsObs.tiff"),
       width = 10, height = 8)
plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```


### Mean absolute deviation and mean raw deviations of simulated fire intervals with respect to observed fire intervals for a given stand type
Non-forest forest type removed (not present in observed data), only pixel/plots with fire evidence
Note that `summaryFireAttributes` has pixels with fire evidence -- fire intervals of 0 correspond to pixels that only had one fire in the first year of the analysed period.

```{r simVsObsFires2, cache = FALSE}
## average fire interval differences
## calculate the average observed median fire interval first
## then the absolute difference of each pixel's simulated median fire interval to the observed average (per veg type)
## and average across pixels and repliates
## allPixelBurnData only has burnt pixels, use it to filter summaryFireAttributes
pixWFires <- unique(allPixelBurnData[noFires > 1, .(scenario, rep, pixelIndex)])
## mean fire interval per forest type - to compare with camerons fire intervals.
plotData <- summaryFireAttributes[vegTypeCN != "No veg."][pixWFires, 
                                                          on = .(scenario, rep, pixelIndex), nomatch = 0]
plotData2 <- copy(plotData)
plotData2[, vegTypeCN := "landscape"]
plotData <- rbind(plotData, plotData2)

## vegType MADs first
plotData2 <- ageDataCN[firePresAbs > 0,]
plotData3 <- copy(plotData2)
plotData3[, Cover.dendro := "landscape"]
plotData2 <- rbind(plotData2, plotData3)
plotData2 <- plotData2[, list(avgMedian.FIObs = mean(median.FI, na.rm = TRUE)),
                       by = .(Cover.dendro)]

setnames(plotData2, "Cover.dendro", "vegTypeCN")
plotData <- plotData2[plotData, on = "vegTypeCN", nomatch = NULL]

if (nrow(plotData[is.na(avgMedian.FIObs) | is.na(medianFreq)])) {
  stop("NAs detected")
}

plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(medianFreq - avgMedian.FIObs))),
                      by = .(scenario, rep, vegTypeCN)]

## boxplot differences
plot44 <- ggplot(plotData,
                 aes(x = vegTypeCN,
                     y = meanFreq - avgMedian.FIObs,
                     fill = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  geom_boxplot() +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", linewidth = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  labs(title = "Avg. differences from observed fire intervals",
       y = expression("sim." - bar("obs.")), x = "")

## mean absolute differences
x_order <- names(vegTypeCNLabels[vegTypeCNLabels != "No forest"])
plot44.2 <- MADPlot(plotData2, x = "vegTypeCN", y = "meanAbsDevSimObs",
                    colour = "scenario", colValues = scenColours, colLabels = scenLabels,
                    labllr, xlabels = vegTypeCNLabels, xorder = rev(x_order),
                    x.text.angle = 45, flipCoord = FALSE,
                    titleLab = "Mean abs. deviation from observed median fire intervals", 
                    yLab = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))))

```

```{r plot&savePlots18, echo = FALSE}
plot44
ggsave(plot = plot44 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanFIDiff.tiff"),
       width = 14, height = 7)
plot44.2
ggsave(plot = plot44.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsFIDev.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(plot39 + theme(plot.title = element_blank(), plot.subtitle = element_blank(), 
                                     axis.title.x = element_blank(), legend.position = "right"),
                      plot44.2 + theme(legend.position = "right",
                                       plot.title = element_blank(),
                                       legend.direction = "vertical",
                                       legend.box = "vertical"),
                      ncol = 1, labels = "auto", label_size = 20, align = "v", axis = "b")


ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_meanFISimVsObsTest_MAD_VegTypeCN.tiff"),
       width = 8, height = 8)
gc(reset = TRUE)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```


## FIRE ATTRIBUTES BY PYRODIVERSITY LEVEL
Means as in HVs
```{r fireAttriPyro, echo = FALSE}
endYear <- max(yearSubset)
tempData <- allHVData[year == endYear,
                      .(HVtype, HV_noPM, HV_PM, rep, repHV, vegType)]
tempData <- melt.data.table(tempData, measure.vars = c("HV_noPM", "HV_PM"),
                            variable.name = "scenario", value.name = "Volume")
tempData$scenario <- sub("HV_", "", tempData$scenario)
tempData <- tempData[HVtype == "fireHV", list(Volume = mean(Volume, na.rm = TRUE)),
                     by = .(rep, vegType, scenario)]
setnames(tempData, "vegType", "vegTypeCN")

## add only landscape level HV sizes 
cols <- grep("mean", names(summaryFireAttributes), value = TRUE)
cols <- c(cols, "scenario", "rep", "pixelIndex", "vegTypeCN")
plotData <- tempData[vegTypeCN == "landscape", .(scenario, rep, Volume)][summaryFireAttributes[, ..cols], on = .(scenario, rep)]
plotData <- melt(plotData, id.vars = c("scenario", "rep", "Volume", "pixelIndex", "vegTypeCN"))
# plotData[variable %in% c("meanPatchS", "meanSevB"), value := log(value + 0.1)]

plot47 <- ggplot(plotData[!variable %in% c("meanSevB", "meanSev")], 
                 aes(x = cut(Volume, breaks = 200, include.lowest = TRUE), 
                     y = value, 
                     fill = scenario)) +
  geom_violin() +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", linewidth = 11/22, linetype = "dotted"),
        strip.placement = "outside", strip.background = element_blank(), strip.text = element_text(size = 16)) +
  labs(y = "", x = "pyrodiversity") +
  facet_grid(variable ~ scenario, scales = "free", switch = "y",
             labeller = labeller(scenario = scenLabels,
                                 variable = c("meanPatchS" = "Mean patch size\n(no. pixels)",
                                              "meanFreq" = "Mean fire interval\n",
                                              "meanSevPropB" = "Mean fire severity\n(% biomass lost)")))

## relationship between pyrodiversity and average fire attributes -----------------
## join HV sizes with fire attributes
plotData <- allHVData[HVtype == "fireHV",
                      .(HV_noPM, HV_PM, rep, repHV, vegType)]
plotData[, vegType := factor(vegType, levels = names(vegTypeCNLabels))]
plotData <- melt.data.table(plotData, measure.vars = c("HV_noPM", "HV_PM"),
                            variable.name = "scenario", value.name = "Volume")
plotData[, scenario := sub("HV_", "", scenario)]

## landscape only -- note that summaryFireAttributes doesn't have a "landscape" vegType
plotData2 <- plotData[vegType == "landscape"]
cols <- grep("mean", names(summaryFireAttributes), value = TRUE)
cols <- c(cols, "scenario", "rep", "pixelIndex", "vegTypeCN")
plotData2 <- summaryFireAttributes[, ..cols][plotData2, on = c("scenario", "rep"),
                                             allow.cartesian = TRUE]  
plotData2[, vegTypeCN := NULL]

## all but landscape
plotData <- plotData[vegType != "landscape"]
plotData <- summaryFireAttributes[, ..cols][plotData, on = c("vegTypeCN==vegType", "scenario", "rep"),
                                            allow.cartesian = TRUE]
setnames(plotData, "vegTypeCN", "vegType")
plotData <- rbind(plotData, plotData2)

cols <- grep("mean", names(plotData), value = TRUE)
plotData <- melt.data.table(plotData, measure.vars = cols,
                            variable.name = "fireAttr", value.name = "value")
## calculate summary stats on fire attributes
plotData <- plotData[, as.list(summary(value)), by = .(scenario, rep, repHV, Volume, vegType, fireAttr)]
plotData <- plotData[fireAttr %in% c("meanFreq", "meanSevPropB", "meanPatchS")]

## log for better visuals
plotData[, logVolume := log(Volume)]
plotData[, logMean := log(Mean)]

scenLabels2 <- as.character(scenLabels)
names(scenLabels2) <- names(scenLabels)

facetLabllr <- labeller(scenario =  as_labeller(scenLabels2, label_parsed),
                        fireAttr = c("meanPatchS" = "Mean patch size\n",
                                     "meanFreq" = "Mean fire interval",
                                     "meanSevPropB" = "Mean fire severity\n"))

fireAttrPyroLandscapePlot <- fireAttrPyroPlotFun(plotData[vegType == "landscape"],  
                                                 x = "Volume", y = "logMean",
                                                 colour = "vegType",
                                                 xFacet = "scenario", yFacet = "fireAttr",
                                                 # shapeLabels = scenLabels, 
                                                 # linetypeValues = scenLinetype,
                                                 # linetypeLabels = scenLabels, 
                                                 colValues = vegTypeCNColours, 
                                                 colLabels = vegTypeCNLabels,
                                                 xLab = "Pyrodiversity",
                                                 labllr = facetLabllr)
fireAttrPyroVegTypesPlot <- fireAttrPyroPlotFun(plotData[vegType != "landscape"],
                                                x = "Volume", y = "logMean",
                                                colour = "vegType",
                                                xFacet = "scenario", yFacet = "fireAttr",
                                                # shapeLabels = scenLabels, 
                                                # linetypeValues = scenLinetype,
                                                # linetypeLabels = scenLabels, 
                                                colValues = vegTypeCNColours, 
                                                colLabels = vegTypeCNLabels, 
                                                xLab = "Pyrodiversity",
                                                labllr = facetLabllr)

```

```{r plot&savePlots23, echo = FALSE}
plot47
ggsave(plot = plot47, filename = file.path(figOutputPath, "results_fireAttrLandscapePyrodiversity.tiff"),
       width = 14, height = 8)

plotSave <- ggarrange(fireAttrPyroVegTypesPlot,
                      fireAttrPyroLandscapePlot + labs(y = "", title = "") + theme(strip.text.y = element_blank()),
                      ncol = 2, nrow = 1, widths = c(1, 0.6), labels = "auto", label.y = 0.95,
                      common.legend = TRUE, legend = "bottom")
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fireAttrVsPyro.tiff"),
       width = 16, height = 10)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$|fireAttr.*Plot", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)
```

## SPECIES COMPOSITION BY VEGETATION TYPE
Only on the sampled years; only B and averg. weighted age
```{r plotsByVegTypeCN, cache = FALSE}
plotData <- allPixelCDMntEnd[, list(vegTypeCN = vegTypeCN,
                                    noFires = noFires,
                                    B = B,
                                    avgAgeBySppSim = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                  sum((B/100), na.rm = TRUE))),
                             by = .(scenario, rep, year, pixelIndex, speciesCode)]
plotData[is.nan(avgAgeBySppSim), avgAgeBySppSim := 0]
## sum B per spp, per stand
plotData[, B := sum(B), by = .(scenario, rep, year, pixelIndex, speciesCode)]
plotData <- unique(plotData)
## sum across pixels per vegType
plotData[, BiomassBySpecies := sum(B), 
         by = .(scenario, rep, year, vegTypeCN, speciesCode)]
# plotData$scenario <- as.character(scenLabels[match(plotData$scenario, names(scenLabels))])

## no. pixels with a veg type, per scenario/rep/year, then average for plot
plotData[noFires > 0, noPixels := length(pixelIndex), by = .(scenario, rep, year, vegTypeCN)]
plotData[noFires > 0, noPixels := round(mean(noPixels)), by = .(scenario, vegTypeCN)]

## SPECIES BIOMASS
## cross pixel sums
## just mean across reps and scaled from 0-1
scenLabels2 <- as.character(scenLabels)
names(scenLabels2) <- names(scenLabels)
plot7 <- sppCompositionPlots(data = plotData[noFires > 0],
                             x = "vegTypeCN", y = "BiomassBySpecies",
                             fill = "speciesCode", fillValues = speciesColours, 
                             fillLabels = speciesLabels, xFacet = "scenario", 
                             xlabels = vegTypeCNLabels,
                             labllr = as_labeller(scenLabels2, label_parsed),
                             titleLab = "Species biomass -- landscape level", yLab = "Relative biomass")
plot7 <- plot7 + 
  geom_text(data = unique(plotData[noFires > 0, .(scenario, vegTypeCN, noPixels)]),
            aes(x = vegTypeCN, y = 1.10, label = noPixels, fill = vegTypeCN))  ## fill is here to avoid an error

## with mean and SD
plot7.2 <- sppCompositionPlots(data = plotData[noFires > 0],
                               x = "vegTypeCN", y = "BiomassBySpecies",
                               fill = "speciesCode", fillValues = speciesColours, 
                               fillLabels = speciesLabels, xFacet = "scenario", 
                               xlabels = vegTypeCNLabels, 
                               labllr = as_labeller(scenLabels2, label_parsed),
                               errorBar = TRUE,
                               titleLab = "Species biomass -- landscape level", 
                               yLab = "Biomass (ton/ha)")

## pixel averages
## just mean across reps and scaled from 0-1
plot7.3 <- sppCompositionPlots(data = plotData[noFires > 0],
                               x = "vegTypeCN", y = "B",
                               fill = "speciesCode", fillValues = speciesColours, 
                               fillLabels = speciesLabels, xFacet = "scenario", 
                               xlabels = vegTypeCNLabels, 
                               labllr = as_labeller(scenLabels2, label_parsed),
                               titleLab = "Species biomass -- pixel level", yLab = "Relative biomass",
                               subtitleLab = "")

## with mean and SD
plot7.4 <- sppCompositionPlots(data = plotData[noFires > 0],
                               x = "vegTypeCN", y = "B", errorBar = TRUE,
                               fill = "speciesCode", fillValues = speciesColours, 
                               fillLabels = speciesLabels, xFacet = "scenario", 
                               xlabels = vegTypeCNLabels, 
                               labllr = as_labeller(scenLabels2, label_parsed),
                               titleLab = "Species biomass -- pixel level", yLab = "Biomass (ton/ha)",
                               subtitleLab = "")

## SPECIES BIOMASS-WEIGHTED AGE
## with mean and SD
plot8 <- sppCompositionPlots(data = plotData[noFires > 0],
                             x = "vegTypeCN", y = "avgAgeBySppSim", errorBar = TRUE,
                             fill = "speciesCode", fillValues = speciesColours, 
                             fillLabels = speciesLabels, xFacet = "scenario", 
                             xlabels = vegTypeCNLabels, labllr = as_labeller(scenLabels2, label_parsed),
                             titleLab = "Species age -- pixel level", 
                             yLab = "Biomass-weighted age",
                             subtitleLab = "")

```

```{r plot&savePlots4, echo = FALSE}
plot7
ggsave(plot = plot7, filename = file.path(figOutputPath, "results_landscapeB_vegTypeCN.tiff"),
       width = 14, height = 10)

plot7.2
ggsave(plot = plot7.2, filename = file.path(figOutputPath, "results_landscapeB_vegTypeCN_wSD.tiff"),
       width = 14, height = 10)

plot7.3
ggsave(plot = plot7.3, filename = file.path(figOutputPath, "results_pixelB_vegTypeCN.tiff"),
       width = 14, height = 10)

plot7.4
ggsave(plot = plot7.4, filename = file.path(figOutputPath, "results_pixelB_vegTypeCN_wSD.tiff"),
       width = 14, height = 10)

plot8
ggsave(plot = plot8, filename = file.path(figOutputPath, "results_pixelAge_vegTypeCN_wSD.tiff"),
       width = 14, height = 10)

plotsRm <- grep("plotData.*|plot1.*|plot2.*|plot3.*|plot4.*|plot7.*|plot8$", ls(), value = TRUE)
plotsRm <- grep("plot29$|plot29.1$|plot29.2$|plot29.3$|plotTest1.2$|plot39$", plotsRm,  invert = TRUE, value = TRUE)
rm(list = plotsRm)
gc(reset = TRUE)

```

