---
title: "LIM - analysis of results (full landscape)"
author: "Ceres Barros"
date: "26/04/2021"
output: html_document
---

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = "~/GitHub/LandscapesInMotion/")
knitr::opts_chunk$set(echo = FALSE, cache = 2, warning = FALSE,
                      fig.width = 10, fig.height = 8)

library(data.table)
library(ggplot2)
library(ggpubr)
library(ggspatial)
library(cowplot)
library(raster)
library(quickPlot)
library(SpaDES)
library(qs)
library(purrr)
library(magick)
library(LandR)
library(future)
library(future.apply)
library(lme4)
library(MuMIn)
library(ToolsCB)

source("R/R_tools/convertToCNVegType.R")
source("R/R_tools/Useful_functions.R")
options("reproducible.useNewDigestAlgorithm" = 2)
options("spades.moduleCodeChecks" = FALSE)
options("reproducible.useCache" = TRUE)
options("reproducible.destinationPath" = normPath("R/SpaDES/inputs"))
options("reproducible.useGDAL" = FALSE)


## general paths
simDirName <- "jun2021Runs"
simPaths <- list(cachePath = file.path("R/SpaDES/cache", simDirName)
                 , modulePath = file.path("R/SpaDES/m")
                 , inputPath = file.path("R/SpaDES/inputs")
                 , outputPath = file.path("R/SpaDES/outputs", simDirName))

## path to figure folder and cache folder
figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis")
dir.create(figOutputPath)
cPath <- file.path(simPaths$cachePath, "postSimAnalyses")
```

### DATA LOADING AND PROCESSING NOTES
```{r dataPrep, include = FALSE, cache = FALSE}
yearSubset <- c(seq(2011, 2111, 5), 2111)

source("R/SpaDES/6_resultsDataPrep.R")

startYear <- as.integer(start(preSimList))
endYear <- as.integer(end(preSimList))

## check
if (endYear != max(allPixelCohortData$year, na.rm = TRUE)) {
  stop("endYear and max(year) differ")
}
if (startYear != min(allPixelCohortData$year, na.rm = TRUE)) {
  stop("startYear and min(year) differ")
}
```

```{r summaryTables, cache=FALSE, include=FALSE}
## SUMMARY ACROSS LANDSCAPE -----------------------------------
## BY SPECIES
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataSpp <- allPixelCohortData[, list(BiomassBySpecies = as.numeric(sum((B/100), na.rm = TRUE)),
                                                      MortalityBySpecies = as.numeric(sum((mortality/100), na.rm = TRUE)),
                                                      aNPPBySpecies = as.numeric(sum((aNPPAct/100), na.rm = TRUE)),
                                                      AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                      sum((B/100), na.rm = TRUE))),
                                               by = .(scenario, rep, year, noFires, speciesCode)]
summaryBurnCohortDataSpp[is.nan(AgeBySppWeighted), AgeBySppWeighted := 0]
summaryBurnCohortDataSpp[, firePresAbs := as.integer(noFires != 0)]
amc::.gc()

## BY FOREST TYPE (def. as dominant species)
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataVegType <- allPixelCohortData[, list(BiomassByVegType = as.numeric(sum((B/100), na.rm = TRUE)),
                                                          MortalityByVegType = as.numeric(sum((mortality/100), na.rm = TRUE)),
                                                          aNPPByVegType = as.numeric(sum((aNPPAct/100), na.rm = TRUE)),
                                                          AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                          sum((B/100), na.rm = TRUE))),
                                                   by = .(scenario, rep, year, noFires, vegType)]
summaryBurnCohortDataVegType[is.nan(AgeBySppWeighted), AgeBySppWeighted := 0]
summaryBurnCohortDataVegType[, firePresAbs := as.integer(noFires != 0)]
amc::.gc()

## BY CAMERON'S VEG TYPE
summaryBurnCohortDataVegTypeCN <- allPixelCohortDataMnt[, list(BiomassByVegType = as.numeric(sum((B/100), na.rm = TRUE)),
                                                               MortalityByVegType = as.numeric(sum((mortality/100), na.rm = TRUE)),
                                                               aNPPByVegType = as.numeric(sum((aNPPAct/100), na.rm = TRUE)),
                                                               AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                               sum((B/100), na.rm = TRUE))),
                                                        by = .(scenario, rep, year, noFires, vegTypeCN)]
summaryBurnCohortDataVegTypeCN[is.nan(AgeBySppWeighted), AgeBySppWeighted := 0]
summaryBurnCohortDataVegTypeCN[, firePresAbs := as.integer(noFires != 0)]
amc::.gc()
```

```{r plotLabels, include = FALSE}
## make species labels/colours
speciesLabels <- LandR::equivalentName(value = unique(summaryBurnCohortDataSpp$speciesCode), column = "EN_generic_full",
                                       df = preSimList$sppEquiv)
names(speciesLabels) <- unique(summaryBurnCohortDataSpp$speciesCode)

speciesColours <- levels(preSimList$vegTypeMap)[[1]]$colors
names(speciesColours) <- levels(preSimList$vegTypeMap)[[1]]$VALUE

## make vegType labels/colours
vegTypeLabels <- as.character(levels(preSimList$vegTypeMap)[[1]]$VALUE)
vegTypeLabels <- LandR::equivalentName(value = vegTypeLabels, column = "EN_generic_full",
                                       df = preSimList$sppEquiv)
vegTypeLabels[length(vegTypeLabels) + 1] <- "No veg."
names(vegTypeLabels) <- c(levels(preSimList$vegTypeMap)[[1]]$ID, "0")

vegTypeColours <- as.character(levels(preSimList$vegTypeMap)[[1]]$colors)
vegTypeColours[length(vegTypeColours) + 1] <- "grey40"
names(vegTypeColours) <- c(levels(preSimList$vegTypeMap)[[1]]$ID, "0")

vegTypeCNLabels <- unique(as.character(summaryBurnCohortDataVegTypeCN$vegTypeCN))
names(vegTypeCNLabels) <- vegTypeCNLabels
vegTypeCNLabels <- sub("PIEN", "Spruce", vegTypeCNLabels)
vegTypeCNLabels <- sub("MMC", "Moist conif.", vegTypeCNLabels)
vegTypeCNLabels <- sub("mixedwood", "Mixed", vegTypeCNLabels)
vegTypeCNLabels <- sub("broadleaf", "Deciduous", vegTypeCNLabels)
vegTypeCNLabels <- sub("PICO", "Pine", vegTypeCNLabels)
vegTypeCNLabels <- sub("DMCPSME", "Dry conif./Douglas-fir", vegTypeCNLabels)
vegTypeCNLabels <- sub("^PSME$", "Douglas-fir", vegTypeCNLabels)
vegTypeCNLabels <- sub("dryPSME", "Dry Douglas-fir", vegTypeCNLabels)

vegTypeCNColours <- vegTypeCNLabels
vegTypeCNColours <- RColorBrewer::brewer.pal(length(vegTypeCNColours), name = "Set1")
names(vegTypeCNColours) <- names(vegTypeCNLabels)

## remove rasters to save memory
rm(list = grep("Stk", ls(), value = TRUE))
amc::.gc()
```


### SCENARIO EFFECTS ON STAND AGE, ALPHA DIVERSITY AND BETA DIVERSITY
Across the landscape in pixels with/without fire
```{r age_scenario}
## SCENARIO EFFECTS ON STAND AGE------
## scenario effects on stand age across landscape
plotData <- allPixelCohortData[year == endYear,
                               list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                    sum((B/100), na.rm = TRUE))),
                               by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]

plotData[, firePresAbs := as.factor(firePresAbs)]
plotData[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData <- plotData[!is.na(ecoregionGroup) & !is.na(AgeBySppWeighted)]

## some ecoregionGroups only have one observation, leading to signular fit
ageEffectsLMList <- lapply(split(plotData, by = "firePresAbs"), function(DT) {
  lmer(AgeBySppWeighted ~ scenario + (scenario | ecoregionGroup), data = DT)
})
print("No fire")
summary(ageEffectsLMList$`0`)

print("Fire")
summary(ageEffectsLMList$`1`)

## fitted values vector is shorter than nrow, prob. due to signularity. predict using the same data.
plotData[firePresAbs == 0, predVals := predict(ageEffectsLMList$`0`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 0])]
plotData[firePresAbs == 1, predVals := predict(ageEffectsLMList$`1`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 1])]

plotTest2 <- ggplot(plotData) +
  geom_boxplot(aes(x = firePresAbs, y = AgeBySppWeighted, fill = scenario)) +
  geom_point(aes(x = firePresAbs, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_color_manual(values = c("red", "red")) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  labs(y = "biomass-weighted age", x = "")
```

```{r alphaDiv_scenario}
## SCENARIO EFFECTS ON ALPHA DIVERSITY ------------------
## scenario effects on alpha-div across landscape
## inverse Simpson concentration (Whittaker 1972)
plotData <- allPixelCohortData[year == endYear]
plotData[, sumB := sum(B, na.rm = TRUE),
         by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, pixelIndex, speciesCode, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]

plotData[, firePresAbs := as.factor(firePresAbs)]
plotData[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData <- plotData[!is.na(ecoregionGroup) & !is.na(alphaDiv)]

## some ecoregionGroups only have one observation, leading to signular fit
alphaEffectsLMList <- lapply(split(plotData, by = "firePresAbs"), function(DT) {
  lmer(alphaDiv ~ scenario + (scenario | ecoregionGroup), data = DT)
})
summary(alphaEffectsLMList$`1`)

## fitted values vector is shorter than nrow, prob. due to signularity. predict using the same data.
plotData[firePresAbs == 0, predVals := predict(alphaEffectsLMList$`0`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 0])]
plotData[firePresAbs == 1, predVals := predict(alphaEffectsLMList$`1`, type = "response",
                                               re.form = NA,
                                               newdata = plotData[firePresAbs == 1])]

plotTest3 <- ggplot(plotData) +
  geom_boxplot(aes(x = firePresAbs, y = alphaDiv, fill = scenario)) +
  geom_point(aes(x = firePresAbs, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_color_manual(values = c("red", "red")) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  labs(y = "alpha-div.", x = "")
```

```{r betaDiv_scenario}
## SCENARIO EFFECTS ON BETA DIVERSITY ------------------
## scenario effects on beta-div across landscape - with fire vs. no fire
## from multiplicative decomposition where both alpha
## and gamma diversity are inverse Simpson concentration (Whittaker 1972)
# alpha-div
plotData <- allPixelCohortData[year == endYear]
plotData[, sumB := sum(B, na.rm = TRUE),
         by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, pixelIndex, speciesCode, firePresAbs, ecoregionGroup)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, pixelIndex, firePresAbs, ecoregionGroup)]

## gamma-div
plotData2 <- allPixelCohortData[year == endYear,
                                list(BiomassBySpecies = sum(B, na.rm = TRUE)),
                                by = .(scenario, rep, firePresAbs, speciesCode, ecoregionGroup)]
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, firePresAbs, ecoregionGroup)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, firePresAbs, speciesCode, ecoregionGroup)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, firePresAbs, ecoregionGroup)]

## beta-div
plotData2 <- plotData2[plotData, on = .(scenario, rep, firePresAbs, ecoregionGroup)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, firePresAbs, ecoregionGroup)]

plotData2[, firePresAbs := as.factor(firePresAbs)]
plotData2[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData2 <- unique(plotData2[!is.na(ecoregionGroup) & !is.na(betaDiv)])

## some ecoregionGroups only have one observation, leading to signular fit
betaEffectsLMList <- lapply(split(plotData2, by = "firePresAbs"), function(DT) {
  lmer(betaDiv ~ scenario + (1|ecoregionGroup), data = DT)
})
summary(betaEffectsLMList$`1`)

## fitted values vector is shorter than nrow, prob. due to signularity. predict using the same data.
plotData2[firePresAbs == 0, predVals := predict(betaEffectsLMList$`0`, type = "response",
                                                re.form = NA,
                                                newdata = plotData2[firePresAbs == 0])]
plotData2[firePresAbs == 1, predVals := predict(betaEffectsLMList$`1`, type = "response",
                                                re.form = NA,
                                                newdata = plotData2[firePresAbs == 1])]

plotTest4 <- ggplot(plotData2) +
  geom_boxplot(aes(x = firePresAbs, y = betaDiv, fill = scenario)) +
  geom_point(aes(x = firePresAbs, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_color_manual(values = c("red", "red")) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  labs(y = "beta-div.", x = "")

plotTest4
```

```{r betaDiv_scenario2}
## scenario effects on beta-div across landscape - regardless of fire presence
## from multiplicative decomposition where both alpha
## and gamma diversity are inverse Simpson concentration (Whittaker 1972)
# alpha-div
plotData <- allPixelCohortData[year == endYear]
plotData[, sumB := sum(B, na.rm = TRUE),
         by = .(scenario, rep, pixelIndex, ecoregionGroup)]
plotData <- plotData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                     by = .(scenario, rep, pixelIndex, speciesCode, ecoregionGroup)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, pixelIndex, ecoregionGroup)]

## gamma-div
plotData2 <- allPixelCohortData[year == endYear,
                                list(BiomassBySpecies = sum(B, na.rm = TRUE)),
                                by = .(scenario, rep, speciesCode, ecoregionGroup)]
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, ecoregionGroup)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, speciesCode, ecoregionGroup)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, ecoregionGroup)]

## beta-div
plotData2 <- plotData2[plotData, on = .(scenario, rep, ecoregionGroup)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, ecoregionGroup)]

plotData2[, ecoregionGroup := as.factor(ecoregionGroup)]
plotData2 <- unique(plotData2[!is.na(ecoregionGroup) & !is.na(betaDiv)])

## some ecoregionGroups only have one observation, leading to signular fit
betaEffectsLMList2 <- lmer(betaDiv ~ scenario + (1|ecoregionGroup), data = plotData2)
## no effect - pixels wihout fire dampen the response.
plotData2[, predVals := predict(betaEffectsLMList2, type = "response", re.form = NA)]

plotTest5 <- ggplot(plotData2) +
  geom_boxplot(aes(x = scenario, y = betaDiv, fill = scenario)) +
  geom_point(aes(x = scenario, y = predVals, colour = scenario),
             position = position_dodge(width = 0.75), size = 2, show.legend = FALSE) +
  geom_hline(yintercept = 0, colour = "grey", linetype = "dashed") +
  scale_color_manual(values = c("red", "red")) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  labs(y = "beta-div.", x = "")
```

```{r plot&savePlots14, echo = FALSE}
plotSave <- ggarrange(plotTest2 + theme(legend.position = "none"),
                      plotTest3 + theme(legend.position = "none"),
                      plotTest5 + theme(legend.position = "none"),
                      get_legend(plotTest2 + theme(legend.key.size = unit(1.5, "cm"))),
                      ncol = 2, nrow = 2,
                      labels = c("a", "b", "c", ""), font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageAlphaBetaDivEffectsTest.tiff"),
       width = 12, height = 7)
rm(plotTest2, plotTest3, plotTest5)
gc()
```


```{r modelSave, include = FALSE}
## save models:
saveRDS(ageDiffLMList, file = file.path(simPaths$outputPath, "ageDiffModel.rds"))
saveRDS(ageEffectsLMList, file = file.path(simPaths$outputPath, "ageEffectsModel.rds"))
saveRDS(alphaEffectsLMList, file = file.path(simPaths$outputPath, "alphaEffectsModel.rds"))
saveRDS(betaEffectsLMList, file = file.path(simPaths$outputPath, "betaEffectsModel.rds"))
saveRDS(betaEffectsLMList2, file = file.path(simPaths$outputPath, "betaEffectsModel2.rds"))
```

### BIOMASS, MORTALITY, AVG. AGE AND NO COHORTS BY SPECIES
```{r plotsBySpecies, cache = FALSE}
## PLOTS -----------------------------------------------
## MODELLED PROPERTIES ---------------------------------
## BY SPECIES ------------
## total biomass
plotData <- summaryBurnCohortDataSpp[, list(BiomassBySpecies = sum(BiomassBySpecies)),
                                     by = .(scenario, year, rep, speciesCode, firePresAbs)]
plot1 <- ggplot(data = plotData,
                aes(x = year, y = log(BiomassBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape biomass", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot2 <- ggplot(data = summaryBurnCohortDataSpp,
                aes(x = year, y = log(BiomassBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape biomass", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires)

## total mortality
plotData <- summaryBurnCohortDataSpp[, list(MortalityBySpecies = sum(MortalityBySpecies)),
                                     by = .(scenario, year, rep, speciesCode, firePresAbs)]
plot3 <- ggplot(data = plotData,
                aes(x = year, y = log(MortalityBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape mortality", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot4 <- ggplot(data = summaryBurnCohortDataSpp,
                aes(x = year, y = log(MortalityBySpecies + 0.000001), colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Total landscape mortality", y = "log-biomass (ton/ha)",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires)
amc::.gc()

## average age
plotData <- allPixelCohortData[, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                      sum((B/100), na.rm = TRUE))),
                               by = .(scenario, year, rep, firePresAbs, speciesCode)]
plot5 <- ggplot(data = plotData,
                aes(x = year, y = AgeBySppWeighted, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by species") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot6 <- ggplot(data = summaryBurnCohortDataSpp,
                aes(x = year, y = AgeBySppWeighted, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires)

## no. cohorts
plotData <- allPixelCohortData[B > 0, list(noCohorts = length(unique(age))),
                               by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, speciesCode)]
plot7 <- ggplot(data = plotData,
                aes(x = year, y = noCohorts, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts",
       subtitle = "by species") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot8 <- ggplot(data = plotData,
                aes(x = year, y = noCohorts, colour = speciesCode)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = speciesColours, labels = speciesLabels) +
  labs(title = "Avg. no. cohorts", y = "no. cohorts",
       subtitle = "by species") +
  facet_grid(scenario ~ noFires)

amc::.gc()
```

```{r plot&savePlots, echo = FALSE}
## biomass
plotSave <- ggarrange(plot1,
                      plot2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeB.tiff"),
       width = 14, height = 7)

## age
plotSave <- ggarrange(plot5,
                      plot6 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAge.tiff"),
       width = 14, height = 7)

## no. cohorts:
plotSave <- ggarrange(plot7 + theme(plot.subtitle = element_blank()),
                      plot8 +
                        theme(plot.subtitle = element_blank(),
                              axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_noCohorts.tiff"),
       width = 14, height = 7)
rm(plot1, plot2, plot5, plot6, plot7, plot8)
gc()
```

#### Variability across repetitions
```{r varRepsBySpecies, cache = FALSE}
## VARIABILITY ACROSS REPS -----------------------------
## BY SPECIES ---------------------
## total biomass across landscape
plotData <- summaryBurnCohortDataSpp[year == endYear, list(BiomassBySpecies = sum(BiomassBySpecies)),
                                     by = .(scenario, year, rep, speciesCode, firePresAbs)]
plot1var <- ggplot(data = plotData,
                   aes(x = speciesCode, y = log(BiomassBySpecies + 0.000001),
                       fill = speciesCode)) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = speciesColours, labels = speciesLabels) +
  scale_x_discrete(labels = speciesLabels) +
  labs(title = "Total biomass (year 100)", y = "log-biomass (ton/ha)",
       x = "", subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## average stand biomass
plotData <- allPixelCohortData[year == endYear, list(B = sum(B/100, na.rm = TRUE)),   ## copllapse cohorts first
                               by = .(scenario, rep, firePresAbs, pixelIndex, speciesCode)]
plotData <- plotData[, list(avgBspp = mean(B, na.rm = TRUE)),    ## now average across landscape
                     by = .(scenario, rep, firePresAbs, speciesCode)]
plot2var <- ggplot(data = plotData,
                   aes(x = speciesCode, y = avgBspp, fill = speciesCode)) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = speciesColours, labels = speciesLabels) +
  scale_x_discrete(labels = speciesLabels) +
  labs(title = "Avg. stand biomass (year 100)", y = "biomass (ton/ha)",
       x = "" , subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## average age across landscape
plotData <- allPixelCohortData[year == endYear, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                     sum((B/100), na.rm = TRUE))),
                               by = .(scenario, year, rep, firePresAbs, speciesCode)]
plot3var <- ggplot(data = plotData,
                   aes(x = speciesCode, y = AgeBySppWeighted, fill = speciesCode)) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = speciesColours, labels = speciesLabels) +
  scale_x_discrete(labels = speciesLabels) +
  labs(title = "Avg. age (year 100)", y = "biomass-weighted age",
       x = "" , subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## average stand age
plotData <- allPixelCohortData[year == endYear,
                               list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                    sum((B/100), na.rm = TRUE))),   ## calculate per stand first
                               by = .(scenario, rep, firePresAbs, pixelIndex, speciesCode)]
plotData <- plotData[, list(AgeBySppWeighted = mean(AgeBySppWeighted, na.rm = TRUE)),    ## now average across landscape
                     by = .(scenario, rep, firePresAbs, speciesCode)]
plot4var <- ggplot(data = plotData,
                   aes(x = speciesCode, y = AgeBySppWeighted, fill = speciesCode)) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = speciesColours, labels = speciesLabels) +
  scale_x_discrete(labels = speciesLabels) +
  labs(title = "Avg. stand age (year 100)", y = "biomass-weighted age",
       x = "" , subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## avg no. cohorts in stand
plotData <- allPixelCohortData[year == endYear & B > 0,
                               list(noCohorts = length(unique(age))),   ## calculate per stand first
                               by = .(scenario, rep, firePresAbs, pixelIndex, speciesCode)]
plotData <- plotData[, list(avgNoCohorts = mean(noCohorts, na.rm = TRUE)),    ## now average across landscape
                     by = .(scenario, rep, firePresAbs, speciesCode)]
plot5var <- ggplot(data = plotData,
                   aes(x = speciesCode, y = avgNoCohorts, fill = speciesCode)) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = speciesColours, labels = speciesLabels) +
  scale_x_discrete(labels = speciesLabels) +
  labs(title = "Avg. no. cohorts in a stand (year 100)", y = "no. cohorts",
       x = "" , subtitle = "by species") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))
```

```{r plot&savePlots9, echo = FALSE, echo = FALSE}
plotSave <- ggarrange(plot1var +
                        theme(axis.title.x = element_blank(), axis.text.x = element_blank(),
                              plot.margin = margin(0,0,0,0)),
                      plot3var +
                        theme(axis.title.x = element_blank(), axis.text.x = element_blank(),
                              plot.title = element_blank(), plot.margin = margin(0,0,0,0)) +
                        labs(title = "", subtitle = ""),
                      plot5var + theme(plot.title = element_blank(),
                                       plot.margin = margin(0,0,0,5, unit = "mm")) +
                        labs(title = "", subtitle = ""), ncol = 1,
                      heights = c(1, 0.9, 1.3),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeBAgeCohortsVar.tiff"),
       width = 7, height = 12)

rm(plot1var, plot3var, plot5var)
gc()
```

### BIOMASS, MORTALITY, AVG. AGE AND NO COHORTS BY VEG TYPE (dom species)
```{r plotsByDomSpecies, cache = FALSE}
## BY FOREST TYPE (DOMINANT SPECIES) ------------
## no. pixels
plotData <- allPixelCohortData[, list(noPixelsVeg = length(unique(pixelIndex))),
                               by = .(scenario, year, rep, firePresAbs, vegType)]
## add 0s to missing veg types in a year
plotData <- plotData %>%
  tidyr::pivot_wider(names_from = vegType, values_from = noPixelsVeg,
                     values_fill = list(noPixelsVeg = 0)) %>%
  as.data.table(.) %>%
  melt(., id.vars = c("scenario", "year", "rep", "firePresAbs"),
       variable.name = "vegType", value.name = "noPixelsVeg")

plot9 <- ggplot(data = plotData,
                aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "stack") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Abundance of cover type", y = "no. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot9.2 <- ggplot(data = plotData,
                  aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "fill") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Cover type abundance", y = "prop. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))
amc::.gc()

plotData <- allPixelCohortData[, list(noPixelsVeg = length(unique(pixelIndex))),
                               by = .(scenario, year, rep, noFires, vegType)]
## add 0s to missing veg types in a year
plotData <- plotData %>%
  tidyr::pivot_wider(names_from = vegType, values_from = noPixelsVeg,
                     values_fill = list(noPixelsVeg = 0)) %>%
  as.data.table(.) %>%
  melt(., id.vars = c("scenario", "year", "rep", "noFires"),
       variable.name = "vegType", value.name = "noPixelsVeg")

plot10 <- ggplot(data = plotData,
                 aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "stack") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Cover type abundance", y = "no. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ noFires)

plot10.2 <- ggplot(data = plotData,
                   aes(x = year, y = noPixelsVeg, fill = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "area", position = "fill") +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Cover type abundance", y = "prop. pixels",
       subtitle = "(dominant species cover type)") +
  facet_grid(scenario ~ noFires)

## no. cohorts
plotData <- allPixelCohortData[B > 0, list(noCohorts = length(unique(age))),
                               by = .(scenario, year, rep, pixelIndex, firePresAbs, noFires, vegType)]
plot11 <- ggplot(data = plotData,
                 aes(x = year, y = noCohorts, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. no. cohorts in a stand", y = "no. cohorts",
       subtitle = "by dom. species cover type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot12 <- ggplot(data = plotData,
                 aes(x = year, y = noCohorts, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. no. cohorts in a stand", y = "no. cohorts",
       subtitle = "by dom. species cover type") +
  facet_grid(scenario ~ noFires)

## total biomass
plotData <- summaryBurnCohortDataVegType[, list(BiomassByVegType = sum(BiomassByVegType)),
                                         by = .(scenario, year, rep, vegType, firePresAbs)]
plot13 <- ggplot(data = plotData,
                 aes(x = year, y = log(BiomassByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot14 <- ggplot(data = summaryBurnCohortDataVegType,
                 aes(x = year, y = log(BiomassByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total biomass", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires)

## total mortality
plotData <- summaryBurnCohortDataVegType[, list(MortalityByVegType = sum(MortalityByVegType)),
                                         by = .(scenario, year, rep, vegType, firePresAbs)]
plot15 <- ggplot(data = plotData,
                 aes(x = year, y = log(MortalityByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total mortality", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot16 <- ggplot(data = summaryBurnCohortDataVegType,
                 aes(x = year, y = log(MortalityByVegType + 0.000001), colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Total mortality", y = "log-biomass (ton/ha)",
       subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires)

## average age
plotData <- allPixelCohortData[, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                      sum((B/100), na.rm = TRUE))),
                               by = .(scenario, year, rep, firePresAbs, vegType)]

plot17 <- ggplot(data = plotData,
                 aes(x = year, y = AgeBySppWeighted, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by dominant species cover type") +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

plot18 <- ggplot(data = summaryBurnCohortDataVegType,
                 aes(x = year, y = AgeBySppWeighted, colour = as.factor(vegType))) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_colour_manual(values = vegTypeColours, labels = vegTypeLabels) +
  labs(title = "Avg. age", y = "biomass-weighted age",
       subtitle = "by dominant species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ noFires)
amc::.gc()
```

```{r plot&savePlots2, echo = FALSE}
## biomass
plotSave <- ggarrange(plot13 + theme(plot.title = element_text(size = 17)),
                      plot14 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeBVegType.tiff"),
       width = 14, height = 7)

## age
plotSave <- ggarrange(plot17,
                      plot18 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAgeVegType.tiff"),
       width = 14, height = 7)

## veg type abundance 
plotSave <- ggarrange(plot9.2,
                      plot10.2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = ""),
                      widths = c(0.4, 0.7), labels = "auto", font.label = list(size = 20),
                      legend = "bottom", common.legend = TRUE)
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeVegTypes.tiff"),
       width = 14, height = 7)

## no. cohorts
plotSave <- ggarrange(plot11,
                      plot12 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_noCohortsVegType.tiff"),
       width = 14, height = 7)

rm(plot13, plot14, plot17, plot18, plot9.2, plot10.2, plot11, plot12)
gc()
```

#### Variability across repetitions
```{r varRepsByDomSpecies, cache = FALSE}
## (DOMINANT SPECIES) ------------
## total biomass across landscape
plotData <- summaryBurnCohortDataVegType[year == endYear, list(BiomassBySpecies = sum(BiomassByVegType)),
                                         by = .(scenario, rep, vegType, firePresAbs)]
plot6var <- ggplot(data = plotData,
                   aes(x = as.factor(vegType), y = log(BiomassBySpecies + 0.000001),
                       fill = as.factor(vegType))) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  scale_x_discrete(labels = vegTypeLabels) +
  labs(title = "Total biomass (year 100)", y = "log-biomass (ton/ha)",
       x = "" , subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## average stand biomass
plotData <- allPixelCohortData[year == endYear, list(B = sum(B/100, na.rm = TRUE)),   ## copllapse cohorts first
                               by = .(scenario, rep, firePresAbs, pixelIndex, vegType)]
plotData <- plotData[, list(avgBvegType = mean(B, na.rm = TRUE)),    ## now average across landscape
                     by = .(scenario, rep, firePresAbs, vegType)]
plot7var <- ggplot(data = plotData,
                   aes(x = as.factor(vegType), y = avgBvegType, fill = as.factor(vegType))) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  scale_x_discrete(labels = vegTypeLabels) +
  labs(title = "Avg. stand biomass (year 100)", y = "biomass (ton/ha)",
       x = "" , subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## average age across landscape
plotData <- allPixelCohortData[year == endYear, list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                                     sum((B/100), na.rm = TRUE))),
                               by = .(scenario, year, rep, firePresAbs, vegType)]
plot8var <- ggplot(data = plotData,
                   aes(x = as.factor(vegType), y = AgeBySppWeighted, fill = as.factor(vegType))) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  scale_x_discrete(labels = vegTypeLabels) +
  labs(title = "Avg. age (year 100)", y = "biomass-weighted age",
       x = "" , subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## average stand age
plotData <- allPixelCohortData[year == endYear,
                               list(AgeBySppWeighted = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                    sum((B/100), na.rm = TRUE))),   ## calculate per stand first
                               by = .(scenario, rep, firePresAbs, pixelIndex, vegType)]
plotData <- plotData[, list(AgeBySppWeighted = mean(AgeBySppWeighted, na.rm = TRUE)),    ## now average across landscape
                     by = .(scenario, rep, firePresAbs, vegType)]
plot9var <- ggplot(data = plotData,
                   aes(x = as.factor(vegType), y = AgeBySppWeighted, fill = as.factor(vegType))) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  scale_x_discrete(labels = vegTypeLabels) +
  labs(title = "Avg. stand age (year 100)", y = "biomass-weighted age",
       x = "" , subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## avg no. cohorts in stand
plotData <- allPixelCohortData[year == endYear & B > 0,
                               list(noCohorts = length(unique(age))),   ## calculate per stand first
                               by = .(scenario, rep, firePresAbs, pixelIndex, vegType)]
plotData <- plotData[, list(avgNoCohorts = mean(noCohorts, na.rm = TRUE)),    ## now average across landscape
                     by = .(scenario, rep, firePresAbs, vegType)]
plot10var <- ggplot(data = plotData,
                    aes(x = as.factor(vegType), y = avgNoCohorts, fill = as.factor(vegType))) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  scale_x_discrete(labels = vegTypeLabels, drop = FALSE) +
  labs(title = "Avg. no. cohorts in a stand (year 100)", y = "no. cohorts",
       x = "" , subtitle = "by dom. species cover type") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## no. pixels
plotData <- allPixelCohortData[year == endYear, list(noPixelsVeg = length(unique(pixelIndex))),
                               by = .(scenario, year, rep, firePresAbs, vegType)]
## add 0s to missing veg types in a year
plotData <- plotData %>%
  tidyr::pivot_wider(names_from = vegType, values_from = noPixelsVeg,
                     values_fill = list(noPixelsVeg = 0)) %>%
  as.data.table(.) %>%
  melt(., id.vars = c("scenario", "year", "rep", "firePresAbs"),
       variable.name = "vegType", value.name = "noPixelsVeg")

plot11var <- ggplot(data = plotData,
                    aes(x = as.factor(vegType), y = noPixelsVeg, fill = as.factor(vegType))) +
  geom_boxplot(show.legend = FALSE) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels) +
  scale_x_discrete(labels = vegTypeLabels) +
  labs(title = "Abundance of cover type (year 100)", y = "no. pixels",
       x = "" , subtitle = "(dominant species cover type)") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))
```

```{r plot&savePlots10, echo = FALSE}
plotSave <- ggarrange(plot6var + theme(plot.subtitle = element_blank(),
                                       axis.title.x = element_blank(), axis.text.x = element_blank()),
                      plot8var +
                        theme(plot.margin = margin(l = 10, unit = "mm"), plot.subtitle = element_blank(),
                              axis.title.x = element_blank(), axis.text.x = element_blank()),
                      plot10var +
                        theme(plot.margin = margin(l = 9, unit = "mm"), plot.subtitle = element_blank()),
                      plot11var + theme(plot.subtitle = element_blank()),
                      ncol = 2, nrow = 2,
                      heights = c(1, 1.6),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeBAgeCohortsVarVegType.tiff"),
       width = 14, height = 9)

rm(plot6var, plot8var, plot10var, plot11var)
gc()
```


### ALPHA AND BETA DIVERSITY PLOTS
```{r alphaDiv, cache = FALSE}
## BIODIVERSITY METRICS --------------------------------
## ALPHA DIVERSITY --------------
## inverse Simpson concentration (Whittaker 1972)
rm(plotData, plotData2)
amc::.gc()
allPixelCohortData[, sumB := sum(B, na.rm = TRUE),
                   by = .(scenario, rep, year, pixelIndex, firePresAbs, noFires)]
plotData <- allPixelCohortData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                               by = .(scenario, rep, year, pixelIndex, speciesCode, firePresAbs, noFires)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, year, pixelIndex, firePresAbs, noFires)]

plot33 <- ggplot(data = plotData,
                 aes(x = year, y = alphaDiv, colour = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  labs(title = "Avg. alpha-diversity", y = "alpha-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## map of alpha - avg across reps
plotData2 <- plotData[year == endYear, list(alphaDiv = mean(alphaDiv)),
                      by = .(scenario, pixelIndex)]
alphaStk <- lapply(split(plotData2, by = "scenario"), function(DT, RTM) {
  rasAlpha <- RTM
  rasAlpha[] <- NA
  rasAlpha[DT$pixelIndex] <- DT$alphaDiv
  rasAlpha
}, RTM = preSimList$rasterToMatch)
alphaStk <- stack(alphaStk)

rasData <- data.table(vals = getValues(alphaStk), coordinates(alphaStk))
rasData <- rasData[!is.na(vals.noPM)]
rasData[, delta := vals.noPM - vals.PM]
rasData <- melt(rasData, id.vars = c("x", "y", "delta"))
rasData$variable <- sub("vals.", "", rasData$variable)

plotMap1 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "transparent") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = value)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  scale_fill_distiller(palette = "YlGnBu", direction = 1,
                       breaks = c(0:length(unique(allPixelCohortData$speciesCode))),
                       labels = c(0:length(unique(allPixelCohortData$speciesCode))),
                       limits = c(0, length(unique(allPixelCohortData$speciesCode))),
                       na.value = "transparent") +
  labs(x = "longitude", y = "latitude", fill = "alpha-div.") +
  facet_wrap(~ variable)

plotMap1hist <- ggplot(rasData[!is.na(value)]) +
  geom_density(aes(x = value, fill = variable, alpha = variable)) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1)) +
  labs(y = "density", x = "alpha-div.")

## delta plot
plotMap1.2 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "grey85") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = delta)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  scale_fill_distiller(palette = "RdBu", direction = 1,
                       na.value = "transparent") +
  labs(x = "longitude", y = "latitude", fill = expression(paste(Delta, "alpha-div.")))
```

```{r betaDiv, cache = FALSE}
## BETA DIVERSITY --------------
## from multiplicative decomposition where both alpha
## and gamma diversity are inverse Simpson concentration (Whittaker 1972)
## alpha-div
plotData <- allPixelCohortData[, list(relB = sum(B, na.rm = TRUE)/sumB),
                               by = .(scenario, rep, year, pixelIndex, speciesCode, firePresAbs, noFires)]
plotData <- plotData[, list(alphaDiv = 1/sum(relB^2)),
                     by = .(scenario, rep, year, pixelIndex, firePresAbs, noFires)]

## gamma-div - firePresAbs
plotData2 <- copy(summaryBurnCohortDataSpp)
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, year, firePresAbs)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, year, firePresAbs, speciesCode)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, year, firePresAbs)]

## beta-div  - firePresAbs
plotData2 <- plotData2[plotData, on = .(scenario, rep, year, firePresAbs)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, year, firePresAbs)]

plot35 <- ggplot(data = plotData2,
                 aes(x = year, y = betaDiv, colour = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  labs(title = "Avg. beta-diversity", y = "beta-div.") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(~ firePresAbs,
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## gamma-div - no fires
plotData2 <- copy(summaryBurnCohortDataSpp)
plotData2[, sumB := sum(BiomassBySpecies, na.rm = TRUE),
          .(scenario, rep, year, noFires)]
plotData2 <- plotData2[, list(relB = sum(BiomassBySpecies, na.rm = TRUE)/sumB),
                       by = .(scenario, rep, year, noFires, speciesCode)]
plotData2 <- plotData2[, list(gammaDiv = 1/sum(relB^2)),
                       by = .(scenario, rep, year, noFires)]
## beta-div
plotData2 <- plotData2[plotData, on = .(scenario, rep, year, noFires)]
plotData2 <- plotData2[, list(betaDiv = gammaDiv * sum((1/.N) * (1/alphaDiv), na.rm = TRUE)),
                       by = .(scenario, rep, year, noFires)]

plot36 <- ggplot(data = plotData2,
                 aes(x = year, y = betaDiv, colour = scenario)) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
  labs(title = "Avg. beta-diversity", y = "beta-div.")  +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(~ noFires)
```

```{r plot&savePlots8, echo = FALSE}
plotSave <- ggarrange(plot33,
                      plot35, common.legend = TRUE, legend = "top",
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAlphaBetaScenario.tiff"),
       width = 14, height = 6)

rm(plot33, plot35)
gc()
```

## MAPS - veg type (dominant species)
```{r mapPlots, cache = FALSE}
## MAPS ------------------------
## dominant species - to deal with reps we need to reclassify the stands after averaging across reps.
plotData <- allPixelCohortData[year %in% c(startYear, endYear), 
                               list(B = mean(B, na.rm = TRUE),
                                    age =  as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                        sum((B/100), na.rm = TRUE))),
                               by = .(year, scenario, pixelIndex, speciesCode, firePresAbs)]

plotData <- lapply(split(plotData[B > 0], by = c("scenario", "year")), vegTypeGenerator,
                   vegLeadingProportion = 0, sppEquiv = preSimList$sppEquiv,
                   sppEquivCol = P(preSimList)$Biomass_borealDataPrep$sppEquivCol,
                   pixelGroupColName = "pixelIndex", doAssertion = FALSE)  ## turn assertions off so that the algorythm choice is based on table size
plotData <- rbindlist(plotData, use.names = TRUE)
setnames(plotData, "leading", "vegType")

plotData[, vegType := as.numeric(factor(vegType))]

vegTypeStk <- lapply(split(plotData, by =  c("scenario", "year")), function(DT, RTM) {
  rasVeg <- RTM
  rasVeg[] <- NA
  rasVeg[DT$pixelIndex] <- DT$vegType
  rasVeg
}, RTM = preSimList$rasterToMatch)
vegTypeStk <- stack(vegTypeStk)

myCompareRaster <- function(x, y) compareRaster(x, y, values = TRUE)
areEqual <- Reduce(myCompareRaster, as.list(vegTypeStk[[grep(startYear, names(vegTypeStk), value = TRUE)]]))
if (areEqual) {
  layers2Keep <- c(grep(startYear, names(vegTypeStk), value = TRUE)[1], 
                   grep(startYear, names(vegTypeStk), invert = TRUE, value = TRUE))
  vegTypeStk <- vegTypeStk[[layers2Keep]]
  names(vegTypeStk) <- sub(".*2011", "startYear", names(vegTypeStk))
} else {
  stop("initial veg type raster not identical across scenarios")
}

ageStk <- lapply(split(plotData[year == endYear], by = "scenario"), function(DT, RTM) {
  rasVeg <- RTM
  rasVeg[] <- NA
  rasVeg[DT$pixelIndex] <- DT$age
  rasVeg
}, RTM = preSimList$rasterToMatch)
ageStk <- stack(ageStk)

## vegetation type
rasData <- data.table(vals = getValues(vegTypeStk), coordinates(vegTypeStk))
rasData <- melt(rasData, id.vars = c("x", "y"))
rasData$variable <- sub("vals.", "", rasData$variable)
rasData[variable == "startYear", variable := startYear]

rm(vegTypeStk)
amc::.gc()

plotMap2 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "transparent") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = as.factor(value))) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank()) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels,
                    na.translate = FALSE) +
  labs(x = "longitude", y = "latitude") +
  facet_wrap(~ variable)

rasData2 <- rasData2 <- rasData[variable != startYear & !is.na(value)]
rasData2$variable <- sub(paste0(".", endYear), "", rasData2$variable, fixed = TRUE)
plotMap2hist <- ggplot(rasData2) +
  geom_bar(aes(x = as.factor(value), fill = as.factor(value),
               alpha = variable == "PM"), position = "dodge") +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank(),
        axis.title.x = element_blank()) +
  scale_fill_manual(values = vegTypeColours, labels = vegTypeLabels,
                    na.translate = FALSE) +
  scale_alpha_manual(labels = c("TRUE" = "PM", "FALSE" = "noPM"),
                     values = c("TRUE" = 1, "FALSE" = 0.6)) +
  scale_x_discrete(labels = vegTypeLabels) +
  guides(alpha = guide_legend(nrow = 2)) +
  labs(y = "no. pixels")

## age
rasData <- data.table(vals = getValues(ageStk), coordinates(ageStk))
rasData <- rasData[!is.na(vals.noPM)]
rasData[, delta := vals.noPM - vals.PM]
rasData <- melt(rasData, id.vars = c("x", "y", "delta"))
rasData$variable <- sub("vals.", "", rasData$variable)

rm(ageStk)
amc::.gc()

plotMap3 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "transparent") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = value)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0)) +
  scale_fill_distiller(palette = "Greens", na.value = "transparent",
                       direction = 1) +
  labs(x = "longitude", y = "latitude", fill = "age") +
  facet_wrap(~ variable)

plotMap3hist <- ggplot(rasData[!is.na(value)]) +
  geom_density(aes(x = value, fill = variable, alpha = variable)) +
  theme_pubr(base_size = 16) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0), legend.title = element_blank()) +
  scale_alpha_manual(values = c("PM" = 0.6, "noPM" = 1), guide = "none") +
  labs(y = "density", x = "age (years)")

## delta plot
plotMap3.2 <- ggplot() +
  layer_spatial(data = preSimList$studyArea, col = "black",
                fill = "grey85") +
  geom_raster(data = rasData,
              mapping = aes(x, y, fill = delta)) +
  annotation_north_arrow(style = north_arrow_minimal,
                         height = unit(1, "cm"), width = unit(1, "cm"),
                         location = "tr", which_north = "true") +
  theme_pubr(base_size = 16) +
  scale_fill_distiller(palette = "RdBu", direction = 1,
                       na.value = "transparent") +
  labs(x = "longitude", y = "latitude", fill = expression(paste(Delta, "age")))

rm(rasData)
amc::.gc()
```

```{r plot&savePlots11, echo = FALSE}
plotSave <- ggarrange(plotMap1 + theme(legend.position = "right"),
                      plotMap1hist +
                        theme(legend.position = c(0.7, 0.95), legend.justification = c("left", "top")),
                      ncol = 1, heights = c(2,1), widths = c(0.98, 1))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_avgAlphaDivMap.tiff"),
       width = 8, height = 12)

plotSave <- ggarrange(plotMap2 + theme(legend.position = "none"),
                      plotMap3 + theme(legend.position = "right"),
                      plotMap2hist + theme(axis.text.x = element_blank(), legend.position = "none") +
                        guides(fill = guide_legend(nrow = 2), alpha = guide_legend(nrow = 2)),
                      plotMap3hist + theme(legend.position = c(0.95, 0.95),
                                           legend.justification = c("right", "top")),
                      get_legend(plotMap2hist),
                      ncol = 2, nrow = 3, heights = c(1,0.3,0.1),
                      font.label = list(size = 24), labels = c("a", "b"),
                      widths = c(1, 0.9), align = "hv")

plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_avgVegTypeAgeMap.tiff"),
       width = 18, height = 12)

plotSave <- ggarrange(plotMap1.2 + theme(legend.position = "bottom") +
                        guides(fill = guide_colorbar(title.position = "top", barwidth = 10)),
                      plotMap3.2 + theme(legend.position = "bottom",
                                         axis.text.y = element_blank(), axis.title.y = element_blank()) +
                        guides(fill = guide_colorbar(title.position = "top", barwidth = 10)),
                      ncol = 2, nrow = 1,
                      labels = c("a", "b", ""), font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_deltaAvgAgeAlphaMap.tiff"),
       width = 8, height = 8)

rm(plotMap1, plotMap1hist, plotMap1.2, plotMap2, plotMap2hist, plotMap3, plotMap3hist, plotMap3.2)
gc()
```
