---
title: "LIM - analysis of results (montane -- new: sims with 2000yrs)"
subtitle: "Only publication results are included" 
author: "Ceres Barros"
date: "26/04/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(getwd()))
knitr::opts_chunk$set(echo = FALSE, cache = 2, warning = FALSE,
                      fig.width = 10, fig.height = 8)
```

```{r setup2, include=FALSE}
if (!exists("pkgDir")) {
  pkgDir <- file.path(
    if (Sys.info()[["user"]] == "rstudio") "packages_docker" else "packages",
    version$platform,
    paste0(version$major, ".", strsplit(version$minor, "[.]")[[1]][1])
  )
  
  if (!dir.exists(pkgDir)) {
    dir.create(pkgDir, recursive = TRUE)
  }
  .libPaths(pkgDir)
}

library(data.table)
library(ggplot2)
library(ggpubr)
library(ggspatial)
library(cowplot)
library(raster)
library(stars)
library(sf)
library(quickPlot)
library(SpaDES)
library(qs)
library(purrr)
library(magick)
library(LandR)
library(future)
library(future.apply)
library(lme4)
library(MuMIn)
library(ToolsCB)

source("R/R_tools/convertToCNVegType.R")
source("R/R_tools/hypervolumesHelpers.R")
source("R/R_tools/Useful_functions.R")
source("R/R_tools/utilsForResultsAnalyses.R")
options("reproducible.useNewDigestAlgorithm" = 2)
options("spades.moduleCodeChecks" = FALSE)
options("reproducible.useCache" = TRUE)
options("reproducible.destinationPath" = normPath("R/SpaDES/inputs"))
options("reproducible.useGDAL" = FALSE)


## general paths
simDirName <- "mar2022Runs"
if (Sys.info()["nodename"] == "W-VIC-A127584") {
  simPaths <- list(cachePath = file.path("F:", basename(getwd()), "R/SpaDES/cache", simDirName, "postSimAnalyses")
                   , modulePath = normPath(file.path("R/SpaDES/m"))
                   , inputPath = normPath(file.path("R/SpaDES/inputs"))
                   , outputPath = file.path("F:", basename(getwd()), "R/SpaDES/outputs", simDirName))
} else if (grepl("for-cast", Sys.info()["nodename"])) {
  simPaths <- list(cachePath = file.path("R/SpaDES/cache", simDirName, "postSimAnalyses")
                   , modulePath = normPath(file.path("R/SpaDES/m"))
                   , inputPath = normPath(file.path("R/SpaDES/inputs"))
                   , outputPath = normPath(file.path("R/SpaDES/outputs", simDirName))
                   , rasterPath = file.path("/mnt/scratch/cbarros", basename(getwd()), "R/SpaDES/scratch/raster")
                   , scratchPath = file.path("/mnt/scratch/cbarros", basename(getwd()), "R/SpaDES/scratch"))
} else {
  simPaths <- list(cachePath = normPath(file.path("R/SpaDES/cache", simDirName, "postSimAnalyses"))
                   , modulePath = normPath(file.path("R/SpaDES/m"))
                   , inputPath = normPath(file.path("R/SpaDES/inputs"))
                   , outputPath = normPath(file.path("R/SpaDES/outputs", simDirName)))
}

if (grepl("for-cast", Sys.info()["nodename"]) ||
    grepl("4458e1a42ddc", Sys.info()["nodename"])) {
  data.table::setDTthreads(5)
  options(bitmapType="cairo")
}

## path to figure folder and cache folder
figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane")

## merge Douglas-fir/dry-conifer stands?
## no need with last year classif
mergeDMCPSME <- FALSE  ## merge DMCPSME PSME dryPSME
mergePSME <- TRUE ## merge PSME dryPSME
if (mergeDMCPSME) {
  figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane/mergeDMCPSME")
  HVoutputPathMergedVegType <- file.path(simPaths$outputPath, "hypervolumes", "mergeDMCPSME")
}
if (mergePSME) {
  HVoutputPathMergedVegType <- file.path(simPaths$outputPath, "hypervolumes", "mergePSME")
  figOutputPath <- file.path(simPaths$outputPath, "figuresAnalysis/Montane/mergePSME")
}
dir.create(figOutputPath, recursive = TRUE)
```

### DATA LOADING AND PROCESSING NOTES
Given the size of the data put together in a pixel-based format, results were sampled every 10 years (instead of the 5-year interval used for saving),

```{r dataPrep, cache=FALSE, include=FALSE}
yearSubset <- unique(as.integer(c(seq(3511, 4011, 5), 4011)))
runPrepResultsModule <- FALSE
source("R/SpaDES/simResultsDataPrep.R")
source("R/SpaDES/obsResultsDataPrep.R")
rm(allPixelCohortData) ## not needed
gc(reset = TRUE)

if (mergeDMCPSME) {
  allPixelCohortDataMnt[vegTypeCN %in% c("DMCPSME", "PSME", "dryPSME"), vegTypeCN := "DMCPSME"]
  ageDataCN[Cover.dendro %in% c("DMCPSME", "PSME", "dryPSME"), Cover.dendro := "DMCPSME"]
}

if (mergePSME) {
  allPixelCohortDataMnt[vegTypeCN %in% c("PSME", "dryPSME"), vegTypeCN := "PSME"]
  ageDataCN[Cover.dendro %in% c("PSME", "dryPSME"), Cover.dendro := "PSME"]
}

## need to use sampled years as "last year" -- maybe average per rep
yearSamples <- sample5SimYears(allPixelCohortDataMnt[, .(year, rep)])   ## seed ensures same years are drawn

allPixelCDMntEnd <- allPixelCohortDataMnt[yearSamples, on = .(year, rep)]

## average all continuous properties and re-classify stands.
# allPixelCDMntEnd <- Cache(averagAllPixelCDMntEnd,
#                           allPixelCDMntEnd = allPixelCDMntEnd,
#                           omitArgs = "allPixelCDMntEnd",
#                           cacheRepo = simPaths$cachePath,
#                           .cacheExtra = .robustDigest(allPixelCDMntEnd[, .(pixelIndex, speciesCode, year, B)], quick = TRUE))
# 
# allPixelCDMntEnd[, vegTypeCN := as.factor(vegTypeCN)]
gc(reset = TRUE)


## add vegTypes at end  year - for pyrodiv HV vegTypes were classified at the end to capture
## 500 years of fire history. This was not the same in vegHV for which we sampled 5 years, each 
## with it's veg types -- this seems wrong or hard to compare but it will do for now.

## summarise fire data
source("R/R_tools/prepFireData4HVs.R")

## drop unused levels
allPixelCohortDataMnt$vegTypeCN <- droplevels(allPixelCohortDataMnt$vegTypeCN)
allPixelCDMntEnd$vegTypeCN <- droplevels(allPixelCDMntEnd$vegTypeCN)
summaryFireAttributes$vegTypeCN <- droplevels(summaryFireAttributes$vegTypeCN)

## get HV data
HVoutputPath <- file.path(simPaths$outputPath, "hypervolumes")
useFirstLastYear <- FALSE
source("R/R_tools/prepHVData.R")
```

```{r summaryTables, cache=FALSE, include=FALSE}
## SUMMARY ACROSS LANDSCAPE -----------------------------------
byCols <-  c("scenario", "rep", "year", "noFires")
cols <- which(as.matrix(allPixelCohortDataMnt[, lapply(.SD, is.numeric)]))
cols <- names(allPixelCohortDataMnt)[cols]
cacheExtra <- colSums(allPixelCohortDataMnt[, ..cols])

## BY SPECIES
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataSpp <- Cache(makeSummaryTable,
                                  cohortData = allPixelCohortDataMnt, 
                                  byCols = c(byCols, "speciesCode"),
                                  .cacheExtra = list(cacheExtra),
                                  cacheRepo = simPaths$cachePath,
                                  userTags = c("summaryBurnCohortDataSpp"),
                                  omitArgs = c("userTags", "cohortData"))
gc(reset = TRUE)

## BY FOREST TYPE (def. as dominant species)
## remember that biomass is multiplied by 100 in *boreal*, this will revert the units to tonnes/ha
summaryBurnCohortDataVegType <- Cache(makeSummaryTable,
                                      cohortData = allPixelCohortDataMnt, 
                                      byCols = c(byCols, "vegType"),
                                      .cacheExtra = list(cacheExtra),
                                      cacheRepo = simPaths$cachePath,
                                      userTags = c("summaryBurnCohortDataSpp"),
                                      omitArgs = c("userTags", "cohortData"))
gc(reset = TRUE)

## BY CAMERON'S VEG TYPE
summaryBurnCohortDataVegTypeCN <- Cache(makeSummaryTable,
                                        cohortData = allPixelCohortDataMnt, 
                                        byCols = c(byCols, "vegTypeCN"),
                                        .cacheExtra = list(cacheExtra),
                                        cacheRepo = simPaths$cachePath,
                                        userTags = c("summaryBurnCohortDataSpp"),
                                        omitArgs = c("userTags", "cohortData")) 
gc(reset = TRUE)
```

```{r plotLabels, include = FALSE}
source("R/R_tools/plotLabels&Cols.R")

## remove large objs rasters to save memory
rm(list = c(grep("Stk", ls(), value = TRUE)))
amc::.gc()
```

### TESTING DIFFERENCES BETWEEN OBSERVED AND SIMULATED DATA
AGES
At the end of the simulation (or averaged across sampled years), by species
```{r testAges}
## STAT TESTS ------------------------------------------
## AGE SIM VS OBS ----
## comparing simulated and observed ages
## ages compared at the species-level, rather than veg type given that some veg types in the sims don't exist
## in the obs data and this would lead to data loss
## simulated ages below the minimum DBH age are excluded from comparisons.
## note that species-level comparisons do not use average species ages, so the differences are calculated between 
## cohort age and the observed median species age
cols <- which(as.matrix(allPixelCDMntEnd[, lapply(.SD, is.numeric)]))
cols <- names(allPixelCDMntEnd)[cols]
cacheExtra <- colSums(allPixelCDMntEnd[, ..cols])
plotData <- Cache(do.call,
                  what = ageComp_data,
                  args = list("simData" = allPixelCDMntEnd,
                              "obsData" = ageDataCN,
                              "cacheRepo" = simPaths$cachePath),
                  .cacheExtra = list(cacheExtra),
                  userTags = "ageComp_data",
                  omitArgs = c("args", "userTags"),
                  cacheRepo = simPaths$cachePath)
plotData[, ageDiffSimObs := age - avgAgeSppObs]
plotData <- plotData[!is.na(ageDiffSimObs)]

ageDiffLMList <- lapply(split(plotData, by = "firePresAbs"), function(DT) {
  # lm(abs(abs(ageDiffSimObs)) ~ scenario * speciesCode, data = DT)
  nlme::gls(abs(abs(ageDiffSimObs)) ~ scenario * speciesCode, weights = nlme::varIdent(form = ~1|speciesCode),
            data = DT)   ## better AIC and residuals
})

plotData[firePresAbs == "0", 
         pred := predict(ageDiffLMList$`0`, type = "response")]
plotData[firePresAbs == "1", 
         pred := predict(ageDiffLMList$`1`, type = "response")]
if (isFALSE(class(ageDiffLMList$`0`) == "gls")) {
  plotData[firePresAbs == "0", 
           predSE := predict(ageDiffLMList$`0`, type = "response", se = TRUE)["se.fit"]]
}

if (isFALSE(class(ageDiffLMList$`1`) == "gls")) {
  plotData[firePresAbs == "1", 
           predSE := predict(ageDiffLMList$`1`, type = "response", se = TRUE)["se.fit"]]
}

plotTest1.2 <- ggplot(plotData, aes(x = firePresAbs)) +
  geom_boxplot(aes(y = abs(ageDiffSimObs), fill = scenario)) +
  scale_x_discrete(labels = c("0" = "no fire", "1" = "fire")) +
  scale_fill_manual(values = scenColours, labels = scenLabels) +
  theme_pubr(base_size = 16) +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Differences between median simulated and observed ages",
       y = expression(bgroup("|", "sim." - bar("obs."), "|")),
       x = "")

plotTest1 <- plotTest1.2 +
  facet_wrap(~ speciesCode, labeller = labeller(speciesCode = speciesLabels))

```

```{r plot&savePlots, echo = FALSE}
plotSave <- ggarrange(plotTest1, 
                      plotTest1.2, common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20),
                      widths = c(1, 0.6))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest.tiff"),
       width = 14, height = 7)
rm(plotTest1)  ## plotTest1.2 is used again later
gc()
```

## BIOMASS, MORTALITY, AVG. AGE AND NO COHORTS BY SPECIES
```{r plotsBySpecies, cache = FALSE}
## PLOTS -----------------------------------------------
## MODELLED PROPERTIES ---------------------------------
## total biomass
## biomass
byCols <- c("scenario", "rep", "speciesCode", "firePresAbs", "noFires")
plotData <- summaryBurnCohortDataSpp[, .SD, .SDcols = c(byCols, "BiomassBySpecies")]
plotData$scenario <- as.character(scenLabels[match(plotData$scenario, names(scenLabels))])
plotData[, logBiomassBySpecies := log(BiomassBySpecies + 1)]

plot1 <- summaryPlot(data = plotData, x = "speciesCode", y = "logBiomassBySpecies", 
                     colour = "speciesCode", xlabels = speciesLabels, colValues = speciesColours,
                     colLabels = speciesLabels, titleLab = "Total landscape biomass", 
                     subtitleLab = "by species", yLab = "log-biomass (ton/ha)",
                     x.text.angle = 45)
plot1 <- plot1 +
  guides(colour = "none") +
  facet_grid(scenario ~ firePresAbs, labeller = labeller(scenario = label_parsed))

plot2 <- summaryPlot(data = plotData, x = "noFires", y = "logBiomassBySpecies", 
                     colour = "speciesCode", colValues = speciesColours, 
                     colLabels = speciesLabels, titleLab = "Total landscape biomass",
                     subtitleLab = "by species", yLab = "log-biomass (ton/ha)")
plot2 <- plot2 +
  stat_summary(fun = "mean", position = position_dodge(width = 0.8),
               geom = "line") +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ ., labeller = labeller(scenario = label_parsed))

## average age
plotData <- plotData[,  ## absences can't lower the average ages
                     list(avgAgeBySppSim = median(age, na.rm = TRUE)),
                     by = .(scenario, rep, pixelIndex, year, firePresAbs, speciesCode)]
plotData[is.nan(avgAgeBySppSim), avgAgeBySppSim := 0]
plotData$scenario <- as.character(scenLabels[match(plotData$scenario, names(scenLabels))])

plot5 <- summaryPlot(data = plotData, x = "speciesCode", y = "avgAgeBySppSim", 
                     colour = "speciesCode", xlabels = speciesLabels, colValues = speciesColours,
                     colLabels = speciesLabels, titleLab = "Species age", 
                     yLab = "Median biomass-weighted age",
                     x.text.angle = 45) +
  facet_grid(scenario ~ firePresAbs,
             labeller = labeller(scenario = label_parsed, firePresAbs = c("0" = "no fire", "1" = "fire")))

plot6 <- summaryPlot(data = plotData, x = "noFires", y = "avgAgeBySppSim", 
                     colour = "speciesCode", colValues = speciesColours,
                     colLabels = speciesLabels, titleLab = "Species age", 
                     yLab = "Median biomass-weighted age") +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  guides(colour = guide_legend(override.aes = list(size = 1.5))) +
  facet_grid(scenario ~ ., labeller = label_parsed)

gc(reset = TRUE)
```

```{r plot&savePlots3, echo = FALSE}
## biomass
plotSave <- ggarrange(plot1,
                      plot2 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeB.tiff"),
       width = 14, height = 7)

## age
plotSave <- ggarrange(plot5,
                      plot6 +
                        theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
                        labs(title = "", subtitle = ""),
                      widths = c(0.4, 0.7),
                      legend = "bottom", common.legend = TRUE,
                      labels = "auto", font.label = list(size = 20))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_landscapeAge.tiff"),
       width = 14, height = 7)

rm(plot1, plot2, plot5, plot6)
gc()
```

## COMPARING SIMULATED AND OBSERVED DATA
### Age medians CIs - by species
```{r simVsObsAges, cache = FALSE}
## SIMULATED VS. OBSERVED DATA ------------
## age distribution at end of simulation vs cameron's
## pixel-level differences from observed medians

plotData <- ageComp_data(allPixelCDMntEnd, ageDataCN, biomassWeighted = FALSE, cacheRepo = simPaths$cachePath)
plotData2 <- copy(ageDataCN[, .(speciesCode, Reconstructed.age, firePresAbs)])
plotData2 <- plotData2[!is.na(speciesCode)]

## TODO: avgAgeBySppSim should be raw ages.

plot29 <- simObsDistsPlot(simData = plotData, x = "speciesCode", ySim = "avgAgeBySppSim",
                          colSim = "scenario", obsData = plotData2, yObs = "Reconstructed.age", 
                          xlabels = speciesLabels, x.text.angle = 45,
                          colValues = scenColours, 
                          colLabels = scenLabels, 
                          titleLab = "Biomass-weighted age", subtitleLab = "by species", yLab = "age") 
plot29 <- plot29 +
  facet_grid(~ firePresAbs,
             labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire"))) 

plotData[, firePresAbs := as.factor(firePresAbs)]
plotData2[, firePresAbs := as.factor(firePresAbs)]
plot30 <- simObsDistsPlot(simData = plotData, x = "firePresAbs", ySim = "avgAgeBySppSim",
                          colSim = "scenario", obsData = plotData2, yObs = "Reconstructed.age", 
                          xlabels = c("0" = "no fire", "1" = "fire"), 
                          colValues = scenColours, 
                          colLabels = scenLabels, 
                          titleLab = "Biomass-weighted age", subtitleLab = "across species", yLab = "age") 

## only fire pixels, no means
plotData3 <- data.table(plotData2[firePresAbs == 1], scenario = "observed")
setnames(plotData3, "Reconstructed.age", "avgAgeBySppSim")
plotData3 <- rbind(plotData3, plotData[firePresAbs == 1], fill = TRUE, use.names = TRUE)
plotData3[, scenario := factor(scenario, levels = c("noPM", "observed", "PM"))]

plot29.1 <- simObsDistsPlot(simData = plotData3, x = "speciesCode", ySim = "avgAgeBySppSim",
                            showMeans = FALSE, colSim = "scenario", xlabels = speciesLabels, 
                            colValues = scenColours, 
                            x.text.angle = 45,
                            colLabels = scenLabels, 
                            titleLab = "Biomass-weighted age", subtitleLab = "by species", yLab = "age")

plot30.1 <- simObsDistsPlot(simData = plotData3, x = "scenario", ySim = "avgAgeBySppSim",
                            showMeans = FALSE, colSim = "scenario", xlabels = scenLabels, 
                            colValues = scenColours,
                            colLabels = scenLabels, 
                            titleLab = "Biomass-weighted age", subtitleLab = "across species", yLab = "age")

```

```{r plot&savePlots7, echo = FALSE}
plotSave <- plot_grid(plot_grid(plot29 + theme(legend.position = "none"),
                                plot30 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObs.tiff"),
       width = 14, height = 7)

plotSave <- plot_grid(plot_grid(plot29.1 + theme(legend.position = "none"),
                                plot30.1 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29.1 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObs2.tiff"),
       width = 14, height = 7)
```

### Age medians CIs - by forest type
Forest types are defined for a sample of years across the quasi equilibrium period.
Non-forest forest type removed -- not present in observed data, so could impact "landscape" comparisons

```{r simVsObsAges_vegType, cache = FALSE}
## SIMULATED VS. OBSERVED DATA ------------
## age distribution at end of simulation vs cameron's
plotData <- ageComp_data(allPixelCDMntEnd, ageDataCN, speciesLevel = FALSE, cacheRepo = simPaths$cachePath)
plotData2 <- ageDataCN[, .(Cover.dendro, Stand.age.3, firePresAbs)]
setnames(plotData2, "Cover.dendro", "vegTypeCN")
plotData2 <- plotData2[, list(avgAgeBySppObs = median(Stand.age.3, na.rm = TRUE)),
                       by = .(vegTypeCN, firePresAbs)]

## TODO: avgAgeBySppSim should be stand ages.

plot29.2 <- simObsDistsPlot(simData = plotData, x = "vegTypeCN", ySim = "avgAgeBySppSim",
                            colSim = "scenario", obsData = plotData2, yObs = "Stand.age.3", 
                            xlabels = vegTypeCNLabels, x.text.angle = 45,
                            colValues = scenColours, 
                            colLabels = scenLabels, 
                            titleLab = "Biomass-weighted age", subtitleLab = "by forest type", yLab = "age") 
plot29.2 <- plot29.2 +
  facet_grid( ~ firePresAbs,
              labeller = labeller(scenario = scenLabels, firePresAbs = c("0" = "no fire", "1" = "fire"))) 

plotData[, firePresAbs := as.factor(firePresAbs)]
plotData2[, firePresAbs := as.factor(firePresAbs)]
plot30.2 <- simObsDistsPlot(simData = plotData, x = "firePresAbs", ySim = "avgAgeBySppSim",
                            colSim = "scenario", obsData = plotData2, yObs = "Stand.age.3", 
                            xlabels = c("0" = "no fire", "1" = "fire"),
                            colValues = scenColours, 
                            colLabels = scenLabels, 
                            titleLab = "Biomass-weighted age", subtitleLab = "across forest type", yLab = "age") 


## only fire pixels, no means
plotData3 <- data.table(plotData2[firePresAbs == 1], scenario = "observed")
setnames(plotData3, "Stand.age.3", "avgAgeBySppSim")
plotData3 <- rbind(plotData3, plotData[firePresAbs == 1], fill = TRUE, use.names = TRUE)
plotData3[, scenario := factor(scenario, levels = c("noPM", "observed", "PM"))]

plot29.3 <- simObsDistsPlot(simData = plotData3, x = "vegTypeCN", ySim = "avgAgeBySppSim",
                            colSim = "scenario", x.text.angle = 45,
                            xlabels = vegTypeCNLabels, showMeans = FALSE,
                            colValues = scenColours, 
                            colLabels = scenLabels, 
                            titleLab = "Biomass-weighted age", subtitleLab = "by forest type", yLab = "age") 

plot30.3 <- simObsDistsPlot(simData = plotData3, x = "scenario", ySim = "avgAgeBySppSim",
                            colSim = "scenario",
                            xlabels = scenLabels, showMeans = FALSE,
                            colValues = scenColours, 
                            colLabels = scenLabels, 
                            titleLab = "Biomass-weighted age", subtitleLab = "across forest type", yLab = "age") 
```

```{r plot&savePlots8, echo = FALSE}
plotSave <- plot_grid(plot_grid(plot29.2 + theme(legend.position = "none"),
                                plot30.2 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29.2 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsVegTypeCN.tiff"),
       width = 14, height = 7)

plotSave <- plot_grid(plot_grid(plot29.3 + theme(legend.position = "none"),
                                plot30.3 + theme(legend.position = "none"),
                                nrow = 1, rel_widths = c(1, 0.7),
                                labels = "auto", label_size = 20, axis = "b", align = "h"),
                      get_legend(plot29.3 + theme(legend.direction = "vertical")), 
                      rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsVegTypeCN2.tiff"),
       width = 14, height = 7)
```

### Median absolute deviations and quantile deviations of simulated ages by stand type
(quantile deviations - 50, 75, 95%)
Forest types are defined for a sample of years across the quasi equilibrium period.
Non-forest forest type removed -- not present in observed data, so could impact "landscape" comparisons

```{r simVsObsAgesDif, cache = FALSE}
## mean age differences
## calculate avg weighted ages (per species) per pixel first, then average across species per pixel
## then take the absolute difference of each stand to the observed average (per veg type) across reps
plotData <- ageComp_data(allPixelCDMntEnd, ageDataCN, speciesLevel = FALSE, 
                         addLandscape = TRUE, cacheRepo = simPaths$cachePath)
plotData <- plotData[, avgAgeBySppSim := median(avgAgeBySppSim, na.rm = TRUE),
                     by = .(scenario, rep, year, pixelIndex, firePresAbs, vegTypeCN)]
plotData[, speciesCode := NULL]
plotData <- plotData[!is.na(avgAgeBySppObs)]
plotData <- unique(plotData)

plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(avgAgeBySppSim - avgAgeBySppObs))),
                      by = .(scenario, rep, vegTypeCN, firePresAbs)]

## differences
x_order <- names(vegTypeCNLabels[vegTypeCNLabels != "No forest"])
plot32 <- DevPlot(plotData, x = "vegTypeCN", y = avgAgeBySppSim - avgAgeBySppObs,
                  xlabels = vegTypeCNLabels, xorder = x_order,
                  fillLabels = scenLabels, fillValues = scenColours,
                  xFacet = "firePresAbs", 
                  labllr = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")),
                  titleLab = "Avg. differences from observed ages",
                  yLab = expression("sim." - bar("obs.")))


## mean absolute differences
plot32.2 <- MADPlot(plotData2, x = "vegTypeCN", y = "meanAbsDevSimObs", 
                    colour = "scenario", colValues = scenColours, 
                    colLabels = scenLabels, xlabels = vegTypeCNLabels,
                    xorder = x_order, xFacet = "firePresAbs", 
                    labllr = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")),
                    titleLab = "Mean abs. deviation from observed ages",
                    yLab = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))))

## QUANTILE DEVIATIONS
## forest-type-level differences between simulated and observed upper quantiles
plotData <- ageComp_data(allPixelCDMntEnd, ageDataCN, speciesLevel = FALSE, 
                         addLandscape = TRUE, cacheRepo = simPaths$cachePath)
plotData[, speciesCode := NULL]
plotData <- plotData[!is.na(avgAgeBySppObs)]
plotData <- unique(plotData)

plotData <- plotData[, `:=`(quant50AgeBySpp = quantile(avgAgeBySppSim, probs = 0.5, na.rm = TRUE),
                            quant75AgeBySpp = quantile(avgAgeBySppSim, probs = 0.75, na.rm = TRUE),
                            quant95AgeBySpp = quantile(avgAgeBySppSim, probs = 0.95, na.rm = TRUE)),
                     by = .(scenario, rep, firePresAbs, vegTypeCN)]

plotData2 <- rbind(
  ageDataCN[, list(quant50AgeBySppObs = quantile(Stand.age.3, probs = 0.5, na.rm = TRUE),
                   quant75AgeBySppObs = quantile(Stand.age.3, probs = 0.75, na.rm = TRUE),
                   quant95AgeBySppObs = quantile(Stand.age.3, probs = 0.95, na.rm = TRUE)), 
            by = .(Cover.dendro, firePresAbs)],
  ageDataCN[, list(quant50AgeBySppObs = quantile(Stand.age.3, probs = 0.5, na.rm = TRUE),
                   quant75AgeBySppObs = quantile(Stand.age.3, probs = 0.75, na.rm = TRUE),
                   quant95AgeBySppObs = quantile(Stand.age.3, probs = 0.95, na.rm = TRUE),
                   Cover.dendro = "landscape"), 
            by = .(firePresAbs)])

plotData <- plotData2[plotData, on = c("Cover.dendro==vegTypeCN", "firePresAbs")]
setnames(plotData, "Cover.dendro", "vegTypeCN")
plotData[, firePresAbs := as.factor(firePresAbs)]
plotData <- plotData[!is.na(quant50AgeBySppObs)]
if (any(is.na(plotData))) stop()

## this mean makes no sense. there should be only one value this is simply a deviation.
plotData2 <- plotData[, list(meanAbsDevSimObsQuant50 = 1/.N * sum(abs(quant50AgeBySpp - quant50AgeBySppObs)),
                             meanAbsDevSimObsQuant75 = 1/.N * sum(abs(quant75AgeBySpp - quant75AgeBySppObs)),
                             meanAbsDevSimObsQuant95 = 1/.N * sum(abs(quant95AgeBySpp - quant95AgeBySppObs))),
                      by = .(scenario, rep, vegTypeCN, firePresAbs)]
plotData2 <- melt(plotData2, id.vars = c("scenario", "rep", "vegTypeCN", "firePresAbs"))

plot32.3 <- ggplot(plotData2, 
                   aes(x = vegTypeCN, y = value, colour = variable, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               alpha = 0.7, fill = "white") +
  scale_color_viridis_d(option = "viridis", begin = 0.3, end = 0.8, 
                        labels = c("meanAbsDevSimObsQuant50" = "50%", 
                                   "meanAbsDevSimObsQuant75" = "75%", 
                                   "meanAbsDevSimObsQuant95" = "95%"),
                        name = "Quantile: ") +
  scale_x_discrete(labels = vegTypeCNLabels, 
                   limits = unique(c("landscape", sort(unique(plotData2$vegTypeCN)))),
                   expand = c(-0.2, 1.1)) +
  scale_shape_manual(labels = scenLabels, values = c("PM" = 24, "noPM" = 19)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Quantile absolute deviation", shape = "",
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|")), x = "") +
  coord_flip() +
  facet_wrap(~ firePresAbs, scales = "free_x", 
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## only pixels with fire
## order veg types, with landscape at the end
factorLevs <- c(as.character(sort(setdiff(unique(plotData2$vegTypeCN), "landscape"))), "landscape")
plotData2[, vegTypeCN := factor(vegTypeCN, levels = factorLevs)]

plot32.4 <- ggplot(plotData2[firePresAbs == "1"], 
                   aes(x = variable, y = value, colour = scenario, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               size = 0.7) +
  scale_x_discrete(labels = c("meanAbsDevSimObsQuant50" = "50%", 
                              "meanAbsDevSimObsQuant75" = "75%", 
                              "meanAbsDevSimObsQuant95" = "95%")) +
  scale_shape_discrete(labels = scenLabels, name = "") +
  scale_color_discrete(labels = scenLabels, name = "") +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(title = "Quantile absolute deviation", x = "", 
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|"))) +
  facet_wrap(~ vegTypeCN, scales = "free_x", ncol = 4,
             labeller = labeller(vegTypeCN = vegTypeCNLabels))

```

```{r plot&savePlots13, echo = FALSE}
plot32
ggsave(plot = plot32 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAgeDiffVegTypeCN.tiff"),
       width = 14, height = 7)
plot32.2
ggsave(plot = plot32.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsAgeDevVegTypeCN.tiff"),
       width = 10, height = 5)
plot32.3
ggsave(plot = plot32.3 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_MADquantVegTypeCNs.tiff"),
       width = 10, height = 6)

plotSave <- plot_grid(
  plot_grid(plot29.2 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.2 + theme(legend.position = "none", plot.title = element_blank()),
            nrow = 1, rel_widths = c(1, 0.7), axis = "b", align = "h",
            labels = "auto", label_size = 20),
  plot_grid(plot32.2 + theme(legend.position = "none", plot.title = element_blank()),
            get_legend(plot29.2 + theme(legend.direction = "vertical")),
            nrow = 1, rel_widths = c(1, 0.7), axis = "t", align = "v",
            labels = c("c", ""), label_size = 20),
  nrow = 2, rel_heights = c(1, 0.7), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MAD_VegTypeCN.tiff"),
       width = 12, height = 10)

plotSave <- plot_grid(
  plot_grid(plot29.2 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.2 + theme(legend.position = "bottom", plot.title = element_blank()),
            nrow = 1, 
            rel_widths = c(1, 0.7),
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot32.3 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MADquant_VegTypeCN.tiff"),
       width = 10, height = 10)

plotSave <- plot_grid(
  plot_grid(plot29.3 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.3 + theme(legend.position = "right", plot.title = element_blank(), plot.subtitle = element_blank()),
            nrow = 1, 
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot32.4 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "lr", align = "v")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MADquant_VegTypeCN2.tiff"),
       width = 10, height = 10)

gc()
```

### Mean absolute deviations and quantile deviations of simulated ages by species
(typical MAD, and quantile deviations - 50, 75, 95%)
```{r simVsObsAgesDif2, cache = FALSE}
## mean age differences
## calculate avg weighted ages across observed stands first
## then the absolute difference of each stand to the observed average (per veg type) across reps
## don't average across years/pixels -- leave all replicates.
plotData <- allPixelCDMntEnd[B > 0,
                             list(avgAgeBySppSim = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                sum((B/100), na.rm = TRUE))),
                             by = .(scenario, rep, year, pixelIndex, firePresAbs, speciesCode)]
plotData$age <- NULL
plotData <- unique(plotData)
plotData2 <- copy(plotData)
plotData2[ , speciesCode := "landscape"]
plotData <- rbind(plotData, plotData2)

plotData2 <- ageDataCN[, .(speciesCode, Reconstructed.age, firePresAbs)]
plotData2 <- plotData2[!is.na(speciesCode)]

plotData3 <- copy(plotData2)
plotData3[, speciesCode := "landscape"]
plotData2 <- rbind(plotData2, plotData3)

plotData2 <- plotData2[, list(avgAgeBySppObs = median(Reconstructed.age, na.rm = TRUE)),
                       by = .(speciesCode, firePresAbs)]

plotData <- plotData2[plotData, on = .(speciesCode, firePresAbs)]
plotData <- plotData[!is.na(avgAgeBySppObs) & !is.na(avgAgeBySppSim)]
plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(avgAgeBySppSim - median(avgAgeBySppObs)))),
                      by = .(scenario, rep, speciesCode, firePresAbs)]

## differences
plot43 <- DevPlot(plotData, x = "speciesCode", y = avgAgeBySppSim - avgAgeBySppObs,
                  xlabels = speciesLabels, fillValues = scenColours,
                  fillLabels = scenLabels, xFacet = "firePresAbs", 
                  labllr = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")),
                  titleLab = "Avg. differences from observed ages",
                  yLab = expression("sim." - bar("obs.")))


## mean absolute differences
plot43.2 <- MADPlot(plotData2, x = "speciesCode", y = "meanAbsDevSimObs", 
                    colour = "scenario", colValues = scenColours, colLabels = scenLabels, 
                    xlabels = c(speciesLabels, landscape = "landscape"),
                    xorder = c("landscape", names(speciesLabels)), xFacet = "firePresAbs", 
                    labllr = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")),
                    titleLab = "Mean abs. deviation from observed ages",
                    yLab = expression(bar(bgroup("|", "sim." - bar("obs."), "|")))) 


## species-level differences between simulated and observed upper quantiles
plotData <- allPixelCDMntEnd[B > 0,  ## absences can't lower the average ages
                             list(avgAgeBySppSim = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                sum((B/100), na.rm = TRUE))),
                             by = .(scenario, rep, pixelIndex, firePresAbs, speciesCode)]
plotData$age <- NULL
plotData <- unique(plotData)
plotData2 <- copy(plotData)
plotData2[ , speciesCode := "landscape"]
plotData <- rbind(plotData, plotData2)

plotData <- plotData[, list(quant50AgeBySpp = quantile(avgAgeBySppSim, probs = 0.5, na.rm = TRUE),
                            quant75AgeBySpp = quantile(avgAgeBySppSim, probs = 0.75, na.rm = TRUE),
                            quant95AgeBySpp = quantile(avgAgeBySppSim, probs = 0.95, na.rm = TRUE)),
                     by = .(scenario, rep, firePresAbs, speciesCode)]

plotData2 <- copy(ageDataCN[, .(speciesCode, Reconstructed.age, firePresAbs)])
plotData2 <- plotData2[!is.na(speciesCode)]

plotData3 <- copy(plotData2)
plotData3[, speciesCode := "landscape"]
plotData2 <- rbind(plotData2, plotData3)

plotData2 <- plotData2[, list(quant50AgeBySppObs = quantile(Reconstructed.age, probs = 0.5, na.rm = TRUE),
                              quant75AgeBySppObs = quantile(Reconstructed.age, probs = 0.75, na.rm = TRUE),
                              quant95AgeBySppObs = quantile(Reconstructed.age, probs = 0.95, na.rm = TRUE)), 
                       by = .(speciesCode, firePresAbs)]

plotData <- plotData2[plotData, on = .(speciesCode, firePresAbs)]
plotData[, firePresAbs := as.factor(firePresAbs)]
plotData <- plotData[!is.na(quant50AgeBySppObs)]
if (any(is.na(plotData))) stop()

plotData2 <- plotData[, list(meanAbsDevSimObsQuant50 = 1/.N * sum(abs(quant50AgeBySpp - quant50AgeBySppObs)),
                             meanAbsDevSimObsQuant75 = 1/.N * sum(abs(quant75AgeBySpp - quant75AgeBySppObs)),
                             meanAbsDevSimObsQuant95 = 1/.N * sum(abs(quant95AgeBySpp - quant95AgeBySppObs))),
                      by = .(scenario, rep, speciesCode, firePresAbs)]

plotData2 <- melt(plotData2, id.vars = c("scenario", "rep", "speciesCode", "firePresAbs"))

plot43.3 <- ggplot(plotData2, 
                   aes(x = speciesCode, y = value, colour = variable, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               alpha = 0.7, fill = "white") +
  scale_color_viridis_d(option = "viridis", begin = 0.3, end = 0.8, 
                        labels = c("meanAbsDevSimObsQuant50" = "50%", 
                                   "meanAbsDevSimObsQuant75" = "75%", 
                                   "meanAbsDevSimObsQuant95" = "95%"),
                        name = "Quantile: ") +
  scale_x_discrete(labels = speciesLabels,
                   limits = unique(c("landscape", sort(plotData2$speciesCode))),
                   expand = c(-0.2, 1.1)) +
  scale_shape_manual(labels = scenLabels, values = c("PM" = 24, "noPM" = 19)) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(title = "Quantile absolute deviation", shape = "",
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|")), x = "") +
  coord_flip() +
  facet_wrap(~ firePresAbs, scales = "free_x", 
             labeller = labeller(firePresAbs = c("0" = "no fire", "1" = "fire")))

## only pixels with fire
## order veg types, with landscape at the end
factorLevs <- c(as.character(sort(setdiff(unique(plotData2$speciesCode), "landscape"))), "landscape")
plotData2[, speciesCode := factor(speciesCode, levels = factorLevs)]

plot43.4 <- ggplot(plotData2[firePresAbs == "1"], 
                   aes(x = variable, y = value, colour = scenario, 
                       shape = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  stat_summary(fun.data = "mean_ci", position = position_dodge(width = 0.8),
               size = 1) +
  scale_x_discrete(labels = c("meanAbsDevSimObsQuant50" = "50%", 
                              "meanAbsDevSimObsQuant75" = "75%", 
                              "meanAbsDevSimObsQuant95" = "95%")) +
  scale_shape_discrete(labels = scenLabels, name = "") +
  scale_color_discrete(labels = scenLabels, name = "") +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(panel.grid.major.x = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(title = "Quantile absolute deviation", x = "", 
       y = expression(bgroup("|", "quant."["sim."] - "quant."["obs."], "|"))) +
  facet_wrap(~ speciesCode, scales = "free_x", ncol = 3,
             labeller = labeller(speciesCode = c(speciesLabels, landscape = "landscape")))
```

```{r plot&savePlots14, echo = FALSE}
plot43
ggsave(plot = plot43 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAgeDiffSpecies.tiff"),
       width = 14, height = 7)
plot43.2
ggsave(plot = plot43.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsAgeDevSpecies.tiff"),
       width = 10, height = 5)

plot43.3
ggsave(plot = plot43.3 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_MADquantSpecies.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(plot_grid(plot43 + theme(legend.position = "none"),
                                plotTest1.2 + theme(legend.position = "none"),
                                ncol = 2, nrow = 1, align = "h", axis = "b",
                                labels = "auto", font.label = list(size = 20),
                                rel_widths = c(1, 0.7)), 
                      get_legend(plot43 + theme(legend.direction = "vertical")),
                      ncol = 2, nrow = 1, rel_widths = c(1, 0.15))
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_meanAbsAgeDev_ageSimVsObsTestSpecies.tiff"),
       width = 15, height = 7)

plotSave <- plot_grid(
  plot_grid(plot29 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30 + theme(legend.position = "none", plot.title = element_blank()),
            nrow = 1, rel_widths = c(1, 0.7), axis = "b", align = "h",
            labels = "auto", label_size = 20),
  plot_grid(plot43.2 + theme(legend.position = "none", plot.title = element_blank()),
            get_legend(plot29 + theme(legend.direction = "vertical")),
            nrow = 1, rel_widths = c(1, 0.7), axis = "t", align = "v",
            labels = c("c", ""), label_size = 20),
  nrow = 2, rel_heights = c(1, 0.7), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MAD_Species.tiff"),
       width = 10, height = 10)

plotSave <- plot_grid(
  plot_grid(plot29 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30 + theme(legend.position = "bottom", plot.title = element_blank()),
            nrow = 1, 
            rel_widths = c(1, 0.7),
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot43.3 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "l", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MADquant_Species.tiff"),
       width = 10, height = 10)


plotSave <- plot_grid(
  plot_grid(plot29.1 + theme(legend.position = "none", plot.title = element_blank(), plot.subtitle = element_blank()),
            plot30.1 + theme(legend.position = "bottom", plot.title = element_blank(), plot.subtitle = element_blank()),
            nrow = 1, 
            axis = "b", align = "h",
            labels = c("a", "b", ""), label_size = 20),
  plot_grid(plot43.4 + theme(legend.position = "right",
                             plot.title = element_blank(),
                             legend.direction = "vertical",
                             legend.box = "vertical"),
            labels = c("c"), label_size = 20),
  nrow = 2, rel_heights = c(0.8, 1), axis = "lr", align = "h")
plotSave
ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_ageSimVsObsTest_MADquant_Species2.tiff"),
       width = 10, height = 10)

# rm(plot43, plot43.2, plotTest1.2)
gc()
```

### No. fires, fire frequency, fire size and fire severity
```{r simVsObsFires, cache = FALSE}
## fire size distribution
plot37 <- densityPlot(summaryFireAttributes[vegTypeCN != "No veg."], 
                      x = meanPatchS + 1, fill = "scenario", alpha = "scenario",
                      fillValues = scenColours, fillLabels = scenLabels, 
                      alphaValues = c("PM" = 0.6, "noPM" = 1),
                      titleLab = "Fire patch size distribution",
                      xLab = "Mean patch size (no. pixels)")

plot37.2 <- plot37.2 +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## average no. of pixels with certain fire frequency
plotData <- allPixelCohortDataMnt[, list(noPixels = length(unique(pixelIndex))),
                                  by = .(scenario, rep, year, noFires)]
plot38 <- ggplot(plotData,
                 aes(x = as.factor(noFires), y = noPixels, fill = scenario)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge", alpha = 0.5) +
  stat_summary(fun.data = "mean_sd", aes(colour = scenario),
               geom = "errorbar", position = "dodge", show.legend = FALSE) +
  stat_summary(aes(label = round(..y..), colour = scenario),
               fun = "mean", geom = "text", show.legend = FALSE,
               position = position_dodge(width = 0.9), vjust = -1) +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(x = "no. fires", y = "no. pixels")

## average no. of fires per forest type across quasi-equilibrium period
plotData <- allPixelCDMntEnd[vegTypeCN != "No veg.", 
                             list(meanNoFires = mean(noFires),
                                  sdNoFires = sd(noFires)),
                             by = .(scenario, vegTypeCN)]
plot36 <- ggplot(plotData) +
  geom_bar(aes(x = vegTypeCN, y = meanNoFires, fill = scenario),
           position = "dodge", stat = "identity", alpha = 0.5) +
  geom_errorbar(aes(x = vegTypeCN,
                    ymin = meanNoFires - sdNoFires, 
                    ymax = meanNoFires + sdNoFires,
                    colour = scenario),
                position = "dodge", show.legend = FALSE) +
  scale_fill_discrete(labels = scenLabels) +
  scale_colour_discrete(labels = scenLabels) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  labs(y = "no. fires", x = "")

## only simulated fire intervals
plot39.3 <- densityPlot(summaryFireAttributes[vegTypeCN != "No veg."], 
                        x = meanFreq + 1, fill = "scenario", alpha = "scenario",
                        fillValues = scenColours, fillLabels = scenLabels, 
                        alphaValues = c("PM" = 0.6, "noPM" = 1),
                        titleLab = "Fire interval distribution",
                        xLab = "Mean fire interval")

plot39.4 <- plot39.3 + 
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## distribution of fire severity per stand across landscape
plot40 <- densityPlot(summaryFireAttributes[vegTypeCN != "No veg."], 
                      x = meanSevB + 1, fill = "scenario", alpha = "scenario",
                      fillValues = scenColours, fillLabels = scenLabels, 
                      alphaValues = c("PM" = 0.6, "noPM" = 1),
                      titleLab = "Fire severity distribution",
                      xLab = "Mean fire severity\n(biomass lost, ton/ha)")

## distribution of fire severity per stand by veg types defined for a sample of years across the quasi equilibrium period.
## as used for HVs
plot41 <- plot40 +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))

## distribution of fire severity by veg types defined every year
## so not always the same pixels
plotData <- unique(allPixelCohortDataMnt[vegTypeCN != "No veg.", .(scenario, rep, year, pixelIndex, vegTypeCN)])
plotData <- summaryFireAttributes[vegTypeCN != "No veg.",
                                  .(scenario, rep, pixelIndex, meanSevB)][plotData, on = .(scenario, rep, pixelIndex)]
plot42 <- densityPlot(plotData, 
                      x = log(meanSevB + 1), fill = "scenario", alpha = "scenario",
                      fillValues = scenColours, fillLabels = scenLabels, 
                      alphaValues = c("PM" = 0.6, "noPM" = 1),
                      titleLab = "Fire severity distribution",
                      xLab = "Mean fire severity\n(biomass lost, ton/ha)")
plot42 <- plot42 +
  facet_wrap(~ vegTypeCN, ncol = 4, labeller = labeller(vegTypeCN = vegTypeCNLabels))
```

```{r plot&savePlots15, echo = FALSE}
plotSave <- ggarrange(plot37 + theme(plot.title = element_blank()), 
                      plot37.2 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "results_meanPatchSizeDist.tiff"),
       width = 16, height = 6)
ggsave(plot = plot36 + theme(legend.position = c(0.9, 0.9), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_noFiresVegTypeCN.tiff"),
       width = 8, height = 7)
ggsave(plot = plot38 + theme(legend.position = c(0.9, 0.9), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_noPixelsVsnoFires.tiff"),
       width = 8, height = 7)
plotSave <- ggarrange(plot39.3 + theme(plot.title = element_blank()), 
                      plot39.4 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "results_meanFireIntDist.tiff"),
       width = 16, height = 6)

plotSave <- ggarrange(plot40 + theme(plot.title = element_blank()), 
                      plot41 + theme(plot.title = element_blank()),
                      widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", common.legend = TRUE, legend = "bottom")
ggsave(plotSave, filename = file.path(figOutputPath, "results_meanSevDist.tiff"),
       width = 16, height = 6)

ggsave(plot = plot42 + theme(legend.position = c(0.9, 0.1), legend.background = element_blank()),
       filename = file.path(figOutputPath, "results_meanSevDist_sampleYearVegTypeCN.tiff"),
       width = 10, height = 8)

plotSave <- ggarrange(plot37 + theme(plot.title = element_blank()),
                      plot37.2 + theme(plot.title = element_blank()),
                      plot39.3, 
                      plot39.4 + theme(plot.title = element_blank()),
                      plot40, 
                      plot41 + theme(plot.title = element_blank()),
                      common.legend = TRUE, legend = "bottom",
                      nrow = 3, ncol = 2, widths = c(0.5, 1),
                      font.label = list(size = 20),
                      labels = "auto", align = "hv")
ggsave(plot = plotSave,
       filename = file.path(figOutputPath, "results_fireAttrLandscape.tiff"),
       width = 16, height = 12)

```

### boxplots of  no. fires, fire frequency, fire size and fire severity
Non-forest forest types and pixels w/o included since these plots are showing data used for PBRs
```{r fireAttr_boxplots, cache = FALSE}
x_order <- names(vegTypeCNLabels)
## fire size
plot45 <- boxPlot(data, x = "vegTypeCN", y = meanPatchS + 1, 
                  fill = "scenario", xlabels = vegTypeCNLabels, xorder = x_order,
                  fillValues = scenColours, fillLabels = scenLabels,
                  titleLab = NULL, yLab = "Mean patch size (no. pixels)")

plot46 <- boxPlot(summaryFireAttributes, x = "vegTypeCN", y = meanFreq + 1, 
                  fill = "scenario", xlabels = vegTypeCNLabels, xorder = x_order,
                  fillValues = scenColours, fillLabels = scenLabels,
                  titleLab = NULL, yLab = "Mean fire interval (years)")

## fire severity
plot47 <- boxPlot(summaryFireAttributes, x = "vegTypeCN", y = meanSevB + 1, 
                  fill = "scenario", xlabels = vegTypeCNLabels, xorder = x_order,
                  fillValues = scenColours, fillLabels = scenLabels,
                  titleLab = NULL, yLab = "Mean fire severity\n(biomass lost, ton/ha)")
```

```{r plot&savePlots17, echo = FALSE}
plotSave <- ggarrange(plot45,
                      plot46, 
                      plot47, 
                      common.legend = TRUE, legend = "bottom",
                      ncol = 1,
                      font.label = list(size = 20),
                      labels = "auto")
ggsave(plot = plotSave,
       filename = file.path(figOutputPath, "results_fireAttrLandscape_boxplots.tiff"),
       width = 10, height = 12, dpi = 300)

```

### "Fire regime" plots
As in Cameron & Daniels 2020 (Fig. 9b,c): median and  SD of fire interval~severity, per forest type

```{r fireAttr_boxplots, cache = FALSE}
plotData <- summaryFireAttributes[vegTypeCN != "No veg.", 
                                  list(meanFreq_median = median(meanFreq),
                                       meanFreq_sd = sd(meanFreq),
                                       meanSevB_median = median(meanSevB),
                                       meanSevB_sd = sd(meanSevB)),
                                  by = .(scenario, vegTypeCN)]

plotData$scenario <- as.character(scenLabels[match(plotData$scenario, names(scenLabels))])

jitter_wd <- 100
jitter_hg <- 5
jitter_sd <- 456
plot48 <- ggplot(plotData, aes(y = meanFreq_median, x = meanSevB_median, colour = vegTypeCN)) +
  geom_point(size = 2, alpha = 0.5, 
             position = position_jitter(width = jitter_wd, height = jitter_hg, seed = jitter_sd)) +
  geom_errorbar(aes(ymin = meanFreq_median - meanFreq_sd, 
                    ymax = meanFreq_median + meanFreq_sd),
                alpha = 0.5, 
                position = position_jitter(width = jitter_wd, height = jitter_hg, seed = jitter_sd)) +
  geom_errorbarh(aes(xmin = meanSevB_median - meanSevB_sd, 
                     xmax = meanSevB_median + meanSevB_sd),
                 alpha = 0.5, 
                 position = position_jitter(width = jitter_wd, height = jitter_hg, seed = jitter_sd)) +
  scale_colour_manual(labels = vegTypeCNLabels[names(vegTypeCNLabels) %in% plotData$vegTypeCN],
                      values = vegTypeCNColours[names(vegTypeCNLabels) %in% plotData$vegTypeCN]) +
  theme_pubr(base_size = 14, legend = "bottom") +
  theme(legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.background = element_blank()) +
  labs(x = "Mean fire severity\n(biomass lost, ton/ha)",
       y = "Mean fire interval (years)") +
  facet_wrap(~ scenario, labeller = label_parsed)

```

```{r plot&savePlots16, echo = FALSE}
ggsave(plot = plot48, filename = file.path(figOutputPath, "results_fireRegime_crossPlot.tiff"),
       width = 8, height = 6)
```


### Fire interval comparisons  with observed data
Non-forest forest type removed, only pixel/plots with fire evidence
Note that `summaryFireAttributes`  has pixels with fire and without fires. So pixels without fires need to be removed
Also, in the observed data mean/median fire intervals were not calculated for plots that had one fire event only. So pixels with a single fire event are also removed
```{r simVsObsFires, cache = FALSE}
## TODO: use median FI everywhere. obs median already changed
## allPixelBurnData only has burnt pixels, use it to filter summaryFireAttributes
pixWFires <- unique(allPixelBurnData[noFires > 1, .(scenario, rep, pixelIndex)])

## mean fire interval per forest type - to compare with camerons fire intervals.
plotData <- summaryFireAttributes[pixWFires, on = .(scenario, rep, pixelIndex), nomatch = 0]
plotData <- plotData[vegTypeCN %in% ageDataCN$Cover.dendro, 
                     .(scenario, rep, pixelIndex, meanFreq, vegTypeCN)] 
plotData2 <- copy(plotData)
plotData2[, vegTypeCN := "landscape"]
plotData <- rbind(plotData, plotData2)

plotData2 <- unique(ageDataCN[firePresAbs > 0, .(Cover.dendro, median.FI, Patch.ID)])
plotData3 <- copy(plotData2)
plotData3[, Cover.dendro := "landscape"]
plotData2 <- rbind(plotData2, plotData3)

setnames(plotData2, "Cover.dendro", "vegTypeCN")

plot39 <- simObsDistsPlot(simData = plotData, x = "vegTypeCN", ySim = "meanFreq", 
                          colSim = "scenario",
                          obsData = plotData2, yObs = "median.FI", xlabels = vegTypeCNLabels,
                          colValues = scenColours, colLabels = scenLabels, x.text.angle = 45,
                          showMeans = FALSE,
                          titleLab = "Mean fire interval", subtitleLab = "by forest type",
                          yLab = "Fire interval")
plot39 <- plot39 + 
  geom_point(data = plotData2[vegTypeCN %in% c("broadleaf", "PIEN")],   ## these only have one point
             aes(x = vegTypeCN, y = median.FI, colour = "observed"),
             position = position_dodge(width = 0.9), show.legend = FALSE) 
```

```{r plot&savePlots16, echo = FALSE}
ggsave(plot = plot39, filename = file.path(figOutputPath, "results_meanFireIntSimVsObs.tiff"),
       width = 10, height = 8)
```


### Mean absolute deviation simulated fire intervals with respect to observed fire intervals for a given stand type
Non-forest forest type removed (not present in observed data), only pixel/plots with fire evidence
Note that `summaryFireAttributes`  has pixels with fire evidence -- fire intervals of 0 correspond to pixels that only had one fire in the first year of the analysed period.
```{r simVsObsFires2, cache = FALSE}
## TODO: compare medians, not mean frequencies (obs median already changed)

## mean age differences
## calculate avg weighted ages across observed stands first
## then the absolute difference of each stand to the observed average (per veg type) across reps
## allPixelBurnData only has burnt pixels, use it to filter summaryFireAttributes
pixWFires <- unique(allPixelBurnData[noFires > 1, .(scenario, rep, pixelIndex)])
## mean fire interval per forest type - to compare with camerons fire intervals.
plotData <- summaryFireAttributes[vegTypeCN != "No veg."][pixWFires, 
                                                          on = .(scenario, rep, pixelIndex), nomatch = 0]

plotData2 <- copy(plotData)
plotData2[, vegTypeCN := "landscape"]
plotData <- rbind(plotData, plotData2)

## vegType MADs first
plotData2 <- ageDataCN[firePresAbs > 0,]
plotData3 <- copy(plotData2)
plotData3[, Cover.dendro := "landscape"]
plotData2 <- rbind(plotData2, plotData3)
plotData2 <- plotData2[, list(avgMedian.FIObs = mean(median.FI, na.rm = TRUE)),
                       by = .(Cover.dendro)]

setnames(plotData2, "Cover.dendro", "vegTypeCN")
plotData <- plotData2[plotData, on = "vegTypeCN"]

if (nrow(plotData[is.na(avgMedian.FIObs) | is.na(meanFreq)])) {
  stop("NAs detected")
}

plotData2 <- plotData[, list(meanAbsDevSimObs = 1/.N * sum(abs(meanFreq - avgMedian.FIObs))),
                      by = .(scenario, rep, vegTypeCN)]

## boxplot differences
plot44 <- ggplot(plotData,
                 aes(x = vegTypeCN,
                     y = meanFreq - avgMedian.FIObs,
                     fill = scenario)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  geom_boxplot() +
  scale_fill_discrete(labels = scenLabels) +
  theme_pubr(base_size = 16, legend = "bottom", x.text.angle = 45) +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted")) +
  scale_x_discrete(labels = vegTypeCNLabels) +
  labs(title = "Avg. differences from observed fire intervals",
       y = expression("sim." - bar("obs.")), x = "")

## mean absolute differences
x_order <- names(vegTypeCNLabels[vegTypeCNLabels != "No forest"])
plot44.2 <- MADPlot(plotData2, x = "vegTypeCN", y = "meanAbsDevSimObs",
                    colour = "scenario", colValues = scenColours, colLabels = scenLabels,
                    labllr, xlabels = vegTypeCNLabels, xorder = x_order,
                    x.text.angle = 45, titleLab = "Mean abs. deviation from observed median fire intervals", 
                    yLab = expression(bar(bgroup("|", "sim." - bar("obs."), "|"))))

```

```{r plot&savePlots18, echo = FALSE}
plot44
ggsave(plot = plot44 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanFIDiff.tiff"),
       width = 14, height = 7)
plot44.2
ggsave(plot = plot44.2 + theme(legend.position = "right"),
       filename = file.path(figOutputPath, "results_meanAbsFIDev.tiff"),
       width = 10, height = 5)

plotSave <- plot_grid(plot39 + theme(plot.title = element_blank(), plot.subtitle = element_blank(), 
                                     axis.title.x = element_blank(), legend.position = "right"),
                      plot44.2 + theme(legend.position = "right",
                                       plot.title = element_blank(),
                                       legend.direction = "vertical",
                                       legend.box = "vertical"),
                      ncol = 1, labels = "auto", label_size = 20, align = "v", axis = "b")


ggsave(plot = plotSave, filename = file.path(figOutputPath, "results_meanFISimVsObsTest_MAD_VegTypeCN.tiff"),
       width = 8, height = 8)
gc()
```


## FIRE ATTRIBUTES BY PYRODIVERSITY LEVEL
```{r fireAttriPyro, echo = FALSE}
## TODO: change to medians.
tempData <- allHVData[year == end(preSimList),
                      .(HVtype, HV_noPM, HV_PM, rep, repHV, vegType)]
tempData <- melt.data.table(tempData, measure.vars = c("HV_noPM", "HV_PM"),
                            variable.name = "scenario", value.name = "Volume")
tempData$scenario <- sub("HV_", "", tempData$scenario)
tempData <- tempData[HVtype == "fireHV", list(Volume = mean(Volume, na.rm = TRUE)),
                     by = .(rep, vegType, scenario)]
setnames(tempData, "vegType", "vegTypeCN")

## add only landscape level HV sizes 
plotData <- tempData[vegTypeCN == "landscape", .(scenario, rep, Volume)][summaryFireAttributes, on = .(scenario, rep)]
plotData <- melt(plotData, id.vars = c("scenario", "rep", "Volume", "pixelIndex", "vegTypeCN"))
plotData[variable %in% c("meanPatchS", "meanSevB"), value := log(value + 0.1)]

plot47 <- ggplot(plotData[variable != "meanSev"], aes(x = as.factor(round(log(Volume), 3)), 
                                                      y = value, 
                                                      fill = as.factor(round(log(Volume), 3)))) +
  geom_violin() + 
  theme_pubr(base_size = 16, legend = "bottom") +
  theme(legend.title = element_blank(), panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
        strip.placement = "outside", strip.background = element_blank(), strip.text = element_text(size = 16)) +
  labs(y = "", x = "pyrodiversity") +
  facet_grid(variable ~ scenario, scales = "free", switch = "y",
             labeller = labeller(scenario = scenLabels,
                                 variable = c(meanFreq = "Mean fire interval",
                                              meanSevB = "Mean severity",
                                              meanPatchS = "Mean patch size")))

## relationship  between pyrodiversity and fire attributes -----------------
## join HV sizes with fire attributes
plotData <- allHVData[HVtype == "fireHV",
                      .(HV_noPM, HV_PM, rep, repHV, vegType)]
plotData[, vegType := factor(vegType, levels = names(vegTypeCNLabels))]
plotData <- melt.data.table(plotData, measure.vars = c("HV_noPM", "HV_PM"),
                            variable.name = "scenario", value.name = "Volume")
plotData[, scenario := sub("HV_", "", scenario)]
## center and scale volume as in model
plotData[, Volume := log(Volume),
         by = .(scenario, vegType)]

plotData2 <- plotData[vegType == "landscape"]
plotData2 <- summaryFireAttributes[plotData2, on = c("scenario", "rep"),
                                   allow.cartesian = TRUE]
plotData2[,vegTypeCN := NULL]

plotData <- plotData[vegType != "landscape"]
plotData <- summaryFireAttributes[plotData, on = c("vegTypeCN==vegType", "scenario", "rep"),
                                  allow.cartesian = TRUE]
setnames(plotData, "vegTypeCN", "vegType")
plotData <- rbind(plotData, plotData2)

plotData <- melt.data.table(plotData, measure.vars = c("meanFreq", "meanSevB", "meanPatchS"),
                            variable.name = "fireAttr", value.name = "value")
## calculate summary stats
plotData <- plotData[, as.list(summary(value)), by = .(scenario, rep, repHV, Volume, vegType, fireAttr)]


fireAttrPyroPlotFun <- function(plotData) {
  ggplot(plotData,
         aes(x = log(Volume+1), y = log(Mean + 1),
             colour = vegType, linetype = scenario,
             shape = scenario)) +
    geom_point(size = 2) +
    stat_smooth(method = "gam", formula = y ~ s(x, k = 3), se = FALSE) +
    geom_hline(aes(yintercept = -Inf)) + ## to force axes lines.
    geom_vline(aes(xintercept = -Inf)) +
    coord_cartesian(clip = "off") +
    scale_x_continuous(label = scales::label_number(accuracy = 0.01)) +
    scale_shape_discrete(labels = scenLabels, name = "") +
    scale_linetype_manual(values = scenLinetype, labels = scenLabels) +
    scale_colour_manual(labels = vegTypeCNLabels, values = vegTypeCNColours, name = "") +
    theme_pubr(base_size = 12, margin = TRUE) +
    theme(legend.box = "horizontal", strip.text.y = element_text(size = 12),
          strip.background = element_blank(), strip.placement = "outside",
          panel.grid.major.y = element_line(colour = "grey", size = 11/22, linetype = "dotted"),
          panel.spacing.x = unit(1.5, "line")) +
    labs(x = "Pyrodiversity\n(log-hypervolume size)", y = "", title = "") +
    facet_grid(fireAttr ~ vegType,
               scales = "free", switch = "y",
               labeller = labeller(vegType = vegTypeCNLabels,
                                   fireAttr = c("meanPatchS" = "Mean patch size\n(no. pixels)",
                                                "meanFreq" = "Mean fire interval",
                                                "meanSevB" = "Mean fire severity\n(biomass lost, ton/ha)")))
}

fireAttrPyroLandscapePlot <- fireAttrPyroPlotFun(plotData[vegType == "landscape"])
fireAttrPyroVegTypesPlot <- fireAttrPyroPlotFun(plotData[vegType != "landscape"])

plotSave <- ggarrange(fireAttrPyroVegTypesPlot,
                      fireAttrPyroLandscapePlot + labs(y = "", title = "") + theme(strip.text.y = element_blank()),
                      ncol = 2, nrow = 1, widths = c(1, 0.2), labels = "auto", label.y = 0.95,
                      common.legend = TRUE, legend = "bottom")
ggsave(plot = plotSave, filename = file.path(figOutputPath, "fireAttrVsPyro.tiff"),
       width = 20, height = 7)
```

```{r plot&savePlots23, echo = FALSE}
plot47
ggsave(plot = plot47, filename = file.path(figOutputPath, "results_fireAttrLandscapePyrodiversity.tiff"),
       width = 14, height = 8)
```

## SPECIES COMPOSITION BY VEGETATION TYPE
Only on the sampled years; only B and averg. weighted age
```{r plotsByVegTypeCN, cache = FALSE}
plotData <- allPixelCDMntEnd[, list(vegTypeCN = vegTypeCN,
                                    noFires = noFires,
                                    B = B,
                                    avgAgeBySppSim = as.numeric(sum(age * (B/100), na.rm = TRUE) /
                                                                  sum((B/100), na.rm = TRUE))),
                             by = .(scenario, rep, year, pixelIndex, speciesCode)]
plotData[is.nan(avgAgeBySppSim), avgAgeBySppSim := 0]
## sum B per spp
plotData[, B := sum(B), by = .(scenario, rep, year, pixelIndex, speciesCode)]
plotData <- unique(plotData)
## sum across pixels per vegType
plotData[, BiomassBySpecies := sum(B), 
         by = .(scenario, rep, year, vegTypeCN, speciesCode)]
plotData$scenario <- as.character(scenLabels[match(plotData$scenario, names(scenLabels))])

## no. pixels with a veg type, per scenario/rep/year, then average for plot
plotData[noFires > 0, noPixels := length(pixelIndex), by = .(scenario, rep, year, vegTypeCN)]
plotData[noFires > 0, noPixels := round(mean(noPixels)), by = .(scenario, vegTypeCN)]

## SPECIES BIOMASS
## cross pixel sums
## just mean across reps and scaled from 0-1
plot7 <- sppCompositionPlots(data = plotData[noFires > 0],
                             x = "vegTypeCN", y = "BiomassBySpecies",
                             fill = "speciesCode", fillValues = speciesColours, 
                             fillLabels = speciesLabels, xFacet = "scenario", 
                             xlabels = vegTypeCNLabels, labllr = labeller(scenario = label_parsed),
                             titleLab = "Species biomass", yLab = "Proportion of biomass")
plot7 <- plot7 + 
  geom_text(data = unique(plotData[noFires > 0, .(scenario, vegTypeCN, noPixels)]),
            aes(x = vegTypeCN, y = 1.05, label = noPixels))

## with mean and SD
plot7.2 <- sppCompositionPlots(data = plotData[noFires > 0],
                               x = "vegTypeCN", y = "BiomassBySpecies",
                               fill = "speciesCode", fillValues = speciesColours, 
                               fillLabels = speciesLabels, xFacet = "scenario", 
                               errorBar = TRUE,
                               xlabels = vegTypeCNLabels, labllr = labeller(scenario = label_parsed),
                               titleLab = "Species biomass", yLab = "Total biomass")

## pixel averages
## just mean across reps and scaled from 0-1
plot7.3 <- sppCompositionPlots(data = plotData[noFires > 0],
                               x = "vegTypeCN", y = "B",
                               fill = "speciesCode", fillValues = speciesColours, 
                               fillLabels = speciesLabels, xFacet = "scenario", 
                               xlabels = vegTypeCNLabels, labllr = labeller(scenario = label_parsed),
                               titleLab = "Species biomass", yLab = "Relative biomass",
                               subtitleLab = "by species, within pixels")

## with mean and SD
plot7.4 <- sppCompositionPlots(data = plotData[noFires > 0],
                               x = "vegTypeCN", y = "B", errorBar = TRUE,
                               fill = "speciesCode", fillValues = speciesColours, 
                               fillLabels = speciesLabels, xFacet = "scenario", 
                               xlabels = vegTypeCNLabels, labllr = labeller(scenario = label_parsed),
                               titleLab = "Species biomass", yLab = "Total biomass",
                               subtitleLab = "by species, within pixels")

## SPECIES BIOMASS-WEIGHTED AGE
## with mean and SD
plot8 <- sppCompositionPlots(data = plotData[noFires > 0],
                               x = "vegTypeCN", y = "avgAgeBySppSim", errorBar = TRUE,
                               fill = "speciesCode", fillValues = speciesColours, 
                               fillLabels = speciesLabels, xFacet = "scenario", 
                               xlabels = vegTypeCNLabels, labllr = labeller(scenario = label_parsed),
                               titleLab = "Mean weighted age", yLab = "Biomass-weighted age",
                               subtitleLab = "by species, within pixels")

```

```{r plot&savePlots4, echo = FALSE}
plot7
ggsave(plot = plot7, filename = file.path(figOutputPath, "results_landscapeB_vegTypeCN.tiff"),
       width = 14, height = 7)

plot7.2
ggsave(plot = plot7.2, filename = file.path(figOutputPath, "results_landscapeB_vegTypeCN_wSD.tiff"),
       width = 14, height = 7)

plot7.3
ggsave(plot = plot7.3, filename = file.path(figOutputPath, "results_pixelB_vegTypeCN.tiff"),
       width = 14, height = 7)

plot7.4
ggsave(plot = plot7.4, filename = file.path(figOutputPath, "results_pixelB_vegTypeCN_wSD.tiff"),
       width = 14, height = 7)

plot8
ggsave(plot = plot8, filename = file.path(figOutputPath, "results_pixelAge_vegTypeCN_wSD.tiff"),
       width = 14, height = 7)

```


