---
title: "Landscapes In Motion - mixed severity fire landscape model in Alberta Foothills"
author: "CeresBarros"
date: "18/12/2020"
output: html_document
---

#### Requirements
Before proceeding, please make sure you have:
* at least [R v4.0.3](https://cran.r-project.org/bin/windows/base/) and [Rtools40](https://cran.r-project.org/bin/windows/Rtools/) installed (make sure you follow ALL installation instructions for Rtools).
* the R package `devtools`

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "~/GitHub/LandscapesInMotion/")
knitr::opts_chunk$set(echo = FALSE, cache = 2, warning = FALSE)

devtools::install_github("PredictiveEcology/reproducible@development", dependencies = TRUE)
devtools::install_github("achubaty/amc@development", dependencies = TRUE)
devtools::install_github("PredictiveEcology/pemisc@development", dependencies = TRUE, upgrade = TRUE)
devtools::install_github("PredictiveEcology/map@development", dependencies = TRUE, upgrade = TRUE)
devtools::install_github("CeresBarros/LandR@development", dependencies = TRUE, upgrade = TRUE)
devtools::install_github("ianmseddy/LandR.CS", dependencies = TRUE, upgrade = TRUE)
devtools::install_github("PredictiveEcology/quickPlot@development", dependencies = TRUE, upgrade = TRUE)
devtools::install_github("PredictiveEcology/SpaDES.tools@development", dependencies = TRUE, upgrade = TRUE)
devtools::install_github("PredictiveEcology/SpaDES.core@development", dependencies = TRUE, upgrade = TRUE)
devtools::install_github("PredictiveEcology/SpaDES.experiment@development", dependencies = TRUE, upgrade = TRUE)

library(SpaDES)
library(SpaDES.experiment)
library(LandR)

options("reproducible.useNewDigestAlgorithm" = TRUE)
options("spades.moduleCodeChecks" = FALSE)
options("reproducible.useCache" = TRUE)
options("reproducible.inputPaths" = normPath("R/SpaDES/inputs"))  ## store everything in data/ so that there are no duplicated files across modules
options("reproducible.destinationPath" = normPath("R/SpaDES/inputs"))
options("reproducible.useGDAL" = FALSE)

source("R/R_tools/Useful_functions.R")
```

## Simulation setup
Setting up the simulation requires preparing data (e.g. study area, species abundance layers, fire data...) and supplying parameters to the different SpaDES modules used in the simulation. This is done by running a series of Rscripts, which are explained bellow.

### 1. Choose a name for the run, folders and decide the caching mode
`runName` affects ...?
`dirName` will be used to store simulation cache and outputs, broken into different subfolders (e.g. `preSim`, `speciesLayers`) for different simulation components.

```{r simulationSetup1, echo=FALSE, cache=2}
## Set up simulation name  ---------------------------
runName <- "test"

## paths define simulation paths
dirName <- "test"
simPaths <- list(cachePath = file.path("R/SpaDES/cache", dirName)
                 , modulePath = file.path("R/SpaDES/m")
                 , inputPath = file.path("R/SpaDES/inputs")
                 , outputPath = file.path("R/SpaDES/outputs", dirName))

eventCaching <- c(".inputObjects", "init")
useParallel <- FALSE

```

### 2. Prepare simulation inputs
These include the study area polygon shapefiles, species data and fire weather data
Species biomass layers are obtained first and QA "manually". Some species may need to be excluded at this point.
Cache and output files are save in `dirName/speciesLayers` and `dirName/fireWeather` folders inside the `cache/` and `outputs` folders.

```{r simulationSetup2, echo=FALSE, cache=2}
## Get necessary objects -----------------------
source("R/SpaDES/1_simObjects.R")

## Run Biomass_speciesData to get species layers
source("R/SpaDES/2_speciesLayers.R")

## maybe drop some species - Black spruce, and Ponderosa pine have v. few occurrences
plot(simOutSpeciesLayers$speciesLayers)
keepSpp <- sapply(unstack(simOutSpeciesLayers$speciesLayers), FUN = function(ras) {
  propPres <- sum(ras[] > 0, na.rm = TRUE)/sum(!is.na(simOutSpeciesLayers$speciesLayers[[2]][]))
  propPres > 0.05  ## species need to be in at least 5% of the landscaoe
})

keepSpp <- names(simOutSpeciesLayers$speciesLayers)[keepSpp]
simOutSpeciesLayers$speciesLayers <- subset(simOutSpeciesLayers$speciesLayers, keepSpp)
sppEquivalencies_CA <- sppEquivalencies_CA[LIM %in% keepSpp]
sppColorVect <- sppColorVect[keepSpp]
plot(simOutSpeciesLayers$speciesLayers)

## Prepare fire weather tables --------------------
source("R/SpaDES/3_fireWeather.R")
```

After species data and fire weather data are in place, we run all data prep. modules which estimate any necessary parameters and prepare input objects for the actual simulation. This is a pre-simulation run - all cache and output files are saved under `dirName/preSim` inside the `cache/` and `outputs` folders, respectively.
At this point we need to define a few parameters related to the simulation length, start year and frequency of fire, the forest succession time step and whether mixed stands receive a leading-type classification.

Other module-specific parameters are defined in the `4_preSimulation.R` script and documented in each module's `.Rmd` file and `.R` metadata section.

```{r simulationSetup3, echo=FALSE, cache=2}
## Run more data prep -----------------------------
# Biomass_borealDataPrep, LandR_speciesParameters, Biomass_core (just init and year 0) and Biomass_fuelsPFG
## to prepare objects for simulation and FireSense ignition/fire frquency fits
## Define simulation params
simTimes <- list(start = 2011L, end = 2111L)
fireInitialTime <- 5L
fireTimestep <- if (sum(grepl("oneFire", runName))) 100000L else 1L
successionTimestep <- 10L
vegLeadingProportion <- 0 # indicates what proportion the stand must be in one species group for it to be leading.
# If all are below this, then it is a "mixed" stand (e.g. 0 will never classify by leading type)
source("R/SpaDES/4_preSimulation.R")
```

### 3. Setup and run simulation
Choose whether to activate plotting, setup the simulation with the necessary parameters and objects obtained above and run the simulation.
Make sure you adapt the script `5_simulationSetup.R` to suit your needs (e.g. module list, objects to save, ...)

```{r simulationSetup3, echo=FALSE, cache=2}
## if NA nothing will be plotted. Choose 1 for plotting to start at year 1.
plotInitialTime <- NA

## Make actuaL simulation module list, parameters objects, objects and outputs according to run
## name and the parameters above
source("R/SpaDES/5_simulationSetup.R")

graphics.off()
simInitOut <- simInitAndSpades(times = simTimes
                               , params = simParams
                               , modules = simModulesNoPM
                               , objects = simObjects
                               , paths = simPaths
                               , outputs = outputs
                               , debug = TRUE
                               , .plotInitialTime = plotInitialTime
)

## you may choose to save simulation outputs
# saveSimList(simOut, file.path(simPaths$outputPath, paste0("simList_", runName, ".qs")))
# if (!is.na(plotInitialTime))
#   dev.print(tiff, file.path(simPaths$outputPath, paste0("simPlots_", runName, ".tiff")),
#             res = 300, units = "in")
```
