---
title: "Landscapes In Motion - Barros et al. publication runs."
author: "Ceres Barros"
params:
  orig_date: "Created: Dec. 18,  2020"
  update_date: !r paste("Last modified on:", format(Sys.time(), '%d %B, %Y'))
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = "~/LandscapesInMotion/")
knitr::opts_chunk$set(eval = FALSE, echo = TRUE, cache = 2, warning = FALSE)
```

`r params$orig_date`

`r params$update_date`

## Requirements

Before proceeding, please make sure that:

* You are running [R v4.1.3](https://cran.r-project.org/bin/windows/base/) -- later versions will not work.

* [Rtools40](https://cran.r-project.org/bin/windows/Rtools/) installed (make sure you follow all installation instructions for Rtools).

* the R package `devtools`

```{r pkgInstall}
installPkgs <- FALSE
pkgSnapshotFile <- "R/SpaDES/pkgSnapshot.txt"  ## only used if isTRUE(installPkgs)

## run the following script manually the first time, then you can source()
source("R/SpaDES/0_packages.R")

library(Require)
Require(c("raster",
          "SpaDES",
          "data.table",
          "ToolsCB",
          "SpaDES.experiment",
          "LandR (==1.0.7.9026)",
          "reproducible",
          "future"
), upgrade = FALSE, install = FALSE)

## to prevent overflow to threads that aren't actually available
data.table::setDTthreads(threads = 1)
```

## Simulation setup
Setting up the simulation requires preparing data (e.g. study area, species abundance layers, fire data...) and supplying parameters to the different SpaDES modules used in the simulation. This is done by running a series of Rscripts, which are explained bellow.

### 1. Choose a name for the run, folders, decide the caching mode and set `options()`

*   `runName` is a vector of simulation names -- there will be two, one with no 
    partial-mortality after fire("noPM") and another with partial-mortality after fire ("PM")

*   `simDirName` is the name of the subfolder in `cache/` and `outputs/` where
    subfolders (e.g. `preSim`, `speciesLayers`, `noPM` , `PM`, etc.) will be created to store different 
    simulation outputs and caches.

```{r simulationSetup1}
## Set up simulation names  ---------------------------
runName <- c("noPM", "PM")

eventCaching <- c(".inputObjects", "init")
useParallel <- FALSE

## define simulation paths
simDirName <- "mar2022Runs"

simPaths <- list(cachePath = file.path("R/SpaDES/cache", simDirName)
                 , modulePath = file.path("R/SpaDES/m")
                 , inputPath = file.path("R/SpaDES/inputs")
                 , outputPath = file.path("R/SpaDES/outputs", simDirName))

options("reproducible.useNewDigestAlgorithm" = 2,
        "spades.moduleCodeChecks" = FALSE,
        "reproducible.useCache" = TRUE,
        "reproducible.inputPaths" = simPaths$inputPath,
        "reproducible.destinationPath" = simPaths$inputPath,
        "reproducible.useGDAL" = FALSE,
        "reproducible.cacheSaveFormat" = "qs",
        "reproducible.useMemoise" = TRUE,
        "mc.cores" = 1,
        "spades.useRequire" = FALSE,
        "reproducible.useTerra" = FALSE,
        "reproducible.rasterRead" = "raster::raster")

```

### 2. Prepare simulation inputs

#### 2.1. Study area, species cover layers and fire weather data

These include the study area polygon shapefiles, species data and fire weather data
Species biomass layers are obtained first and QA "manually". Some species may need to be excluded at this point.
Cache and output files are save in `dirName/speciesLayers` and `dirName/fireWeather` folders inside the `cache/` and `outputs` folders.

```{r simulationSetup2}
## Get necessary objects -----------------------
source("R/SpaDES/1_simObjects.R")

## Run Biomass_speciesData to get species layers
source("R/SpaDES/2_speciesLayers.R")

## drop some species - Black spruce, and Ponderosa pine have v. few occurrences
plot(simOutSpeciesLayers$speciesLayers)
keepSpp <- sapply(unstack(simOutSpeciesLayers$speciesLayers), FUN = function(ras) {
  propPres <- sum(ras[] > 0, na.rm = TRUE)/sum(!is.na(ras[]))
  propPres > 0.05  ## species need to be in at least 5% of the landscape
})

keepSpp <- names(simOutSpeciesLayers$speciesLayers)[keepSpp]
speciesLayers <- subset(simOutSpeciesLayers$speciesLayers, keepSpp)
sppEquivalencies_CA <- sppEquivalencies_CA[get(sppEquivCol) %in% keepSpp]
sppColorVect <- simOutSpeciesLayers$sppColorVect[keepSpp]
sppNameVector <- intersect(simOutSpeciesLayers$sppNameVector, names(sppColorVect))
raster::plot(speciesLayers)

## Prepare fire weather tables --------------------
source("R/SpaDES/3_fireWeather.R")
```

#### 2.2. Run data preparation and calibration modules

After species data and fire weather data are in place, we run all data prep. modules which estimate any necessary parameters and prepare input objects for the actual simulation. This is a pre-simulation run - all cache and output files are saved under `dirName/preSim` inside the `cache/` and `outputs` folders, respectively.
At this point we need to define a few parameters related to the simulation length, start year and frequency of fire, the forest succession time step and whether mixed stands receive a leading-type classification.

Other module-specific parameters are defined in the `4_preSimulation.R` script and documented in each module's `.Rmd` file and `.R` metadata section.

```{r simulationSetup3}
## Run more data prep -----------------------------
## Biomass_borealDataPrep, LandR_speciesParameters, Biomass_core (just init and year 0) and Biomass_fuelsPFG
## to prepare objects for simulation and FireSense ignition/fire frequency fits
## Define simulation params
simTimes <- list(start = 2011L, end = 4011L)   ## capture several cycles of Doug-fir dynamics
vegLeadingProportion <- 0 # indicates what proportion the stand must be in one species group for it to be leading.
## If all are below this, then it is a "mixed" stand
fireInitialTime <- simTimes$start + 5L
fireTimestep <- if (sum(grepl("oneFire", runName))) 100000L else 1L
successionTimestep <- 10L

source("R/SpaDES/4_preSimulation.R")

LIM_preSimulation <- loadSimList(file.path(simPaths$outputPath, "LIM_preSimulation.qs"))

## re-initialize simulation modules (overcoming seed problem)
reproducible::clearCache(file.path(simPaths$cachePath, "noPM"), ask = FALSE)
reproducible::clearCache(file.path(simPaths$cachePath, "PM"), ask = FALSE)
source("R/SpaDES/4_preSimulationPART2.R")


simListFiles <- list.files(simPaths$outputPath, pattern = "LIM_simInit_", full.names = TRUE, recursive = TRUE)
simListFiles <- grep("PART2.qs$", simListFiles, value = TRUE)
names(simListFiles) <- sub(paste0(simPaths$outputPath, "/(.*)/.*"), "\\1", simListFiles)
LIM_simInitList <- lapply(simListFiles, loadSimList)

## clean unnecessary simLists
rm(simOutSpeciesLayers, simOutFireWeather);
gc(reset = TRUE)

LIM_simInitList$noPM$._randomSeed <- NULL
LIM_simInitList$PM$._randomSeed <- NULL
```

### 3. Setup and run simulation
Choose whether to activate plotting, setup the simulation with the necessary parameters and objects obtained above and run the simulation.
Make sure you adapt the script `5_simulationSetup.R` to suit your needs (e.g. module list, objects to save, ...)

```{r simulationRuns}
## using experiment:
## multicore no longer available from RStudio
# plan("multicore", workers = 2)   
plan("sequential")


## PARTIAL MORTALITY RUNS
clearSimEnv <- TRUE
simExperimentOut <- experiment2(
  PM = LIM_simInitList[["PM"]],
  clearSimEnv = clearSimEnv,
  replicates = 5,
  useCache = FALSE,
  meanStaggerIntervalInSecs = 60)
future:::ClusterRegistry("stop")

## save simLists object.
if (isFALSE(clearSimEnv)) {  ## we have a caching bug so need to clear the env before saving
  for (i in seq_along(simExperimentOut)) {
    rm(list = ls(simExperimentOut[[i]], all.names = TRUE), envir = envir(s))
  }
}
qs::qsave(simExperimentOut, file.path(outputPath(LIM_simInitList[["PM"]]), paste0("LIM_simLists_PM", ".qs")))

rm(simExperimentOut); gc(reset = TRUE)


## NO PARTIAL MORTALITY RUNS
simExperimentOut <- experiment2(noPM = LIM_simInitList[["noPM"]],
                                clearSimEnv = clearSimEnv,
                                replicates = 5,
                                useCache = FALSE,
                                meanStaggerIntervalInSecs = 60)
future:::ClusterRegistry("stop")

## save simLists object.
if (isFALSE(clearSimEnv)) {  ## we have a caching bug so need to clear the env before saving
  for (i in seq_along(simExperimentOut)) {
    rm(list = ls(simExperimentOut[[i]], all.names = TRUE), envir = envir(s))
  }
}
qs::qsave(simExperimentOut, file.path(outputPath(LIM_simInitList[["noPM"]]), paste0("LIM_simLists_noPM", ".qs")))

```
