---
title: "Dave Andison's fire data preliminary analyses"
author: "Ceres Barros"
date: "March 28, 2018"
output: html_document
---

```{r, include = FALSE}
knitr::opts_knit$set(root.dir = getwd())
library(factoextra)
library(reshape2)

```


```{r setup, echo=FALSE}
## source dataprep:
source("R/DAfires_expAnalyses_dataPrep.R")

## subset variables of interest:
vars <- which(names(AB1_vegFireEvents.mdt) %in% 
                c(grep("MOIS|DENS|HEIG|TPR|ORIG|NFL|NAT_N|STRUC", 
                       names(AB1_vegFireEvents.mdt), value = TRUE),
                  grep("^SP", names(AB1_vegFireEvents.mdt), value = TRUE),
                  grep("^USP", names(AB1_vegFireEvents.mdt), value = TRUE),
                  names(AB1_fireEvents), "SEV_CONT",
                  "WATER_TY"))
AB1_vegFireEvents.mdt <- AB1_vegFireEvents.mdt[, vars, with = FALSE]

```


## COMMUNITY COMPOSITION/STRUCTURE PCA
PCA of species percentage cover and height. `^SP` stands for canopy species in decreasing order of dominance, and `^USP` for understory species (also in decreasing order of dominance).
Across all fire event patch types. Blue arrow is SEV_CONT, fitted to the ordination *a posteriori*, using `vegan::env.fit`.
Severity is higher in "plots" dominated by Black spruce (Sb), Lodgepole pine (Pl) and Tamarack (Lt). 
It seems that canopy and understory levels are highly correlated within species.
```{r, echo = FALSE}
pca.vars <- grep("SP|HEIG|SEV_CONT", names(AB1_vegFireEvents.mdt), value = TRUE)
temp <- na.omit(AB1_vegFireEvents.mdt[, pca.vars, with = FALSE])

sp.vars <- grep("SP|HEIG", names(AB1_vegFireEvents.mdt), value = TRUE)
vegCompPCA <- prcomp(temp[, sp.vars, with = FALSE], scale = TRUE)  ## no need for rescaling as variables are all on the sale scale
env.fit <- vegan::envfit(vegCompPCA, env = temp$SEV_CONT)

# dev()
biplot(vegCompPCA)
vegan:::plot.envfit(env.fit)

```

PCA with canopy and understory levels collapsed for tree species (summed and rescaled to 0-1 - maybe not the best way)
Results are similar.
```{r}
pca.vars <- grep("SP|HEIG|SEV_CONT", names(AB1_vegFireEvents.mdt), value = TRUE)
temp <- na.omit(AB1_vegFireEvents.mdt[, pca.vars, with = FALSE])

sp.vars <- grep("SP", names(AB1_vegFireEvents.mdt), value = TRUE)
sp.names <- unique(sub(".*_", "", sp.vars)) 

for(x in sp.names) {
  ## sum canopy and understory percentages per species
  temp[, paste(x):= rowSums(.SD), .SDcols = grep(x, names(temp), value = TRUE)]
}
## and rescale between 0-1
temp[, lapply(.SD, rescale01), .SDcols = sp.names]

## run PCA
pca.vars <- c(sp.names, grep("HEIG|SEV_CONT", names(temp), value = TRUE))
temp <- temp[, pca.vars, with = FALSE]

vegCompPCA <- prcomp(temp[, -"SEV_CONT", with = FALSE], scale = TRUE)
env.fit <- vegan::envfit(vegCompPCA, env = temp$SEV_CONT)

fviz_screeplot(vegCompPCA)
fviz_pca(vegCompPCA, col.var = "red")

biplot(vegCompPCA)
vegan:::plot.envfit(env.fit)

```

Add moisture - can't see much
```{r}
pca.vars <- grep("SP|HEIG|SEV_CONT|MOIST", names(AB1_vegFireEvents.mdt), value = TRUE)
temp <- na.omit(AB1_vegFireEvents.mdt[, pca.vars, with = FALSE])

sp.vars <- grep("SP", names(AB1_vegFireEvents.mdt), value = TRUE)
sp.names <- unique(sub(".*_", "", sp.vars)) 

for(x in sp.names) {
  ## sum canopy and understory percentages per species
  temp[, paste(x):= rowSums(.SD), .SDcols = grep(x, names(temp), value = TRUE)]
}
## and rescale between 0-1
temp[, lapply(.SD, rescale01), .SDcols = sp.names]

## run PCA
pca.vars <- c(sp.names, grep("HEIG|SEV_CONT|MOIST", names(temp), value = TRUE))
temp <- temp[, pca.vars, with = FALSE]

vegCompPCA <- prcomp(temp[, -c("SEV_CONT", "MOIST"), with = FALSE], scale = TRUE)
env.fit <- vegan::envfit(vegCompPCA, env = temp[, list(SEV_CONT, MOIST)])

fviz_screeplot(vegCompPCA)
fviz_pca(vegCompPCA, col.var = "red")

biplot(vegCompPCA)
vegan:::plot.envfit(env.fit)

```


## NOTES
I believe some of the outer matrix patches overlap with the disturbed patches in terms of vegetation polygons, because they often have similar distributions of vegetation attributes, whose frequencies are not being added up in the event perimeter frequencies.

## Pre-fire conditions in fire event patches

```{r canopy_patch, echo = FALSE}
dev()
sp.vars <- grep("SP|HEIG", names(AB1_vegFireEvents.mdt), value = TRUE)
plot.table <- melt(AB1_vegFireEvents.mdt,
                   measure.vars = sp.vars, variable.name = "SPP", value.name = "Cover")
ggplot(plot.table[grep("^SP", SPP),], aes(x = as.factor(PatchType), y = Cover, fill = SPP)) +
  geom_boxplot()
```

### understory species
Probably can't look at understory species by themselves as the data is mostly composed of 0s.
```{r undestory_patch, echo = FALSE}
sp.vars <- grep("SP|HEIG", names(AB1_vegFireEvents.mdt), value = TRUE)
plot.table <- melt(AB1_vegFireEvents.mdt,
                   measure.vars = sp.vars, variable.name = "SPP", value.name = "Cover")
ggplot(plot.table[grep("^USP", SPP),], aes(x = as.factor(PatchType), y = Cover, fill = SPP)) +
  geom_boxplot()

```


### Moisture regime
No noticeable diferences in either the canopy or understory moisture (UMOIS) regimes

```{r moisture_patch, echo = FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$MOIST),], aes(x = as.factor(PatchType), fill = MOIST)) +
  geom_histogram(stat = "count", position = "dodge") #+ facet_wrap(~ PatchType)

ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$UMOIS),], aes(x = as.factor(PatchType), fill = UMOIS)) +
  geom_histogram(stat = "count", position = "dodge") #+ facet_wrap(~ PatchType)

```

### Crown closure class
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of crown closure classes. Inner matrix remnants seem to have lower crown closure.

```{r crownclos_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$DENSI),], aes(x = as.factor(PatchType), fill = DENSI)) +
  geom_histogram(stat = "count", position = "dodge")

ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$UDENS),], aes(x = as.factor(PatchType), fill = UDENS)) +
  geom_histogram(stat = "count", position = "dodge")

```

### Vegetation Height

```{r crownclos_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$HEIGH),], aes(x = as.factor(PatchType), fill = HEIGH)) +
  geom_histogram(stat = "count", position = "dodge")

ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$UHEIG),], aes(x = as.factor(PatchType), fill = HEIGH)) +
  geom_histogram(stat = "count", position = "dodge")

```

### Timber productivity rating
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of timber porductivity classes. Inner matrix remnants seem to be a subsample of the other two.
```{r TPR_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$TPR),], aes(x = as.factor(PatchType), fill = TPR)) +
  geom_histogram(stat = "count", position = "dodge")
```

### Non forest vegetated land
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of non forested land classes. Inner matrix remnants seem to be a subsample of the other two.

```{r NFL_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$NFL),], aes(x = as.factor(PatchType), fill = NFL)) +
  geom_histogram(stat = "count", position = "dodge")
```

### Natural-non vegetated land
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of class frequencies, with quite a few flooded areas (NWF) and rivers (NWR). Inner matix remnants also have several river patches, but no flooded areas. They also seem to have a higher relative proportion of sandy soil (NMS)

```{r NATN_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$NAT_N),], aes(x = as.factor(PatchType), fill = NAT_N)) +
  geom_histogram(stat = "count", position = "dodge")
```

### Forest age - Origin
Disturbed patches and outer matrix remnants have identical age distributions (which are not being added up at all). Inner matrix patches seem to be a very biased subsample.

```{r orig_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$ORIGI),], aes(x = as.factor(PatchType), y = ORIGI)) +
  geom_boxplot()
```


-------------------

## Pre-fire conditions in fire severity classes
### Canopy species
```{r canopy_patch, echo = FALSE}
dev()
sp.vars <- grep("SP|HEIG", names(AB1_vegFireEvents.mdt), value = TRUE)
plot.table <- melt(AB1_vegFireEvents.mdt,
                   measure.vars = sp.vars, variable.name = "SPP", value.name = "Cover")
ggplot(plot.table[grep("^SP", SPP),], aes(x = as.factor(SEV_CONT), y = Cover, fill = SPP)) +
  geom_boxplot()
```

### understory species
Probably can't look at understory species by themselves as the data is mostly composed of 0s.
```{r undestory_patch, echo = FALSE}
sp.vars <- grep("SP|HEIG", names(AB1_vegFireEvents.mdt), value = TRUE)
plot.table <- melt(AB1_vegFireEvents.mdt,
                   measure.vars = sp.vars, variable.name = "SPP", value.name = "Cover")
ggplot(plot.table[grep("^USP", SPP),], aes(x = as.factor(SEV_CONT), y = Cover, fill = SPP)) +
  geom_boxplot()

```


### Moisture regime
No noticeable diferences in either the canopy or understory moisture (UMOIS) regimes

```{r moisture_patch, echo = FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$MOIST),], aes(x = as.factor(SEV_CONT), fill = MOIST)) +
  geom_histogram(stat = "count", position = "dodge") #+ facet_wrap(~ SEV_CONT)

ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$UMOIS),], aes(x = as.factor(SEV_CONT), fill = UMOIS)) +
  geom_histogram(stat = "count", position = "dodge") #+ facet_wrap(~ SEV_CONT)

```

### Crown closure class
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of crown closure classes. Inner matrix remnants seem to have lower crown closure.

```{r crownclos_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$DENSI),], aes(x = as.factor(SEV_CONT), fill = DENSI)) +
  geom_histogram(stat = "count", position = "dodge")

ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$UDENS),], aes(x = as.factor(SEV_CONT), fill = UDENS)) +
  geom_histogram(stat = "count", position = "dodge")

```

### Vegetation Height

```{r crownclos_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$HEIGH),], aes(x = as.factor(SEV_CONT), y = HEIGH)) +
    geom_boxplot()

ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$UHEIG),], aes(x = as.factor(SEV_CONT), y = UHEIG)) +
    geom_boxplot()
```

### Timber productivity rating
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of timber porductivity classes. Inner matrix remnants seem to be a subsample of the other two.
```{r TPR_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$TPR),], aes(x = as.factor(SEV_CONT), fill = TPR)) +
  geom_histogram(stat = "count", position = "dodge")
```

### Non forest vegetated land
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of non forested land classes. Inner matrix remnants seem to be a subsample of the other two.

```{r NFL_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$NFL),], aes(x = as.factor(SEV_CONT), fill = NFL)) +
  geom_histogram(stat = "count", position = "dodge")
```

### Natural-non vegetated land
Disturbed patches and outer matrix remnants have a qualitatively similar distribution of class frequencies, with quite a few flooded areas (NWF) and rivers (NWR). Inner matix remnants also have several river patches, but no flooded areas. They also seem to have a higher relative proportion of sandy soil (NMS)

```{r NATN_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$NAT_N),], aes(x = as.factor(SEV_CONT), fill = NAT_N)) +
  geom_histogram(stat = "count", position = "dodge")
```

### Forest age - Origin
Disturbed patches and outer matrix remnants have identical age distributions (which are not being added up at all). Inner matrix patches seem to be a very biased subsample.

```{r orig_patch, echo=FALSE}
ggplot(AB1_vegFireEvents.mdt[!is.na(AB1_vegFireEvents.mdt$ORIGI),], aes(x = as.factor(SEV_CONT), y = ORIGI)) +
  geom_boxplot()
```

